### 2016-09-20 latex/Adaptive_distance_metric_notes.tex
add

\documentclass[]{article}

\renewcommand{\baselinestretch}{1.2}
\renewcommand{\v}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\mc}{\mathcal}

\def\st{{\rm s.t.}}

\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage[usenames,dvipsnames]{color}
\usepackage{fullpage,graphicx,amssymb,amsmath}
\usepackage{enumerate}
\usepackage{subfigure}

\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}
\newtheorem{conjecture}{Conjecture}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newcommand{\hs}[1]{\hspace{#1}}
\newcommand{\vs}[1]{\vspace{#1}}
\newcommand{\mnorm}[1]{||{#1}||_{\infty}}
\newcommand{\pf}{\textbf{Proof} \indent}
\newcommand{\qed}{\hfill $\Box$}
\newcommand{\argmin}{\rm argmin}
\newcommand{\proof}{\pf}

\newcommand{\Cvar}{\mathbb{CVAR}} % Conditional value-at-risk
%\newcommand{\Cvar}{\mathbb{CV}@\mathbb{R}} % Conditional value-at-risk
\newcommand{\Var}{\mathbb{VAR}} % Value-at-risk
%\newcommand{\Var}{\mathbb{V}\text{a}\mathbb{R}} % Value-at-risk
%\newcommand{\Var}{\mathbb{V}@\mathbb{R}} % Value-at-risk

\newcommand{\cone}{{\rm cone}} % Cone
\newcommand{\conv}{{\rm conv}} % Convex hull
\newcommand{\clconv}{{\rm clconv}} % Closed convex hull
\newcommand{\Cov}{{\rm Cov}} % Covariance
\newcommand{\D}{\mathbb{D}} % Distance metric
\newcommand{\E}{\mathbb{E}} % Expectation
\renewcommand{\P}{\mathbb{P}} % Probability
\renewcommand{\Re}{\mathbb{R}} % Real numbers
\renewcommand{\S}{\mathcal{S}} % Set of scenarios
\newcommand{\Z}{\mathbb{Z}} % Integers

\newcommand{\vell}{\boldsymbol{\ell}}
\newcommand{\valpha}{\boldsymbol{\alpha}}
\newcommand{\vbeta}{\boldsymbol{\beta}}
\newcommand{\vgamma}{\boldsymbol{\gamma}}
\newcommand{\vGamma}{\boldsymbol{\Gamma}}
\newcommand{\vdelta}{\boldsymbol{\delta}}
\newcommand{\vlambda}{\boldsymbol{\lambda}}
\newcommand{\vLambda}{\boldsymbol{\Lambda}}
\newcommand{\vxi}{\boldsymbol{\xi}}
\newcommand{\vpi}{\boldsymbol{\pi}}

\title{Adaptive Distance Metric Selection for Supervised Classification}
\author{Krishnan Kumaran and Dimitri J. Papageorgiou \\
{\small Corporate Strategic Research}\\
{\small ExxonMobil Research and Engineering Company}\\
{\small 1545 Route 22 East, Annandale, NJ 08801 USA}\\
{\small dimitri.j.papageorgiou@exxonmobil.com} \\
}

\begin{document}

\maketitle

\section{Introduction and motivation}

Clustering (also known as unsupervised classification) and Classification (commonly understood to be supervised, i.e., based on training data) are common ways of performing data analysis to perform a range of functions like anomaly detection and diagnosis, data segmentation and model development/refinement. Consequently, there is a large body of research on these topics (see for example [1] and references therein for a survey of currently used methods) offering different solutions ranging from K-means, spectral methods and other more complex methods for Clustering, as well as Support Vector Machines, Artificial Neural Networks (ANN), their non-linear Kernel-based variants and others for Classification.

All clustering methods require a similarity/distance metric between data points. While there are typically a few reasonable choices for most data, the results can depend strongly on this choice. The main goal of this project is to extend existing clustering work (e.g., [2,3,4]) to a semi-supervised classification method that is capable of learning the optimal distance/similarity metric directly from training data. The clustering problem can be formulated as an optimization problem (a mixed-integer linear program in its simplest form) that can be hard to solve for realistic data sizes. This approach using an adaptive distance metric has the potential to provide results of better quality than state-of-the-art techniques like Support Vector Machines.

\section{Problem statement}

Suppose we are given $N$ points $\v{v}_i \in \Re^p$ with class membership $\mc{C}_i$ for $i \in \mc{N} = \{1,\dots,N\}$.
Our goal is to find a distance metric $\D: \Re^p \mapsto \Re$ such that the following conditions hold:
\begin{enumerate}
\item $\D(\v{v}_i,\v{v}_j) = \v{a}^{\top}(\v{v}_i - \v{v}_j) + (\v{v}_i - \v{v}_j)^{\top} \v{B}(\v{v}_i - \v{v}_j) \quad \forall i,j \in \mc{N}$, for some $\v{a} \in \Re^p$ and $\v{B} \in \Re^{p \times p}$ and symmetric
\item $\D(\v{v}_i,\v{v}_j) \geq 0 \quad \forall i,j \in \mc{N}$
\item $\min_{j \in \mc{C}_i} \D(\v{v}_i,\v{v}_j) < \min_{k \notin \mc{C}_i} \D(\v{v}_i,\v{v}_j) \quad \forall i \in \mc{N}$
\end{enumerate}
Note that this is not a true ``distance metric'' since symmetry and the triangle property are not enforced.
The first condition could be extended to include higher order terms.
Let $\vdelta_{ij} = \v{v}_i - \v{v}_j$ for all $i,j \in \mc{N}$.
Finding such a distance metric can be expressed as the following optimization problem:
\begin{subequations} \label{model:1}
\begin{alignat}{4}
\max_{\lambda,\v{a},\v{B},\v{d}}~~& \lambda &&  \\
\st~~& \min_{j \in \mc{C}_i} d_{ij} + \lambda \leq \min_{k \notin \mc{C}_i} d_{ik} & & \qquad \forall i \in \mc{N} \label{eq:separation_requirement} \\
    & d_{ij} = \v{a}^{\top}\vdelta_{ij} + \vdelta_{ij}^{\top}\v{B}\vdelta_{ij} && \qquad \forall i,j \in \mc{N} \\
    & d_{ij} \geq 0 && \qquad  \forall i,j \in \mc{N} \\
    & \v{a} \in \Re^p && \\ 
    & \v{B} \in \Re^{p \times p}, \text{symmetric} &&
\end{alignat}
\end{subequations}

Let $\lambda_i = \left[ \min_{k \notin \mc{C}_i} d_{ik} \right] - \left[ \min_{j \in \mc{C}_i} d_{ij} \right]$ be the difference between the separation/distance from point $i$ to its nearest nonneighbor and the separation/distance from point $i$ to its nearest neighbor.  Ideally, we would like $\lambda_i > 0$ for all $i$.  However, this might not be possible when restricted to a set of distance functions.
In formulation \eqref{model:1}, we would like to maximize the minimum separation over all points as can be seen by re-writing constraint \eqref{eq:separation_requirement} as
$$
\lambda \leq \lambda_i \qquad \forall i \in \mc{N}
$$ 
and noting that the objective function is to maximize $\lambda$.

\subsection{Potential loss functions}

Let $L(\vlambda) = L(\lambda_1,\dots,\lambda_n)$ be a loss function based on the separation of each point $i$. 
Let $f = -L$ be the negative loss function.
In formulation \eqref{model:1}, we are interested in maximizing the function 
$$
f(\vlambda) = -L(\vlambda) = \min_{i \in \mc{N}} \lambda_i~.
$$
Of course, other loss functions are possible and should potentially be considered.

Option 1: Assume $f$ is linear and separable: 
\begin{equation}
f(\vlambda) = \sum_{i \in \mc{N}} f_i(\lambda_i)
\end{equation}

Option 2: Assume $f$ is piecewise linear increasing and separable: 
\begin{equation}
f^{\textrm{PWL-Cont}}(\lambda_i) = \left\{
\begin{array}{ll}
\alpha \lambda_i & \lambda_i \geq 0 \\
\beta \lambda_i & o.w. \\
\end{array}
\right.
\textrm{with } \alpha \leq \beta
\end{equation}

Option 3: Assume $f$ is piecewise linear, increasing up to a  and separable: 
\begin{equation}
f^{\textrm{PWL-DisCont}}(\lambda_i) = \left\{
\begin{array}{ll}
\alpha \lambda_i & \lambda_i \geq 0 \\
\beta & o.w. \\
\end{array}
\right.
\textrm{with }
\end{equation}

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.7]{Loss_functions_concatenated.png}
%\vspace{-0.25in}
\caption{Potential loss functions}
\label{fig:loss_functions_concatenated}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
%\includegraphics[width=5.0in,height=2.5in]{Circles_before_and_after_basic_step.png}
\includegraphics[scale=0.7]{sigmoid_from_wikipedia.png}
%\vspace{-0.25in}
\caption{Sigmoid function. [Source: wikipedia]}
\label{fig:sigmoid}
\end{center}
\end{figure}

\subsection{Imposing a $K>1$ nearest neighbor condition}

Let $d_{i(j)}$ denote the distance of the $j$th closest point to point $i \in \mc{N}$, i.e.,
$d_{i(1)} \leq d_{i(2)} \dots\leq d_{i(|\mc{C}_i|)}$. 
Then, inequality \eqref{eq:separation_requirement} can be rewritten as 
\begin{equation}
d_{i(1)} + \lambda \leq d_{ik} \forall i \in \mc{N}, k \notin \mc{C}_i
\end{equation}

A more restrictive requirement 
\begin{equation}
d_{i(t)} + \lambda \leq d_{ik} \forall i \in \mc{N}, k \notin \mc{C}_i
\end{equation}

The above model can be generalized so that the requirement in inequality \eqref{eq:separation_requirement} holds for the $K$ closest points $j \in \mc{C}_i$, and

%\section{A linear programming approach to a Feasibility Variant of Model \eqref{model:1}}
\section{A linear programming approach to determine the existence of a feasible distance metric}

The existence of a distance metric satisfying conditions 1-3 can be expressed as the following feasibility (optimization) problem, where $\epsilon > 0$ is a given parameter:
\begin{subequations} \label{model:1_feasibility}
\begin{alignat}{4}
\max_{\lambda,\v{a},\v{B},\v{d}}~~& 0 &&  \\
\st~~& \min_{j \in \mc{C}_i} d_{ij} + \epsilon \leq \min_{k \notin \mc{C}_i} d_{ik} & & \qquad \forall i \in \mc{N} \label{eq:separation_requirement_eps} \\
    & d_{ij} = \v{a}^{\top}\vdelta_{ij} + \vdelta_{ij}^{\top} \v{B}\vdelta_{ij} && \qquad \forall i,j \in \mc{N} \\
    & d_{ij} \geq 0 && \qquad  \forall i,j \in \mc{N} \\
    & \v{a} \in \Re^p && \\ 
    & \v{B} \in \Re^{p \times p}, \text{symmetric} &&
\end{alignat}
\end{subequations}

Given $\epsilon > 0$, model \eqref{model:1} can be expressed as a linear programming feasibility problem, albeit potentially a very large one.
\begin{subequations} \label{model:big_lp_1}
\begin{alignat}{4}
\max_{\v{a},\v{B},\v{d},\v{t}}~~& \sum_{i \in \mc{N}} t_i &&  \\
\st~~& t_i + \epsilon \leq d_{ik} && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \label{eq:big_lp_separation_constr_t} \\
    & t_i \leq d_{ij} && \qquad \forall i \in \mc{N}, j \in \mc{C}_i \label{eq:big_lp_dual_constr_t} \\
    & d_{ij} = \sum_{k=1}^p \delta_{ijk} a_{k} + \sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N} \label{eq:big_lp_distance_def_constr_t} \\
    & d_{ij} \geq 0 && \qquad \forall i,j \in \mc{N} \\
    & \v{a} \in \Re^p && \\ 
    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p \\
    & t_i \geq 0 & & \qquad \forall i \in \mc{N}
\end{alignat}
\end{subequations}
Model \eqref{model:big_lp_1} is always feasible since the origin $\v{0}$ is always feasible.
Note that $t_i$ represents the distance to point $i$'s nearest neighbor since constraints \eqref{eq:big_lp_dual_constr_t} ensure that $t_i \leq \min_{j \in \mc{C}_i} d_{ij}$,
while the objective function encourages $t_i = \min_{j \in \mc{C}_i} d_{ij}$ for all $i$.
Meanwhile, constraints \eqref{eq:big_lp_separation_constr_t} ensure that the separation $[\min_{k \in \mc{N}\backslash\mc{C}_i} d_{ik}] - [\min_{j \in \mc{C}_i} d_{ij}]$ is at least $\epsilon$.
If model \eqref{model:big_lp_1} returns a feasible solution with $t_i^* = \min_{j \in \mc{C}_i} d_{ij}^* > 0$ for all $i \in \mc{N}$, then the distance metric satisfies requirements 1-3.
Otherwise there exists a subset $\mc{O}$ of outlier points such that $0 \leq t_i^* < \min_{j \in \mc{C}_i} d_{ij}^*$ for all $i \in \mc{O}$, which means that no such distance metric guaranteeing a minimum separation exists for the choice of $\epsilon$.

\section{Mixed-Integer Linear Optimization Approaches}

\subsection{Max-Min Approach: Maximize the minimum separation with outliers}

Model \eqref{model:1} can be expressed as a huge mixed-integer linear programming problem:
\begin{subequations} \label{model:milp_with_outlier_detection}
\begin{alignat}{4}
\max_{\lambda,\v{B},\v{d},\v{w},\v{y}}~~& f(\vlambda) = \sum_{i \in \mc{N}} f_i(\lambda_i) = \sum_{i \in \mc{N}} (\lambda_i - \rho z_i) & & \\
\st~~& \sum_{j \in \mc{C}_i} w_{ij} + \lambda_i \leq d_{ik} + M_i z_i  && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \\
    & \lambda_i \leq 1 - z_i && \qquad \forall i \in \mc{N} \label{eq:outlier_separation_logic} \\
    & w_{ij} \leq d_{ij} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_1} \\
    & w_{ij} \leq y_{ij} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_2} \\
    & w_{ij} \geq d_{ij} + y_{ij} - 1 && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_3} \\
    & \sum_{j \in \mc{C}_i} y_{ij} = 1 && \qquad \forall i \in \mc{N} \\
    & d_{ij} = \sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N} \label{eq:big_milp_distance_def_constr} \\
    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p \\
    & d_{ij} \geq 0 && \qquad \forall i,j \in \mc{N} \\
    & w_{ij} \geq 0 && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \\
    & y_{ij} \in \{0,1\} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \\
    & z_{i} \in \{0,1\} && \qquad \forall i \in \mc{N} \\
    & \lambda_i \geq 0 & & \qquad \forall i \in \mc{N}
\end{alignat}
\end{subequations}

Model \eqref{model:milp_with_outlier_detection} assumes a linear reward for positive separation and a fixed (constant) penalty $\rho$ for each outlier.  
Outliers are handled through the binary $z_{i}$ decision variables.
If $z_{i} = 1$, then constraint \eqref{eq:outlier_separation_logic} ensures that the separation $\lambda_i$ is 0 and hence ignored; otherwise (if $z_{i} = 0$), this constraint is effectively ignored. 
Constraints \eqref{eq:mccormick_1}-\eqref{eq:mccormick_3} are the so-called McCormick envelopes needed to linearize the bilinear equation $w_{ij} = d_{ij} y_{ij}$.

TODO: Modify to incorporate assumption that $0 \leq d_{ij} \leq 1$ for all $i$ and $j$.

\newpage
\section{Nomenclature}
\begin{center}
\begin{tabular}{cl}
Decision variable & Definition \\
\hline
$d_{ij}$ & distance between points $i$ and $j$ \\
$w_{ij}$ & $d_{ij}y_{ij}$  \\
$y_{ij}$ & 1 if point $j$ is the closest neighbor to $i$; 0 otherwise  \\
$z_{i}$  & 1 if point $i$ is an outlier; 0 otherwise  \\
$\lambda_i$ & separation (difference) between closest non-neighbor and closest neighbor \\$\lambda_i$ & separation (difference) between closest non-neighbor and closest neighbor \\
$\v{B}$ & $\frac{p(p-1)}{2}$ \\ 
\end{tabular}
\end{center}

\begin{proposition}
Note that we may always assume that the data (input vectors) $v_{i}$ have been normalized to reside in the unit hypercube as follows: $v_{ij} \leftarrow (v_{ij} - m)/(M-m)$ where $m=\min\{v_{ij} : i \in \mc{N}, j=1,\dots,D \}$ and $M=\max\{v_{ij} : i \in \mc{N}, j=1,\dots,D \}$.
\end{proposition}

\end{document}

### 2016-09-28 latex/Adaptive_distance_metric_notes.tex
Add

@@
 \usepackage{subfigure}
+
+\usepackage[colorinlistoftodos,bordercolor=orange,backgroundcolor=orange!20,linecolor=orange,textsize=scriptsize]{todonotes}
 
@@
 \end{subequations}
+\todo[inline]{
+Are we missing $a$ in   \eqref{eq:big_milp_distance_def_constr}
+}
 
@@
 TODO: Modify to incorporate assumption that $0 \leq d_{ij} \leq 1$ for all $i$ and $j$.
+
+\subsection{New Idea}
+
+put here the model from above using only one  $\lambda$
+
+\begin{subequations} \label{model:milp_with_outlier_detection_adssasdsa}
+\begin{alignat}{4}
+\max_{\lambda,\v{B},\v{d},\v{w},\v{y}}~~& f(\vlambda) = \sum_{i \in \mc{N}} f_i(\lambda_i) = \sum_{i \in \mc{N}} (\lambda_i - \rho z_i) & & \\
+\st~~& \sum_{j \in \mc{C}_i} w_{ij} + \lambda_i \leq d_{ik} + M_i z_i  && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \\
+    & \lambda_i \leq 1 - z_i && \qquad \forall i \in \mc{N} \label{eq:outlier_separation_logic_adssasdsa} \\
+    & w_{ij} \leq d_{ij} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_1_adssasdsa} \\
+    & w_{ij} \leq y_{ij} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_2_adssasdsa} \\
+    & w_{ij} \geq d_{ij} + y_{ij} - 1 && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_3_adssasdsa} \\
+    & \sum_{j \in \mc{C}_i} y_{ij} = 1 && \qquad \forall i \in \mc{N} \\
+    & d_{ij} = \sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N} \label{eq:big_milp_distance_def_constr_adssasdsa} \\
+    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p \\
+    & d_{ij} \geq 0 && \qquad \forall i,j \in \mc{N} \\
+    & w_{ij} \geq 0 && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \\
+    & y_{ij} \in \{0,1\} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \\
+    & z_{i} \in \{0,1\} && \qquad \forall i \in \mc{N} \\
+    & \lambda_i \geq 0 & & \qquad \forall i \in \mc{N}
+\end{alignat}
+\end{subequations}
 

### 2016-10-19 latex/Adaptive_distance_metric_notes.tex
sync with emails

--- 2016-09-20 latex/Adaptive_distance_metric_notes.tex
@@
 
+\newcommand{\xor}{\underline{\vee}}
+\newcommand{\Xor}{\underline{\bigvee}}
+
 \title{Adaptive Distance Metric Selection for Supervised Classification}
@@
 Finding such a distance metric can be expressed as the following optimization problem:
+
 \begin{subequations} \label{model:1}
@@
 
+\newpage
 %\section{A linear programming approach to a Feasibility Variant of Model \eqref{model:1}}
@@
 
-The existence of a distance metric satisfying conditions 1-3 can be expressed as the following feasibility (optimization) problem, where $\epsilon > 0$ is a given parameter:
-\begin{subequations} \label{model:1_feasibility}
+Let $\mc{F}$ denote the feasible region associated with the distance metric parameters, i.e.,
+\begin{equation}
+\mc{F} = \{ (\v{a},\v{B},\v{d}) \in \Re^p \times \Re^{p \times p} \times \Re_+^{N \times N} : \v{B}~\text{symmetric}, d_{ij} = \v{a}^{\top}\vdelta_{ij} + \vdelta_{ij}^{\top} \v{B}\vdelta_{ij} \quad \forall i,j \in \mc{N} \}
+\end{equation}
+or
+\begin{subequations} \label{set:feasible_region_distance_metric}
 \begin{alignat}{4}
-\max_{\lambda,\v{a},\v{B},\v{d}}~~& 0 &&  \\
-\st~~& \min_{j \in \mc{C}_i} d_{ij} + \epsilon \leq \min_{k \notin \mc{C}_i} d_{ik} & & \qquad \forall i \in \mc{N} \label{eq:separation_requirement_eps} \\
-    & d_{ij} = \v{a}^{\top}\vdelta_{ij} + \vdelta_{ij}^{\top} \v{B}\vdelta_{ij} && \qquad \forall i,j \in \mc{N} \\
-    & d_{ij} \geq 0 && \qquad  \forall i,j \in \mc{N} \\
+\mc{F} = \Bigg\{ \v{a},\v{B},\v{d} : &  &&  \\
+    & d_{ij} = \sum_{k=1}^p \delta_{ijk} a_{k} + \sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N} \label{eq:distance_metric_def} \\
+    & 0 \leq d_{ij} \leq 1 && \qquad \forall i,j \in \mc{N} \\
     & \v{a} \in \Re^p && \\ 
-    & \v{B} \in \Re^{p \times p}, \text{symmetric} &&
+    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p \Bigg\}
 \end{alignat}
@@
 
-Given $\epsilon > 0$, model \eqref{model:1} can be expressed as a linear programming feasibility problem, albeit potentially a very large one.
+The existence of a distance metric satisfying conditions 1-3 can be expressed as the following feasibility (nonlinear optimization) problem, where $\epsilon > 0$ is a given parameter:
+%\begin{subequations} \label{model:1_feasibility}
+%\begin{alignat}{4}
+%\max_{\v{a},\v{B},\v{d}}~~& 0 &&  \\
+%\st~~& \min_{j \in \mc{C}_i} d_{ij} + \epsilon \leq \min_{k \notin \mc{C}_i} d_{ik} & & \qquad \forall i \in \mc{N} \label{eq:separation_requirement_eps} \\
+%    & d_{ij} = \v{a}^{\top}\vdelta_{ij} + \vdelta_{ij}^{\top} \v{B}\vdelta_{ij} && \qquad \forall i,j \in \mc{N} \\
+%    & d_{ij} \geq 0 && \qquad  \forall i,j \in \mc{N} \\
+%    & \v{a} \in \Re^p && \\ 
+%    & \v{B} \in \Re^{p \times p}, \text{symmetric} &&
+%\end{alignat}
+%\end{subequations}
+\begin{subequations} \label{model:1_feasibility}
+\begin{alignat}{4}
+\max_{\v{a},\v{B},\v{d}}~~& 0 &&  \\
+\st~~& \min_{j \in \mc{C}_i} d_{ij} + \epsilon \leq \min_{k \notin \mc{C}_i} d_{ik} & & \qquad \forall i \in \mc{N} \label{eq:separation_requirement_eps} \\
+    & (\v{a},\v{B},\v{d}) \in \mc{F} &&
+\end{alignat}
+\end{subequations}
+Note that if we constrain the distances to be bounded (e.g., $d_{ij} \in [0,1]$), problem \eqref{model:1_feasibility} is not guaranteed to be feasible for an arbitrary choice of $\epsilon$. 
+To see this, let $\epsilon > 0$ and consider an example with three points and two classes.
+Point 1 is located at (0,0), point 2 at (1,1), and point 3 at $(\epsilon/2,\epsilon/2)$.
+Points 1 and 2 belong to class 1, while point 3 belongs to class 2.
+There is no way to create a distance metric that guarantees that $d_{13} > \epsilon$ and $d_{23} > \epsilon$.
+
+There are several ways to proceed.
+
+\subsection{Multi-Objective approach}
+Let $W$ be a positive scalar.  
+We could solve the following LP that maximizes both $\epsilon$ and the minimum distance variables $t_i$:
+\begin{subequations} \label{model:multi_objective_lp_1}
+\begin{alignat}{4}
+\max_{\v{a},\v{B},\v{d},\epsilon,\v{t}}~~& W\epsilon + \sum_{i \in \mc{N}} t_i &&  \\
+\st~~& t_i + \epsilon \leq d_{ik} && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \label{eq:mo_lp_separation_constr_t} \\
+    & t_i \leq d_{ij} && \qquad \forall i \in \mc{N}, j \in \mc{C}_i \label{eq:mo_lp_dual_constr_t} \\
+    & t_i \geq 0 & & \qquad \forall i \in \mc{N} \\
+    & \eqref{set:feasible_region_distance_metric} & & 
+\end{alignat}
+\end{subequations}
+\begin{proposition}
+Problem \eqref{model:multi_objective_lp_1} is always feasible.
+\end{proposition}
+\proof The origin is always a feasible solution.  That is, set $\v{a} = \v{0},\v{B} = \v{0},\v{d} = \v{0},\epsilon = 0,\v{t} = \v{0}$.
+\qed
+
+\subsection{Iterative LP approach}
+
+First solve the following problem to determine the maximum non-neighbor separation $\epsilon$ that is possible. 
+\begin{subequations} \label{model:epsilon_lp_1}
+\begin{alignat}{4}
+\max_{\v{a},\v{B},\v{d},\epsilon}~~& \epsilon &&  \\
+\st~~& \epsilon \leq d_{ik} && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \label{eq:epsilon_lp_separation_constr_t} \\
+    & \eqref{set:feasible_region_distance_metric} & & 
+\end{alignat}
+\end{subequations}
+Let $\epsilon^{\max}$ be the maximum non-neighbor separation, i.e., the optimal value of $\epsilon$ in \eqref{model:epsilon_lp_1}.
+ Note that this problem is identical to problem \eqref{model:multi_objective_lp_1} after omitting the $\v{t}$ decision variables.  Hence, it is guaranteed to be feasible.
+
+Given $\epsilon \in (0,\epsilon^{\max}]$, model \eqref{model:1} can be expressed as a linear programming feasibility problem:
 \begin{subequations} \label{model:big_lp_1}
@@
     & t_i \leq d_{ij} && \qquad \forall i \in \mc{N}, j \in \mc{C}_i \label{eq:big_lp_dual_constr_t} \\
-    & d_{ij} = \sum_{k=1}^p \delta_{ijk} a_{k} + \sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N} \label{eq:big_lp_distance_def_constr_t} \\
-    & d_{ij} \geq 0 && \qquad \forall i,j \in \mc{N} \\
-    & \v{a} \in \Re^p && \\ 
-    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p \\
-    & t_i \geq 0 & & \qquad \forall i \in \mc{N}
+    & t_i \geq 0 & & \qquad \forall i \in \mc{N} \\
+    & \eqref{set:feasible_region_distance_metric} & & 
 \end{alignat}
 \end{subequations}
-Model \eqref{model:big_lp_1} is always feasible since the origin $\v{0}$ is always feasible.
+For $\epsilon \in (0,\epsilon^{\max}]$, model \eqref{model:big_lp_1} is always feasible since the origin $\v{0}$ is always feasible.
 Note that $t_i$ represents the distance to point $i$'s nearest neighbor since constraints \eqref{eq:big_lp_dual_constr_t} ensure that $t_i \leq \min_{j \in \mc{C}_i} d_{ij}$,
@@
 
+The following algorithm can be used to explore potential distance metrics for different levels of separation.
+
+\begin{algorithm}
+%{\small
+\caption{Iterative LP Heuristic}
+\label{algo:iterative_LP_heuristic}
+\begin{algorithmic}[1]
+\STATE Solve model \eqref{model:epsilon_lp_1}. Let $\epsilon^{\max}$ be the optimal objective function value.
+\STATE Let $\mc{E} = \{ i / \epsilon^{\max} : i=1,\ldots,I \}$ (e.g., $I=10$)
+\FOR{ $\epsilon \in \mc{E}$ }
+	\STATE Solve model \eqref{model:big_lp_1}.
+	\STATE Store the outliers and distance metric
+\ENDFOR
+\end{algorithmic}
+%}
+\end{algorithm}
+
+\newpage
 \section{Mixed-Integer Linear Optimization Approaches}
@@
 \newpage
+\section{Generalized disjunctive programming (GDP) formulations}
+
+This section presents several generalized disjunctive programming formulations.
+
+\textbf{Robust GDP formulation with no outliers}
+\begin{subequations} \label{model:gdp_robust_no_outliers}
+\begin{alignat}{4}
+\max_{\lambda,\v{a},\v{B},\v{d}}~~& \lambda &&  \\
+\st~~& \mathop{\Xor}_{j \in \mc{C}_i} [ d_{ij} + \lambda \leq d_{ik} \quad \forall k \notin \mc{C}_i ] && \qquad \forall i \in \mc{N} \label{eq:gdp_separation_constr} \\
+    & (\v{a},\v{B},\v{d}) \in \mc{F} && 
+\end{alignat}
+\end{subequations}
+Constraints \eqref{eq:gdp_separation_constr} read: ``the distance between point $i$ and its in-class neighbor $j_1 \in \mc{C}_i$ plus the separation $\lambda$ must not exceed the distance between point $i$ and all of its non-neighbors'' or ``the distance between point $i$ and its in-class neighbor $j_2 \in \mc{C}_i$ plus $\lambda$ must not exceed ...
+'' or ...
+
+\textbf{Robust GDP formulation with outliers}
+
+\begin{subequations} \label{model:gdp_robust_with_outliers}
+\begin{alignat}{4}
+\max_{\lambda,\v{a},\v{B},\v{d}}~~& \lambda - \rho \sum_{i \in \mc{N}} z_i &&  \\
+\st~~& \Bigg[ \mathop{\Xor}_{j \in \mc{C}_i} [ d_{ij} + \lambda \leq d_{ik} \quad \forall k \notin \mc{C}_i ] \Bigg]~\mathop{\Xor}~[z_i = 1] && \qquad \forall i \in \mc{N} \label{eq:gdp_robust_with_outliers_separation_constr} \\
+    & (\v{a},\v{B},\v{d}) \in \mc{F}, \v{z} \in \Re_+^N && 
+\end{alignat}
+\end{subequations}
+
+\textbf{GDP formulation with outliers}
+
+\begin{subequations} \label{model:gdp_nonrobust_with_outliers}
+\begin{alignat}{4}
+\max_{\vlambda,\v{a},\v{B},\v{d}}~~& \sum_{i \in \mc{N}} \lambda_i &&  \\
+\st~~& \Bigg[ \mathop{\Xor}_{j \in \mc{C}_i} [ d_{ij} + \lambda_i \leq d_{ik} \quad \forall k \notin \mc{C}_i; \lambda_i \geq 0 ] \Bigg]~\mathop{\Xor}~[\lambda_i = -\rho] && \qquad \forall i \in \mc{N} \label{eq:gdp_nonrobust_with_outliers_separation_constr} \\
+    & (\v{a},\v{B},\v{d}) \in \mc{F}, \lambda_i \geq -\rho && 
+\end{alignat}
+\end{subequations}
+
+\newpage
 \section{Nomenclature}

### 2016-10-19 latex/Adaptive_distance_metric_notes.tex
Add aims projest

@@
 \usepackage{algorithm}
-\usepackage[usenames,dvipsnames]{color}
+%\usepackage[usenames,dvipsnames]{color}
+
+\usepackage{todonotes}
+
 \usepackage{fullpage,graphicx,amssymb,amsmath}
@@
 
-TODO: Modify to incorporate assumption that $0 \leq d_{ij} \leq 1$ for all $i$ and $j$.
+\todo[inline]{Modify to incorporate assumption that $0 \leq d_{ij} \leq 1$ for all $i$ and $j$.}
+
+\subsection{Similar to previous but we will have just one lambda}
+\label{sec:mimax_oneLamnda}
+\todo[inline]{FInish this soon and compare with previous approach}
 
@@
 
+\newpage 
+\part{Progress Reports}
+
+\subsection{2016-10-21}
+\begin{itemize}
+\item Loading instance works
+
+\item Solving  \eqref{model:epsilon_lp_1} works now
+
+\item Model \eqref{model:milp_with_outlier_detection}
+works
+
+show some pictures here
+
+\item I did this and that
+\end{itemize}
+{\bf problems and questions:}
+\begin{itemize}
+\item queston 1
+\item question 2
+
+\end{itemize}
+{\bf suggestions:}
+\begin{itemize}
+\item section \ref{sec:mimax_oneLamnda}
+\end{itemize}
+
+\newpage
+\part{Tasks to do }
+
+\begin{itemize}
+\item put here the ideas from excel
+\end{itemize}
+
 \end{document}

### 2016-10-20 latex/Adaptive_distance_metric_notes.tex
Gershgorin Circle Theorem

@@
 \usepackage{subfigure}
+\usepackage{url}
 
@@
 
+\section{Gershgorin Circle Theorem}
+
+Reference \url{https://en.wikipedia.org/wiki/Gershgorin_circle_theorem}
+
+Why do we care about this theorem? It provides a sufficient condition to ensure that a square matrix is positive semi-definite.
+
+Let $\v{A}$ be a symmetric $n \times n$ matrix (hence, all eigenvalues are real).
+Let $R_{i}=\sum _{j\neq {i}} \left|a_{ij}\right|$ be the sum of the absolute values of the non-diagonal entries in the $i$-th row.
+Let $D(a_{ii},R_{i})$ be the closed circle (or disc) centered at $a_{ii}$ with radius $R_{i}$.
+Such a disc is called a Gershgorin disc.
+
+\begin{theorem}[Gershgorin Circle Theorem]
+Every eigenvalue of $\v{A}$ lies within at least one of the Gershgorin discs $D(a_{ii},R_{i})$.
+\end{theorem}
+
+Let $\lambda^{\min}(\v{A})$ be the smallest eigenvalue of $\v{A}$ and let $\lambda_G^{\min}(\v{A}) = \min_{i=1,\ldots,n} \{a_{ii} - R_i\}$.
+\begin{corollary}
+If $\lambda_G^{\min}(\v{A}) \geq 0$, then $\v{A}$ is positive semi-definite. 
+\end{corollary}
+\proof Gershgorin's circle theorem asserts that $\lambda_G^{\min}(\v{A})$ is a lower bound on the minimum eigenvalue of $\v{A}$, i.e., $\lambda^{\min}(\v{A}) \geq \lambda_G^{\min}(\v{A})$.
+One definition of a psd matrix is that all of its eigenvalues are non-negative.
+\qed
+
+In our problem, we may require the matrix $\v{B}$ to be positive semi-definite.
+Gershgorin's theorem tells us that this can be partially accomplished using linear programming techniques.
+(I say ``partially'' because Gershgorin's theorem is not a necessary condition, thus it enforcing $\lambda_G^{\min}(\v{A}) \geq 0$ is actually a restriction, i.e., it may forbid some eligible psd matrices.
+Nevertheless, it's an interesting starting point.)  To accomplish this with our matrix $\v{B}$, let $R_{k}(\v{B})=\sum _{\ell \neq k} \left|b_{k\ell}\right|$ and note that the condition $\lambda_G^{\min}(\v{B}) \geq 0$ implies that $\min_{k=1,\ldots,p} \{b_{kk} - R_k(\v{B})\} \geq 0$, which is equivalent to $b_{kk} - \sum _{\ell \neq k} \left|b_{k\ell}\right| \geq 0$ for all $k=1,\ldots,p$.
+After introducing auxiliary non-negative decision variables $b^+_{k\ell}$ to model $|b_{k\ell}|$ for all $k \neq \ell$, the latter can be converted into a set of linear constraint as follows:
+\begin{subequations} \label{model:gershgorin_restriction}
+\begin{alignat}{4}
+& b_{kk} - \sum _{\ell \neq k} b^+_{k\ell} \geq 0 && \qquad \forall k=1,\ldots,p \\
+& b^+_{k\ell} \geq b_{k\ell} && \qquad \forall k=1,\ldots,p, \ell=1,\ldots,p~(k \neq \ell) \\
+& b^+_{k\ell} \geq -b_{k\ell} && \qquad \forall k=1,\ldots,p, \ell=1,\ldots,p~(k \neq \ell) \\
+& b^+_{k\ell} \geq 0 && \qquad \forall k=1,\ldots,p, \ell=1,\ldots,p~(k \neq \ell)
+\end{alignat}
+\end{subequations}
+
+\todo[inline]{In the AIMMS code, we do not store the full $\v{B}$ matrix, but instead work only with the upper diagonal.
+Thus, it does not make sense to sum over all elements in row $k$ as written in $\sum _{\ell \neq k} b^+_{k\ell}$.
+Task: Write a similar version of constraints~\ref{model:gershgorin_restriction} in Latex.
+Implement these additional variables and constraints in AIMMS.
+Also, include a binary parameter, say, PI-Require-PSD (use underscores) such that these new variables and constraints are only active if PI-Require-PSD = 1, i.e., you should put a conditional statement ``$|$ ~ PI-Require-PSD'' in the ``index domain'' of these new variables and constraints.
+}
+
 \newpage 

### 2016-10-21 latex/Adaptive_distance_metric_notes.tex
add

@@
 
+\section{Plot of number of outliers as function $\epsilon$}
+
+\todo[inline]{Task 1: this should be done before next meeting on 2016-10-27}
+
+\todo[inline]{Task 2: make a plots a number of outliers as function of epsilon
++ show also the datasets which you have used and so on}
+
+\todo[inline]{Task 3: try different datasets, also generate the two gaussian mixtures}
+
+\todo[inline]{Task 4: find out how to export figure to EPS from AIMMS}
+
 \newpage

### 2016-10-21 latex/Adaptive_distance_metric_notes.tex
add

--- 2016-10-20 latex/Adaptive_distance_metric_notes.tex
@@
 
+\section{Plot of number of outliers as function $\epsilon$}
+
+\todo[inline]{this should be done before next meeting on 2016-10-27}
+
+\begin{itemize}
+\item 
+  make a plots a number of outliers as function of epsilon
++ show also the datasets which you have used and so on
+\item 
+  try different datasets, also generate the two gaussian mixtures
+\item   find out how to export figure to EPS from AIMMS
+\item  change a copy of {\bf output scatter plot} to use the learnt distance measure
+\end{itemize}
+
 \newpage

### 2016-10-21 latex/Adaptive_distance_metric_notes.tex
test

--- 2016-10-20 latex/Adaptive_distance_metric_notes.tex
@@
 \usepackage{subfigure}
-\usepackage{url}
 
@@
 
-\section{Gershgorin Circle Theorem}
-
-Reference \url{https://en.wikipedia.org/wiki/Gershgorin_circle_theorem}
-
-Why do we care about this theorem? It provides a sufficient condition to ensure that a square matrix is positive semi-definite.
-
-Let $\v{A}$ be a symmetric $n \times n$ matrix (hence, all eigenvalues are real).
-Let $R_{i}=\sum _{j\neq {i}} \left|a_{ij}\right|$ be the sum of the absolute values of the non-diagonal entries in the $i$-th row.
-Let $D(a_{ii},R_{i})$ be the closed circle (or disc) centered at $a_{ii}$ with radius $R_{i}$.
-Such a disc is called a Gershgorin disc.
-
-\begin{theorem}[Gershgorin Circle Theorem]
-Every eigenvalue of $\v{A}$ lies within at least one of the Gershgorin discs $D(a_{ii},R_{i})$.
-\end{theorem}
-
-Let $\lambda^{\min}(\v{A})$ be the smallest eigenvalue of $\v{A}$ and let $\lambda_G^{\min}(\v{A}) = \min_{i=1,\ldots,n} \{a_{ii} - R_i\}$.
-\begin{corollary}
-If $\lambda_G^{\min}(\v{A}) \geq 0$, then $\v{A}$ is positive semi-definite. 
-\end{corollary}
-\proof Gershgorin's circle theorem asserts that $\lambda_G^{\min}(\v{A})$ is a lower bound on the minimum eigenvalue of $\v{A}$, i.e., $\lambda^{\min}(\v{A}) \geq \lambda_G^{\min}(\v{A})$.
-One definition of a psd matrix is that all of its eigenvalues are non-negative.
-\qed
-
-In our problem, we may require the matrix $\v{B}$ to be positive semi-definite.
-Gershgorin's theorem tells us that this can be partially accomplished using linear programming techniques.
-(I say ``partially'' because Gershgorin's theorem is not a necessary condition, thus it enforcing $\lambda_G^{\min}(\v{A}) \geq 0$ is actually a restriction, i.e., it may forbid some eligible psd matrices.
-Nevertheless, it's an interesting starting point.)  To accomplish this with our matrix $\v{B}$, let $R_{k}(\v{B})=\sum _{\ell \neq k} \left|b_{k\ell}\right|$ and note that the condition $\lambda_G^{\min}(\v{B}) \geq 0$ implies that $\min_{k=1,\ldots,p} \{b_{kk} - R_k(\v{B})\} \geq 0$, which is equivalent to $b_{kk} - \sum _{\ell \neq k} \left|b_{k\ell}\right| \geq 0$ for all $k=1,\ldots,p$.
-After introducing auxiliary non-negative decision variables $b^+_{k\ell}$ to model $|b_{k\ell}|$ for all $k \neq \ell$, the latter can be converted into a set of linear constraint as follows:
-\begin{subequations} \label{model:gershgorin_restriction}
-\begin{alignat}{4}
-& b_{kk} - \sum _{\ell \neq k} b^+_{k\ell} \geq 0 && \qquad \forall k=1,\ldots,p \\
-& b^+_{k\ell} \geq b_{k\ell} && \qquad \forall k=1,\ldots,p, \ell=1,\ldots,p~(k \neq \ell) \\
-& b^+_{k\ell} \geq -b_{k\ell} && \qquad \forall k=1,\ldots,p, \ell=1,\ldots,p~(k \neq \ell) \\
-& b^+_{k\ell} \geq 0 && \qquad \forall k=1,\ldots,p, \ell=1,\ldots,p~(k \neq \ell)
-\end{alignat}
-\end{subequations}
-
-\todo[inline]{In the AIMMS code, we do not store the full $\v{B}$ matrix, but instead work only with the upper diagonal.
-Thus, it does not make sense to sum over all elements in row $k$ as written in $\sum _{\ell \neq k} b^+_{k\ell}$.
-Task: Write a similar version of constraints~\ref{model:gershgorin_restriction} in Latex.
-Implement these additional variables and constraints in AIMMS.
-Also, include a binary parameter, say, PI-Require-PSD (use underscores) such that these new variables and constraints are only active if PI-Require-PSD = 1, i.e., you should put a conditional statement ``$|$ ~ PI-Require-PSD'' in the ``index domain'' of these new variables and constraints.
-}
-
 \newpage 
@@
 \item Model \eqref{model:milp_with_outlier_detection}
-works
+works. I did it in the aimms code "MILP SECTION4" Part.
 
-show some pictures here
-
-\item I did this and that
 \end{itemize}
@@
 \begin{itemize}
-\item queston 1
+\item queston 1 How to show the certain points in the plots?
 \item question 2
 
-\end{itemize}
-{\bf suggestions:}
-\begin{itemize}
-\item section \ref{sec:mimax_oneLamnda}
 \end{itemize}
@@
 \begin{itemize}
-\item put here the ideas from excel
+\item 1. Create new dataset -> e.g. 2 - Guassian with diffrent mu and Sigma
+\item 2. ammend the code to add new point in a.g. Scatter Point
+\item 3. Implement Optimization of Distance Metrix                 ACCOMPLISHED
+\item 4. Add the robust version for section 4. (have just one lambda) both Latex and AIMS (PROCESSING)
+\item 5. Create a performance profiles -- example 100 datasets and comapre 3-4 distance measures 
+\item 6. add new codes for replacing "a delta"  -> to  "a |delta| "           ACCOMPLISHED
+\item 7. add button to load instance          ACCOMPLISHED
+\item 8. For Infesible problem we solved during the meeting why it was not infeasible                  ACCOMPLISHED
+
 \end{itemize}

### 2016-10-21 latex/Adaptive_distance_metric_notes.tex
Add DImitris's stuff

--- 2016-10-21 latex/Adaptive_distance_metric_notes.tex
@@
 
+\usepackage{url}
 \newcommand{\cone}{{\rm cone}} % Cone
@@
 
+\newpage
 \section{Gershgorin Circle Theorem}

### 2016-11-18 latex/Adaptive_distance_metric_notes.tex
Add

--- 2016-10-21 latex/Adaptive_distance_metric_notes.tex
@@
 \newpage 
-\part{Progress Reports}
+\section{Progress Reports 2016-10-21}
 
-\subsection{2016-10-21}
 \begin{itemize}
@@
 
-\newpage
-\part{Tasks to do }
+{\bf Tasks to do }
 
 \begin{itemize}
-\item 1. Create new dataset -> e.g. 2 - Guassian with diffrent mu and Sigma
+\item 1. Create new dataset - e.g.  - Guassian with diffrent mu and Sigma
 \item 2. ammend the code to add new point in a.g. Scatter Point
@@
 \item 5. Create a performance profiles -- example 100 datasets and comapre 3-4 distance measures 
-\item 6. add new codes for replacing "a delta"  -> to  "a |delta| "           ACCOMPLISHED
+\item 6. add new codes for replacing "a delta"  - to  "a |delta| "           ACCOMPLISHED
 \item 7. add button to load instance          ACCOMPLISHED
@@
 
+\newpage
+\section{Progress Reports 2016-11-04}
+
+\begin{itemize}
+\item 1. Create new dataset - e.g.  - Guassian with diffrent mu and Sigma (ACCOMPLISHED)
+
+\item 2. Add the robust version for section 4. (have just one lambda) in AIMMS (ACCOMPLISHED)
+
+\item 3. Find out how to export figure to EPS from AIMMS (PROCESSING)
+
+\item 4. Change a copy of output scatter plot to use the learnt distance measure (ACCOMPLISHED)
+
+\end{itemize}
+{\bf problems and questions:}
+\begin{itemize}
+\item 1. What should I do next? Higher dimension or something else?
+
+\item 2. Still dont know how to draw a circle on a node in AIMMS.
+
+\item 3. I covered the last file u updated by mistake, so I cant see the new theory. Would u please send it to me again? I will merge all of the files in one tex, thx.
+
+\end{itemize}
+
+\newpage
+\section{Progress Reports 2016-11-11}
+
+\subsection{Shatter outliers and see $\epsilon$ and Distance Matrices in LP approach}
+
+First run the model in \eqref{model:epsilon_lp_1} in Aimms. 
+We do these in Annulus Example 10.1 with 150 points, 2 classes, Probability of outliers = 0.05 and Noise = 0.5.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.7]{Example_10_1_Origin.PNG}
+%\vspace{-0.25in}
+\caption{Example 10.1}
+\label{fig:Example_10_1_Origin}
+\end{center}
+\end{figure}
+
+After running the model in \eqref{model:epsilon_lp_1} in Aimms, we get a maximized $\epsilon$ =  0.001113532065 with outliers.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.7]{Example_10_1_outliers_1.PNG}
+%\vspace{-0.25in}
+\caption{Example 10.1 Outliers}
+\label{fig:Example_10_1_outliers_1}
+\end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.7]{Example_10_1_DistanceMatrix_1.PNG}
+%\vspace{-0.25in}
+\caption{Example 10.1 DistanceMatrix}
+\label{fig:Example_10_1_DistanceMatrix_1}
+\end{center}
+\end{figure}
+
+\newpage
+Now we delete the outliers and do\eqref{model:epsilon_lp_1} in Aimms again.
+we get a maximized $\epsilon$ =  0.01597093404 with outliers again.
+This $\epsilon$ is much larger than $\epsilon$ =  0.001113532065 in Example 10.1.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.7]{Example_10_2_outliers_1.PNG}
+%\vspace{-0.25in}
+\caption{Example 10.2 Outliers}
+\label{fig:Example_10_2_outliers_1}
+\end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.7]{Example_10_2_DistanceMatrix_1.PNG}
+%\vspace{-0.25in}
+\caption{Example 10.2 DistanceMatrix}
+\label{fig:Example_10_2_DistanceMatrix_1}
+\end{center}
+\end{figure}
+
+\newpage
+If we keep running the iterations, we get new outliers with new $\epsilon$ s and different Distance Matrix.
+In some cases, there will be always outliers after each iteration.
+Fortunately, In this case, we have only 3 iterations to get no outliers.
+In iteration 3, $\epsilon$ = 0.01597460757.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.7]{Example_10_3_outliers_1.PNG}
+%\vspace{-0.25in}
+\caption{Example 10.3 Outliers}
+\label{fig:Example_10_3_outliers_1}
+\end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.7]{Example_10_3_DistanceMatrix_1.PNG}
+%\vspace{-0.25in}
+\caption{Example 10.3 DistanceMatrix}
+\label{fig:Example_10_3_DistanceMatrix_1}
+\end{center}
+\end{figure}
+
+\newpage
+\subsection{Put back outliers to new model}
+We put back outliers to new model to see if they are still outliers.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.7]{Example_10_3_OutliersBack_1.PNG}
+%\vspace{-0.25in}
+\caption{Example 10.3 Outliers Back}
+\label{fig:Example_10_3_OutliersBack_1}
+\end{center}
+\end{figure}
+
+Compaired to outliers in previous iterations, the previous outliers are still outliers with new Distance Matrices in iteration = 3.
+
+{\bf problems and questions:}
+\begin{itemize}
+\item 1. If a case is "unfortunate" one(keeps popping out outliers in each iteration), how do we choose the value of $\epsilon$ to get a solution?
+
+\item 2. I just show some case that "outliers are still outliers",but how do we guarantee others follow the same rule ?
+
+\end{itemize}
+\newpage
+
+\section{Progress Reports 2016-11-18}
+
+\begin{itemize}
+\item 1. Fix the BUG of mistakes in showing the outliers (ACCOMPLISHED)
+
+\item 2. Fix the mistake of formula using in AIMMS (ACCOMPLISHED)
+
+\item 3. Do Iterations to refill the NonOutliers into the original dataset (Processing)
+
+\end{itemize}
+{\bf problems and questions:}
+\begin{itemize}
+\item 1. AIMMS CODE: How to clone a brand new set from a sub set of "a Set" without any effect when "a Set" changes? Stuck here.
+
+\end{itemize}
+
+\newpage
+
 \end{document}
+
+\section{Nomenclature}

### 2016-11-19 icml2017/paper.tex
add

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% ICML 2016 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Use the following line _only_ if you're still using LaTeX 2.09.
%\documentstyle[icml2016,epsf,natbib]{article}
% If you rely on Latex2e packages, like most moden people use this:
\documentclass{article}

% use Times
\usepackage{times}
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure}

% For citations
\usepackage{natbib}

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2016} with
% \usepackage[nohyperref]{icml2016} above.
\usepackage{hyperref}

% Packages hyperref and algorithmic misbehave sometimes.  We can fix
% this with the following command.
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
\usepackage{icml2016}

% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
%\usepackage[accepted]{icml2016}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{TODO2}

\begin{document}

\twocolumn[
\icmltitle{TODO}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2016
% package.
\icmlauthor{Your Name}{email@yourdomain.edu}
\icmladdress{Your Fantastic Institute,
            314159 Pi St., Palo Alto, CA 94306 USA}
\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
\icmladdress{Their Fantastic Institute,
            27182 Exp St., Toronto, ON M6H 2T1 CANADA}

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{boring formatting information, machine learning, ICML}

\vskip 0.3in
]

\begin{abstract} 
TODO
\end{abstract}

\section{Introduction and Motivation}

\paragraph{Contributions.}

\section{Algorithm}

\section{Numerical Experiments/Results}

\section{Conclusion}

 % Acknowledgements should only appear in the accepted version.

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
%\nocite{langley00}

\bibliography{example_paper}
\bibliographystyle{icml2016}

\end{document}

\section*{Acknowledgements}

\textbf{Do not} include acknowledgements in the initial version of
the paper submitted for blind review.

If a paper is accepted, the final camera-ready version can (and
probably should) include acknowledgements. In this case, please
place such acknowledgements in an unnumbered section at the
end of the paper. Typically, this will include thanks to reviewers
who gave useful comments, to colleagues who contributed to the ideas, 
and to funding agencies and corporate sponsors that provided financial 
support.

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was
% created by Lise Getoor and Tobias Scheffer, it was slightly modified  
% from the 2010 version by Thorsten Joachims & Johannes Fuernkranz, 
% slightly modified from the 2009 version by Kiri Wagstaff and 
% Sam Roweis's 2008 version, which is slightly modified from 
% Prasad Tadepalli's 2007 version which is a lightly 
% changed version of the previous year's version by Andrew Moore, 
% which was in turn edited from those of Kristian Kersting and 
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2016-12-19 papers/Outlier_reinsertion_via_milp.tex
add

\documentclass[]{article}

\renewcommand{\baselinestretch}{1.2}
\renewcommand{\v}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\mc}{\mathcal}

\def\st{{\rm s.t.}}

\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage[usenames,dvipsnames]{color}
\usepackage{fullpage,graphicx,amssymb,amsmath}
\usepackage{enumerate}
\usepackage{subfigure}

\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}
\newtheorem{conjecture}{Conjecture}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newcommand{\hs}[1]{\hspace{#1}}
\newcommand{\vs}[1]{\vspace{#1}}
\newcommand{\mnorm}[1]{||{#1}||_{\infty}}
\newcommand{\pf}{\textbf{Proof} \indent}
\newcommand{\qed}{\hfill $\Box$}
\newcommand{\argmin}{\rm argmin}
\newcommand{\proof}{\pf}

\newcommand{\Cvar}{\mathbb{CVAR}} % Conditional value-at-risk
%\newcommand{\Cvar}{\mathbb{CV}@\mathbb{R}} % Conditional value-at-risk
\newcommand{\Var}{\mathbb{VAR}} % Value-at-risk
%\newcommand{\Var}{\mathbb{V}\text{a}\mathbb{R}} % Value-at-risk
%\newcommand{\Var}{\mathbb{V}@\mathbb{R}} % Value-at-risk

\newcommand{\cone}{{\rm cone}} % Cone
\newcommand{\conv}{{\rm conv}} % Convex hull
\newcommand{\clconv}{{\rm clconv}} % Closed convex hull
\newcommand{\Cov}{{\rm Cov}} % Covariance
\newcommand{\D}{\mathbb{D}} % Distance metric
\newcommand{\E}{\mathbb{E}} % Expectation
\renewcommand{\P}{\mathbb{P}} % Probability
\renewcommand{\Re}{\mathbb{R}} % Real numbers
\renewcommand{\S}{\mathcal{S}} % Set of scenarios
\newcommand{\Z}{\mathbb{Z}} % Integers

\newcommand{\vell}{\boldsymbol{\ell}}
\newcommand{\valpha}{\boldsymbol{\alpha}}
\newcommand{\vbeta}{\boldsymbol{\beta}}
\newcommand{\vgamma}{\boldsymbol{\gamma}}
\newcommand{\vGamma}{\boldsymbol{\Gamma}}
\newcommand{\vdelta}{\boldsymbol{\delta}}
\newcommand{\vlambda}{\boldsymbol{\lambda}}
\newcommand{\vLambda}{\boldsymbol{\Lambda}}
\newcommand{\vxi}{\boldsymbol{\xi}}
\newcommand{\vpi}{\boldsymbol{\pi}}

\newcommand{\xor}{\underline{\vee}}
\newcommand{\Xor}{\underline{\bigvee}}

\title{Outlier re-insertion via Mixed-Integer Linear Programming}
\author{Dimitri J. Papageorgiou \\
{\small Corporate Strategic Research}\\
{\small ExxonMobil Research and Engineering Company}\\
{\small 1545 Route 22 East, Annandale, NJ 08801 USA}\\
{\small dimitri.j.papageorgiou@exxonmobil.com} \\
}

\begin{document}

\maketitle

\section{Outlier re-insertion}

We assume that the distance metric $d_{ij}$ is fixed for the remainder of this section.
Let $\mc{N}$ be the set of all points, 
$\mc{C}_i$ the set of co-class neighbors of point $i$, 
$\bar{\mc{C}}_i$ the set of non co-class neighbors of point $i$, and 
$\mc{O}$ the current set of outliers. 
Let $\mc{IK} = \{ (i,k) \in \mc{N} \times \mc{N} : \nexists~j \in \mc{C}_i \backslash \mc{O}: d_{ij} + \epsilon \leq d_{ik}, k \in \bar{\mc{C}}_i \}$.
Set $M_{ik} = 1 - d_{ik}$. (We are making use of our normalization $d_{ij} \in [0,1]$ here.)
For any outlier penalty parameter $\rho > 0$ (I suggest $\rho = 1$),
the following mixed-integer linear program attempts to minimize the number of outliers given a fixed distance metric.
\begin{subequations} \label{model:milp_outlier_reinsertion}
\begin{alignat}{4}
\min_{\v{y},\v{z}}~~& \rho \sum_{i \in \mc{O}} z_i & & \\
\st~~& \sum_{j \in \mc{C}_i} d_{ij}y_{ij} + \epsilon \leq d_{ik} + M_{ik} z_k && \qquad \forall (i,k) \in \mc{IK} \label{eq:bigM_constraint_reinsertion} \\
    & \sum_{j \in \mc{C}_i} y_{ij} = 1 && \qquad \forall i \in \mc{N} \backslash \mc{O}, j \in \mc{C}_i \label{eq:bigM_select_exactly_one_neighbor_1} \\
    & \sum_{j \in \mc{C}_i} y_{ij} = 1 - z_i && \qquad \forall i \in \mc{O}, j \in \mc{C}_i \label{eq:bigM_select_exactly_one_neighbor_2} \\
    & y_{ij} \leq 1 - z_j && \qquad \forall i \in \mc{N}, j \in \mc{C}_i \cap \mc{O} \\
    & y_{ij} \in \{0,1\} && \qquad \forall i \in \mc{N}, j \in \mc{C}_i \\
    & z_{i} \in \{0,1\} && \qquad \forall i \in \mc{O} \\
    & z_{i} = 0 && \qquad \forall i \in \mc{N} \backslash \mc{O} \label{eq:reinsertion_not_needed_in_aimms}
\end{alignat}
\end{subequations}

Several observations:
\begin{enumerate}
\item Bolun wrote the RHS of constraint~\eqref{eq:bigM_constraint_reinsertion} as $M_i (z_i + z_k)$.  This is correct, but the formulation above is tighter, meaning the linear programming relaxation provides a better lower bound, and thus optimizers believe it will be better.  Why can we replace $M_i (z_i + z_k)$ with $M_{ik} z_k$?  Now that we have constraints~\eqref{eq:bigM_select_exactly_one_neighbor_2}, which effectively set the LHS of \eqref{eq:bigM_constraint_reinsertion} to $\epsilon$ if point $i$ is deemed an outlier ($z_i=1$), there is no reason to include $M_{ik} z_i$ on the RHS of \eqref{eq:bigM_constraint_reinsertion} as well. 
\item What is the set $\mc{IK}$ doing?  What is its purpose?  Given that the distance metric is fixed,
for any pair of points $(i,k): i \in \mc{N}, k \in \bar{\mc{C}}_i$, if 
$$
\min\{ d_{ij} : j \in \mc{C}_i \backslash \mc{O} \} + \epsilon \leq d_{ik}
$$
which holds if and only if 
\begin{equation} \label{eq:reinsertion_existence_condition}
\exists j \in \mc{C}_i \backslash \mc{O} : d_{ij} + \epsilon \leq d_{ik}~,
\end{equation}
then the corresponding constraint~\eqref{eq:bigM_constraint_reinsertion} is already satisfied (and will continue to be satisfied once outliers are considered) and is therefore redundant.
\item Is it really worth the trouble to create the set $\mc{IK}$? Won't the solver take care of this?
While solvers are good at eliminating redundant constraints,
it is best to help them eliminate constraints a priori especially when we can immediately identify them.
This saves the solver time when building the optimization model and in preprocessing. 
Example: Suppose there are 10 classes, 100 points per class, for a total of 1000 points.
For simplicity, suppose there are 3 outliers per class (that is, our algorithm has thus far identified 3 outliers per class so that $|\mc{O}|=30$).
There are 900,000 constraints that must be included if constraints~\eqref{eq:bigM_constraint_reinsertion} are written ``$\forall i \in \mc{N}, k \in \bar{\mc{C}}_i$'' since, for every point $i$ (of which there are 1,000), there are 900 non-neighbors.  However, if we were to replace ``$\forall i \in \mc{N}, k \in \bar{\mc{C}}_i$'' with $\forall (i,k) \in \mc{IK}$, then at least 846,810 (94\%) of the constraints of type \eqref{eq:bigM_constraint_reinsertion} can be eliminated before doing a single optimization. Why? In this example, there are 970 non-outliers, each of which has $9 \times 97$ non-neighbors that are not outliers.  These 846,810 pairs of points have already been shown to satisfy constraints~\eqref{eq:bigM_constraint_reinsertion} to arrive at the current distance metric.  We write ``at least'' because there are likely many other pairs of points involving outliers (i.e., $k \in \mc{O}$) for which the condition \eqref{eq:reinsertion_existence_condition} also holds.  
\end{enumerate}

\subsection{AIMMS implementation}

In AIMMS, there are several items to be aware of.
First, define the set $\mc{IK}$ as follows: 
$$
\mc{IK} = \{ (i,k) | k \in \bar{\mc{C}}_i \texttt{ and not exists}( j \in \mc{C}_i \backslash \mc{O} | d_{ij} + \epsilon \leq d_{ik} ) \}
$$
Second, $z_i$ should only be defined for $i \in \mc{O}$.  You should \textit{not} define it for all $i \in \mc{N}$ and then set $z_i = 0$ for all $i \in \mc{N} \backslash \mc{O}$ as in \eqref{eq:reinsertion_not_needed_in_aimms}. 
Note that AIMMS understands that if $z_i$ appears in a constraint written for all $i \in \mc{N}$, it will only include it when $z_i$ exists.

Third, in summary, the following formulation should be used in AIMMS:
\begin{subequations} \label{model:milp_outlier_reinsertion_aimms}
\begin{alignat}{4}
\min_{\v{y},\v{z}}~~& \rho \sum_{i \in \mc{O}} z_i & & \\
\st~~& \sum_{j \in \mc{C}_i} d_{ij}y_{ij} + \epsilon \leq d_{ik} + M_{ik} z_k  && \qquad \forall (i,k) \in \mc{IK} \label{eq:bigM_constraint_reinsertion_improved} \\
    & \sum_{j \in \mc{C}_i} y_{ij} = 1 - z_i && \qquad \forall i \in \mc{N}, j \in \mc{C}_i \label{eq:bigM_select_exactly_one_neighbor_3} \\
    & y_{ij} \leq 1 - z_j && \qquad \forall i \in \mc{N}, j \in \mc{C}_i \cap \mc{O} \\
    & y_{ij} \in \{0,1\} && \qquad \forall i \in \mc{N}, j \in \mc{C}_i \\
    & z_{i} \in \{0,1\} && \qquad \forall i \in \mc{O}
\end{alignat}
\end{subequations}

\end{document}

### 2016-12-27 icml2017/paper.tex
add

@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{TODO2}
+\icmltitlerunning{A Novel Approach to Supervised Classification Using Non-Linear Metrics}
 
@@
 \twocolumn[
-\icmltitle{TODO}
+\icmltitle{A Novel Approach to Supervised Classification Using Non-Linear Metrics}
 
@@
 % package.
-\icmlauthor{Your Name}{email@yourdomain.edu}
-\icmladdress{Your Fantastic Institute,
-            314159 Pi St., Palo Alto, CA 94306 USA}
-\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
-\icmladdress{Their Fantastic Institute,
-            27182 Exp St., Toronto, ON M6H 2T1 CANADA}
+\icmlauthor{Krishnan Kumaran, Dimitri Papageorgiou, Francisco Trespalacios}{[krisnan.kumaran,dimitri.j.papageorgiou,francisco.trespalacios]@exxonmobil.com}
+\icmladdress{ExxonMobil Corporate Strategic Research,
+            1545 US 22 East, Annandale, NJ 08801 USA}
+\icmlauthor{Martin Takac, Bolun Xu}{[mat614,bo215]@lehigh.edu}
+\icmladdress{Industrial and Systems Eng., Lehigh University
+            200 West Packer Avenue, Bethlehem, 18015}
 
@@
 \begin{abstract} 
-TODO
+Clustering (also known as unsupervised classification) and Classification (commonly understood to be supervised,
+ i.e. based on training data) are common ways of performing data analysis to achieve a range of objectives like 
+anomaly detection and diagnosis, data segmentation and model development/refinement. Consequently, there is a 
+large body of research on these topics (see for example\cite{Hastie} and references therein for a survey of 
+currently used methods) offering different solutions ranging from K-means, spectral methods and other more 
+complex methods for Clustering, and Support Vector Machines (SVM), Artificial(Deep/Shallow) Neural Networks (ANN), their 
+non-linear Kernel-based variants and others for Classification.
+
+In previous work, we developed clustering methods [see 2012 US patent \cite{KKpatent}] which  extend an existing 
+technique known as Agglomerative Clustering using a trade-off curve to automatically select the optimal 
+number of clusters in a consistent manner from the data, a capability not available among other commonly 
+used clustering algorithms like K-means. Like all clustering methods, however, this method requires the 
+choice of a similarity/distance metric between the data points, and while there are typically a few 
+reasonable choices for most data, the results can depend strongly on this choice.
+
+In this work, we extend the concepts behind agglomerative clustering to a supervised classification 
+method aimed at learning the optimal distance/similarity metric directly from training data. The main advantages of
+this form of Supervised Classification, as compared to current state-of-the-art methods (Deep Neural Networks, SVM etc.) are
+\begin{itemize}
+\item{The formulation accommodates multiple disjoint ``islands'' belonging to the same user-specified class, since
+the classification criterion is based on distances to nearest co-class/non-class neighbors. This is a crucial property
+to enable accurate classification while allowing for sufficiently simple metrics that do not require all examples of each
+class to be forced into a single compact region of the transformed space defined by the metric. It also automatically builds
+robustness of classification performance to substantial diversity within user-defined classes, which is often a reality in most practical applications.}
+\item{Another key advantage of our method is that the mis-classifications with the optimally computed metric provide guidelines
+for new data acquisition and data quality control to improve classification performance.
+This is a key ``value-of-information'' criterion that can significantly improve both classification performance and computational burden by ensuring training data completeness, representativeness and economy, which are not adequately addressed in current applications of DNN and other methods which often depend on
+very large quantities of training data (e.g. internet cat images).}
+\end{itemize}
+
+Finally, the metric learning process can be formulated as an optimization problem (Mixed-Integer Linear Program, or MILP, 
+in its simplest form) that can be hard to solve for realistic data sizes, but we present fast and parallelizable methods to compute the optimal metric.
+We demonstrate classification and computational performance of the algorithms through several simple and intuitive examples.
 \end{abstract}
 
-\section{Introduction and Motivation}
+\section{Introduction}  
+Supervised Classification is one of the most commonly used Machine Learning paradigms both in the industry and academic research. There is a large body of past and continuing research on the topic
 
@@
 
-\section{Algorithm}
+\section{Motivation}
+
+\section{Illustration Examples}
+
+\section{Mathematical Formulation}
+
+\section{Algorithm / Work Flow}
 
 \section{Numerical Experiments/Results}
+
+\subsection{NN comparison}
+
+\subsection{Economy of data collection}
+
+DNN - > autoencoders
 

### 2016-12-28 python/p.py
add

@@ -1,0 +1,47 @@
+from __future__ import division
+from pyomo.environ import *
+
+
+def createDefaultModel():
+	model = ConcreteModel()
+
+	model.x = Var([1,2], domain=NonNegativeReals)
+
+	model.OBJ = Objective(expr = model.x[1] + model.x[2])
+	
+	return model
+ 
+
+
+
+
+for j in xrange(20):
+
+	model = createDefaultModel()
+
+	model.Constraint1 = Constraint(expr =  model.x[1] * model.x[2] >= 1)
+
+	opt = SolverFactory("cplex")
+
+	results = opt.solve(model)
+
+
+	print(results)
+
+	print "-------------------"
+	print(model.x.display())
+	print "-------------------"
+
+ 
+print(model.display())
+
+print "-------------------"
+
+
+for j in model.x:
+ 
+	print model.x[j].value
+
+
+
+

### 2016-12-28 tensorflow/09_convolutional_autoencoder.py
add

@@ -151,7 +151,7 @@ def test_mnist():
     # %%
     # Fit all training data
     batch_size = 100
-    n_epochs = 20 #10
+    n_epochs = 5 #10
     for epoch_i in range(n_epochs):
         for batch_i in range(mnist.train.num_examples // batch_size):
             batch_xs, _ = mnist.train.next_batch(batch_size)

### 2016-12-30 python/OurMethod/src/FindMaxEp.py
add

@@ -1,0 +1,87 @@
+'''
+Created 
+
+@author: Bolun
+'''
+from __future__ import division
+from pyomo.environ import *
+
+def loadData(filename):
+    labels = [0, 0,  1, 1]  
+    features = [ [0, 1],[.1, 0.8 ],[.1, -.9 ],[-0.2, 0.01 ] ]
+    return labels, features  
+
+
+def createModelForFidingEpMax(labels, features):
+    
+    model = ConcreteModel()
+
+    dimension = len(features[0])
+    
+    n = len(labels)
+    
+    # Define Matix B
+    for i in xrange(dimension):
+        for j in xrange(dimension):
+            model.B[i][j] = Var(within=Reals, initialize=0)
+            
+    # Define Distance[i,j]
+    for i in xrange(n):
+        for j in xrange(n):
+            model.d[i,j] = Var(within=NonNegativeReals,bounds=(0,1))
+   
+    model.Epsilon = Var(within=NonNegativeReals, bounds=(0,1), initialize=0)
+
+    model.OBJ = model.Epsilon
+ 
+
+
+
+    # this is constraint (11b)
+    for i in xrange(n):
+        myLabel = labels[i]
+        for k in xrange(n):
+            if (i != k) and(labels[k] != myLabel) :
+                model.Constraint11b[i,k] = Constraint(expr =  model.Epsilon <= model.d[i,k])
+            else:
+                model.Constraint11b[i,k] = Constraint(expr =  0 <= 0)
+                
+    # this is constraint (8b)                
+    for i in xrange(n):
+        for j in xrange(n):
+                model.Constraint11b[i,j] = Constraint(expr =  model.Epsilon <= model.d[i,k])
+
+    
+        
+        
+        
+
+
+    
+    return model
+
+
+def test(labels, features):
+ 
+ 
+ 
+ 
+    model = createModelForFidingEpMax(labels, features)
+
+ 
+
+
+    opt = SolverFactory("cplex")
+    solver_manager = SolverManagerFactory('neos')
+    results = solver_manager.solve(model,opt=opt)
+
+
+    print(results)
+
+
+    print(model.display())
+    
+    print "-------------------"
+    
+labels, features = loadData("doesnt matter")    
+test(labels, features)

### 2016-12-30 python/OurMethod/src/test.py

@@ -1,0 +1,24 @@
+'''
+
+
+@author: Bolun
+'''
+labels = [ 0, 0, 1, 1]
+features = [ [0, 1],[.1, 1.1 ],[.1, 2.1 ],[-2, 2.01 ] ]
+dimension = len(features[0])
+    
+print dimension
+print features[1][0]
+
+for i in xrange(0,dimension):
+    print i
+    
+    def c11bRule(model,labels,i,k):
+    n = len(labels)
+    for i in xrange(n):
+        myLabel = labels[i]
+        for k in xrange(n):
+            if labels[k] != myLabel:
+                return 0 <= 0
+            
+    return model.x[i,k,v] <= model.a[i,k]*model.y[i]

### 2017-01-03 python/OurMethod/src/Experiment.py
make python to work

@@ -1,0 +1,30 @@
+from __future__ import division
+
+from OutlierDetection import *
+
+
+
+
+
+od = OutlierDetection('dataset2.txt' )    
+
+epsilonMax, B, D, results, model = od.findLargestEpsilon()
+
+print "Epsilon max = ", epsilonMax
+print 'Matrix B is \n', B
+print "Matrix D is  \n ", D
+
+#print "--------------------"    
+#print(results)
+#print(model.display())
+
+ 
+epsilon = epsilonMax*0.5
+B, D,t, outliers, results, model = od.findDistanceBandSetOfOutliersForEpsilon(epsilon)
+print 'Matrix B is \n', B
+print "Matrix D is  \n ", D
+print "vector t is  \n ", t
+print "outliers: ",outliers
+
+
+

### 2017-01-03 python/OurMethod/src/OutlierDetection.py

@@ -1,0 +1,181 @@
+from pyomo.environ import *
+import numpy as np
+import math
+
+#https://github.com/Pyomo/PyomoGallery/blob/master/network_interdiction/multi_commodity_flow/multi_commodity_flow_interdict.py
+
+    
+
+def solveModel(model):
+        opt = SolverFactory("cplex")
+        solver_manager = SolverManagerFactory('neos')
+        results = solver_manager.solve(model, opt=opt)
+        return results
+
+
+
+
+class OutlierDetection:
+
+    EPS_M = 0.000001
+    def getMatrixDFromResult(self,model):
+        D=np.zeros((self.n, self.n))
+        for i in model.N:
+            for j in model.N:
+                D[i,j] = model.D[(i,j)].value
+        return D
+
+
+
+    def getMatrixBFromResult(self,model):
+        B=np.zeros((self.d, self.d))
+        for i in model.d:
+            for j in model.d:
+                if i==j:
+                    B[i,j] = model.B[(i,j)].value
+                if i>j:
+                    B[i,j] =0.5* model.B[(i,j)].value    
+                    B[j,i] = B[i,j]
+        return B
+
+    
+
+
+    def __init__(self, filename ):
+
+        self.labels = []  
+        self.features = []
+        f = open(filename,'rU')
+        for line in f:
+            data =  line.split(':')
+            self.labels+=[ int(data[0]) ]
+            self.features+=[  [float(xi) for xi in data[1].split() ]              ]
+            
+        #centralize data TODO    
+            
+        #normalizeData
+        M = 0
+        for sample in self.features:
+                normi = sum(xi*xi for xi in sample)
+                M = max(M,normi)
+        M = math.sqrt(M)        
+        self.features = [   [ xi/M for xi in sample  ]        for sample in self.features  ]
+            
+        self.n = len(self.labels)
+        self.nonOutlier = range(self.n)
+        self.outlier = []
+        self.d = len(self.features[0])
+
+
+    def addConstraint_d_ij_as_function_of_features_and_B(self,model):
+        #relation between B and D
+        def distanceBetweenPointGivenB(model, i,j):
+            xi = self.features[i]
+            xj = self.features[j]
+            x = [  (xi[k]-xj[k]) for k in xrange(self.d) ]
+            return ( model.D[(i,j)] ==   sum(  x[k]*x[l]* model.B[(k,l)]      for k in model.d for l in model.d   )      )
[…]

### 2017-01-03 icml2017/paper.tex
Add

@@
 
+\usepackage{xargs}                      % Use more than one optional parameter in a new commands
+\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
+% 
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
+\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
+\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
+\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
+\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
+\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
+
 % The \icmltitle you define below is probably too long as a header.
@@
 \begin{abstract}
+
+\end{abstract}
+
+\section{Introduction}
+
+\todo[inline,color=red]{This is original abstract,
+however, abstract should be just a few lines}
+
 Clustering (also known as unsupervised classification) and Classification (commonly understood to be supervised,
@@
 We demonstrate classification and computational performance of the algorithms through several simple and intuitive examples.
-\end{abstract}
 
@@
 
-\paragraph{Contributions.}
+\todo[inline,color=green]{Explain very clearly what we want to do and why it is important.
 
-\section{Motivation}
+mention
 
-\section{Illustration Examples}
+-clustering
+
+-better NN search
+
+-outlier detection
+
+-where to sample new data
+
+}
+
+\paragraph{Brief Literature Review.}
+
+\cite{weinberger2005distance}
+
+\cite{xing2003distance}
+
+\cite{weinberger2009distance}
+
+\cite{yang2006efficient}
+
+\cite{ying2012distance}
+
+\cite{schultz2004learning}
+
+\cite{rosales2006learning}
+
+\paragraph{Our Contributions.}
+
+\section{Motivation \& Illustration Examples}
 

### 2017-01-03 python/OurMethod/src/Experiment.py

@@ -6,7 +6,11 @@ from OutlierDetection import *
 
 
 
-od = OutlierDetection('dataset2.txt' )    
+od = OutlierDetection('dataset3.txt2' , True)    
+# od = OutlierDetection('50_c2_d2.txt' , False)    
+
+
+
 
 epsilonMax, B, D, results, model = od.findLargestEpsilon()
 

### 2017-01-03 python/OurMethod/src/OutlierDetection.py

@@ -1,15 +1,22 @@
 from pyomo.environ import *
 import numpy as np
 import math
-
+import time
 #https://github.com/Pyomo/PyomoGallery/blob/master/network_interdiction/multi_commodity_flow/multi_commodity_flow_interdict.py
 
     
 
 def solveModel(model):
         opt = SolverFactory("cplex")
-        solver_manager = SolverManagerFactory('neos')
-        results = solver_manager.solve(model, opt=opt)
+        
+        print "-------------Going to solve the model-------------"
+#         solver_manager = SolverManagerFactory('neos')
+#         results = solver_manager.solve(model, opt=opt)
+        
+        results = opt.solve(model)
+        print(results)
+        print "-------------Model solved-------------"
+        
         return results
 
 
@@ -41,7 +48,7 @@ class OutlierDetection:
     
 
 
-    def __init__(self, filename ):
+    def __init__(self, filename ,normalize):
 
         self.labels = []  
         self.features = []
@@ -54,13 +61,14 @@ class OutlierDetection:
         #centralize data TODO    
             
         #normalizeData
-        M = 0
-        for sample in self.features:
-                normi = sum(xi*xi for xi in sample)
-                M = max(M,normi)
-        M = math.sqrt(M)        
-        self.features = [   [ xi/M for xi in sample  ]        for sample in self.features  ]
-            
+        if normalize:
+            M = 0
+            for sample in self.features:
+                    normi = sum(xi*xi for xi in sample)
+                    M = max(M,normi)
+            M = math.sqrt(M)
+            self.features = [   [ xi/M for xi in sample  ]        for sample in self.features  ]
+
         self.n = len(self.labels)
         self.nonOutlier = range(self.n)
         self.outlier = []
@@ -74,7 +82,13 @@ class OutlierDetection:
             xj = self.features[j]
             x = [  (xi[k]-xj[k]) for k in xrange(self.d) ]
             return ( model.D[(i,j)] ==   sum(  x[k]*x[l]* model.B[(k,l)]      for k in model.d for l in model.d   )      )
+        
+        print "SSSSSSSSSSSSS"
+        start_time = time.time()
         model.distanceBetweenPointGivenBConstrain = Constraint(model.N*model.N, rule=distanceBetweenPointGivenB)
+        elapsed_time = time.time() - start_time
+        
+        print "XXXXXXXXXXXx",elapsed_time
 
     def addConstraint_lower_diagonal_of_B_is_zero(self,model):
[…]

### 2017-01-03 tensorflow/09_convolutional_autoencoder.py

@@ -8,7 +8,6 @@ import math
 from libs.activations import lrelu
 from libs.utils import corrupt
 
-
 # %%
 def autoencoder(input_shape=[None, 784],
                 n_filters=[1, 10, 10, 10, 10],
@@ -151,9 +150,13 @@ def test_mnist():
     # %%
     # Fit all training data
     batch_size = 100
-    n_epochs = 5 #10
+    n_epochs = 20
     for epoch_i in range(n_epochs):
+        print epoch_i
+#     for epoch_i in range(2):
         for batch_i in range(mnist.train.num_examples // batch_size):
+#         for   batch_i in range( 1):
+            print batch_i
             batch_xs, _ = mnist.train.next_batch(batch_size)
             train = np.array([img - mean_img for img in batch_xs])
             sess.run(optimizer, feed_dict={ae['x']: train})
@@ -161,22 +164,48 @@ def test_mnist():
 
     # %%
     # Plot example reconstructions
-    n_examples = 20
-    test_xs, _ = mnist.test.next_batch(n_examples)
-    test_xs_norm = np.array([img - mean_img for img in test_xs])
-    recon = sess.run(ae['y'], feed_dict={ae['x']: test_xs_norm})
-    print(recon.shape)
-    fig, axs = plt.subplots(2, n_examples, figsize=(10, 2))
-    for example_i in range(n_examples):
-        axs[0][example_i].imshow(
-            np.reshape(test_xs[example_i, :], (28, 28)))
-        axs[1][example_i].imshow(
-            np.reshape(
-                np.reshape(recon[example_i, ...], (784,)) + mean_img,
-                (28, 28)))
-    fig.show()
-    plt.draw()
-    plt.waitforbuttonpress()
+    
+    fo = open('../python/OurMethod/src/dataset3.txt','w')
+    foi = open('../python/OurMethod/src/dataset3_images.txt','w')
+    
+    for k in xrange(10):
+        print k
+        n_examples = 64
+        test_xs, test_ys = mnist.test.next_batch(n_examples)
+        
+        test_xs_norm = np.array([img - mean_img for img in test_xs])
+        recon = sess.run(ae['y'], feed_dict={ae['x']: test_xs_norm})
+        
+        reconZ = sess.run(ae['z'], feed_dict={ae['x']: test_xs_norm})
+        
+        
+        for sj in xrange(n_examples):
+            out=[]
+            for i in   reconZ[sj]:
+                for j in i:
+                    for k in j:
[…]

### 2017-01-03 python/OurMethod/src/Experiment.py
add

@@ -6,10 +6,8 @@ from OutlierDetection import *
 
 
 
-od = OutlierDetection('dataset3.txt2' , True)    
-# od = OutlierDetection('50_c2_d2.txt' , False)    
-
-
+# od = OutlierDetection('dataset3.txt2' , True)    
+od = OutlierDetection('50_c2_d2.txt' , False)    
 
 
 epsilonMax, B, D, results, model = od.findLargestEpsilon()
@@ -29,6 +27,22 @@ print 'Matrix B is \n', B
 print "Matrix D is  \n ", D
 print "vector t is  \n ", t
 print "outliers: ",outliers
+
+
+# remove outliers and resolve
+
+# start adding points ....  MIP / R_i greeedy / Random insertion
+
+
+
+
+
+
+
+
+
+
+
 
 
 

### 2017-01-03 python/OurMethod/src/NN.py

@@ -1,0 +1,22 @@
+
+
+
+
+#load the data
+
+#training
+#testing data
+
+
+k = 3 #(I will find 3 closed points)
+
+
+# run NN
+# find out how many points in testing are wrongly classified
+
+
+
+
+
+
+

### 2017-01-03 python/OurMethod/src/OutlierDetection.py

@@ -57,7 +57,7 @@ class OutlierDetection:
             data =  line.split(':')
             self.labels+=[ int(data[0]) ]
             self.features+=[  [float(xi) for xi in data[1].split() ]              ]
-            
+        f.close()
         #centralize data TODO    
             
         #normalizeData
@@ -106,38 +106,25 @@ class OutlierDetection:
         # ------------------  definition of sets        
         model.N = Set(initialize=self.nonOutlier, doc='Set of nodes')
         model.d = Set(initialize=range(self.d), doc='Set of features')
-
         # ------------------  definition of variables        
         model.D = Var(model.N * model.N, domain=NonNegativeReals, bounds=(0, 1)) 
-        model.eps = Var(within=NonNegativeReals, bounds=(0, 1), initialize=0)
+        model.eps = Var(within=NonNegativeReals,  initialize=0) #bounds=(0, 1),
         model.B = Var(model.d * model.d   ) #,bounds=(-1, 1) 
-
-
-
         # ------------------  Constraints        
         def epsLessThanDij(model, i,j):
             if self.labels[i] == self.labels[j]:
                 return Constraint.Skip
             else:
                 return ( model.eps <= model.D[(i,j)]   )
-            
-            
         model.epsLessThanDikConstrain = Constraint(model.N*model.N, rule=epsLessThanDij)
-
-        
         self.addConstraint_lower_diagonal_of_B_is_zero(model)
-
         self.addConstraint_d_ij_as_function_of_features_and_B(model)
-
         # ------------------  Objective Function        
         model.OBJ = Objective(expr=model.eps, sense=maximize, doc='maximize epsilon')
         # ------------------  Solve Problem        
-
         results = solveModel(model)
-        
         B = self.getMatrixBFromResult(model)
         D = self.getMatrixDFromResult(model)
-        
         return model.eps.value, B, D, results, model
 
 
@@ -146,17 +133,14 @@ class OutlierDetection:
 
     def findDistanceBandSetOfOutliersForEpsilon(self,epsilon):
         self.epsilon = epsilon
-        
         model = ConcreteModel()
         # ------------------  definition of sets        
         model.N = Set(initialize=self.nonOutlier, doc='Set of nodes')
         model.d = Set(initialize=range(self.d), doc='Set of features')
-
         # ------------------  definition of variables        
[…]

### 2017-01-03 python/OurMethod/src/SVM.py

@@ -1,0 +1,22 @@
+
+
+
+
+#load the data
+
+#training
+#testing data
+
+
+#kernel 0-nothing   1-linear  2- gausian  .....
+
+ 
+# run SVM.....
+# find out how many points in testing are wrongly classified
+
+
+
+
+
+
+

### 2017-01-04 python/OurMethod/src/Experiment.py
add

@@ -13,8 +13,8 @@ od = OutlierDetection('50_c2_d2.txt' , False)
 epsilonMax, B, D, results, model = od.findLargestEpsilon()
 
 print "Epsilon max = ", epsilonMax
-print 'Matrix B is \n', B
-print "Matrix D is  \n ", D
+# print 'Matrix B is \n', B
+# print "Matrix D is  \n ", D
 
 #print "--------------------"    
 #print(results)
@@ -22,16 +22,48 @@ print "Matrix D is  \n ", D
 
  
 epsilon = epsilonMax*0.5
-B, D,t, outliers, results, model = od.findDistanceBandSetOfOutliersForEpsilon(epsilon)
-print 'Matrix B is \n', B
-print "Matrix D is  \n ", D
-print "vector t is  \n ", t
-print "outliers: ",outliers
+t, outliers, results, model = od.findDistanceBandSetOfOutliersForEpsilon(epsilon)
+print "we have ",len(outliers), "outliers: ",outliers
 
 
-# remove outliers and resolve
+notFinished = True
+iteration = 0
+while notFinished:
+    # remove outliers and resolve
+    
+    print "\n\n Iteration ",iteration 
+    
+    od.setOutlierList(outliers)
+    print od.outliers
+    print od.nonOutlier
+    notFinished = od.insertOutliers_Method_CyclicAssignment()
+#     TODO: Bolun, please try to implement this two functions
+#     outliers = insertOutliers_Method_Ri_Assignment()   
+#     outliers = insertOutliers_Method_MIP_Assignment()
 
-# start adding points ....  MIP / R_i greeedy / Random insertion
+    print od.outliers
+    print od.nonOutlier
+
+    if notFinished:
+        # what model do we solve to re-optimize B and D???? I am not sure about this step
+        print od.B
+        epsilonMax, B, D, results, model = od.findLargestEpsilon()
+        print "Epsilon max = ", epsilonMax
+        epsilon = epsilonMax*0.5
+        t, outliersNEW, results, model = od.findDistanceBandSetOfOutliersForEpsilon(epsilon)
+        outliers+=outliersNEW
+        print "we have ",len(outliersNEW), "outliers: ",outliersNEW
+        print "all outliers ",len(outliers)," : ",outliers
+        print od.B
+    
+    iteration=iteration+1
+    
+    
+    
+
+
+
+# start adding points ....   R_i greeedy / Random insertion / MIP 
 
 
 

### 2017-01-04 python/OurMethod/src/OutlierDetection.py

@@ -9,13 +9,13 @@ import time
 def solveModel(model):
         opt = SolverFactory("cplex")
         
-        print "-------------Going to solve the model-------------"
-#         solver_manager = SolverManagerFactory('neos')
-#         results = solver_manager.solve(model, opt=opt)
+#         print "-------------Going to solve the model-------------"
+        solver_manager = SolverManagerFactory('neos')
+        results = solver_manager.solve(model, opt=opt)
         
-        results = opt.solve(model)
-        print(results)
-        print "-------------Model solved-------------"
+#         results = opt.solve(model)
+#         print(results)
+#         print "-------------Model solved-------------"
         
         return results
 
@@ -83,12 +83,9 @@ class OutlierDetection:
             x = [  (xi[k]-xj[k]) for k in xrange(self.d) ]
             return ( model.D[(i,j)] ==   sum(  x[k]*x[l]* model.B[(k,l)]      for k in model.d for l in model.d   )      )
         
-        print "SSSSSSSSSSSSS"
-        start_time = time.time()
-        model.distanceBetweenPointGivenBConstrain = Constraint(model.N*model.N, rule=distanceBetweenPointGivenB)
-        elapsed_time = time.time() - start_time
-        
-        print "XXXXXXXXXXXx",elapsed_time
+#         start_time = time.time()
+        model.distanceBetweenPointGivenBConstrain = Constraint(model.NAll*model.NAll, rule=distanceBetweenPointGivenB)
+#         elapsed_time = time.time() - start_time
 
     def addConstraint_lower_diagonal_of_B_is_zero(self,model):
         #matrix B will be zero under diagonal
@@ -103,11 +100,12 @@ class OutlierDetection:
     def findLargestEpsilon(self):
         
         model = ConcreteModel()
-        # ------------------  definition of sets        
+        # ------------------  definition of sets
         model.N = Set(initialize=self.nonOutlier, doc='Set of nodes')
-        model.d = Set(initialize=range(self.d), doc='Set of features')
+        model.NAll = Set(initialize=range(self.n), doc='Set of nodes')
+        model.d = Set(initialize=range(self.d), doc='Set of features')        
         # ------------------  definition of variables        
-        model.D = Var(model.N * model.N, domain=NonNegativeReals, bounds=(0, 1)) 
+        model.D = Var(model.NAll * model.NAll, domain=NonNegativeReals, bounds=(0, 1)) 
[…]

### 2017-01-04 python/OurMethod/src/Experiment.py
add

@@ -44,17 +44,17 @@ while notFinished:
     print od.outliers
     print od.nonOutlier
 
-    if notFinished:
-        # what model do we solve to re-optimize B and D???? I am not sure about this step
-        print od.B
-        epsilonMax, B, D, results, model = od.findLargestEpsilon()
-        print "Epsilon max = ", epsilonMax
-        epsilon = epsilonMax*0.5
-        t, outliersNEW, results, model = od.findDistanceBandSetOfOutliersForEpsilon(epsilon)
-        outliers+=outliersNEW
-        print "we have ",len(outliersNEW), "outliers: ",outliersNEW
-        print "all outliers ",len(outliers)," : ",outliers
-        print od.B
+#     if notFinished:
+#         # what model do we solve to re-optimize B and D???? I am not sure about this step
+#         print od.B
+#         epsilonMax, B, D, results, model = od.findLargestEpsilon()
+#         print "Epsilon max = ", epsilonMax
+#         epsilon = epsilonMax*0.5
+#         t, outliersNEW, results, model = od.findDistanceBandSetOfOutliersForEpsilon(epsilon)
+#         outliers+=outliersNEW
+#         print "we have ",len(outliersNEW), "outliers: ",outliersNEW
+#         print "all outliers ",len(outliers)," : ",outliers
+#         print od.B
     
     iteration=iteration+1
     

### 2017-01-04 python/OurMethod/src/NN.py
add knn test

@@ -8,14 +8,68 @@
 #testing data
 
 
-k = 3 #(I will find 3 closed points)
+ #(I will find 3 closed points)
 
 
 # run NN
 # find out how many points in testing are wrongly classified
 
 
-
+#########################################  
+# kNN: k Nearest Neighbors  
+  
+# Input:      newInput: vector to compare to existing dataset (1xN)  
+#             dataSet:  size m data set of known vectors (NxM)  
+#             labels:   data set labels (1xM vector)  
+#             k:        number of neighbors to use for comparison   
+              
+# Output:     the most popular class label  
+#########################################  
+  
+from numpy import *  
+import operator  
+  
+# create a dataset which contains 4 samples with 2 classes  
+def createDataSet():  
+    # create a matrix: each row as a sample  
+    group = array([[1.0, 0.9], [1.0, 1.0], [0.1, 0.2], [0.0, 0.1]])  
+    labels = ['A', 'A', 'B', 'B'] # four samples and two classes  
+    return group, labels  
+  
+# classify using kNN  
+def kNNClassify(newInput, dataSet, labels, k):  
+    numSamples = dataSet.shape[0] # shape[0] stands for the num of row  
+  
+    ## step 1: calculate Euclidean distance  
+    # tile(A, reps): Construct an array by repeating A reps times  
+    # the following copy numSamples rows for dataSet  
+    diff = tile(newInput, (numSamples, 1)) - dataSet # Subtract element-wise  
+    squaredDiff = diff ** 2 # squared for the subtract  
+    squaredDist = sum(squaredDiff, axis = 1) # sum is performed by row  
+    distance = squaredDist ** 0.5  
+  
+    ## step 2: sort the distance  
+    # argsort() returns the indices that would sort an array in a ascending order  
+    sortedDistIndices = argsort(distance)  
+  
+    classCount = {} # define a dictionary (can be append element)  
+    for i in xrange(k):  
+        ## step 3: choose the min k distance  
+        voteLabel = labels[sortedDistIndices[i]]  
+  
+        ## step 4: count the times labels occur  
+        # when the key voteLabel is not in dictionary classCount, get()  
+        # will return 0  
+        classCount[voteLabel] = classCount.get(voteLabel, 0) + 1  
+  
+    ## step 5: the max voted class will return  
+    maxCount = 0  
+    for key, value in classCount.items():  
+        if value > maxCount:  
+            maxCount = value  
+            maxIndex = key  
+  
+    return maxIndex   
 
 
 

### 2017-01-06 python/OurMethod/src/Experiment.py
add

@@ -2,18 +2,19 @@ from __future__ import division
 
 from OutlierDetection import *
 
+import pickle 
+filename = 'dataset_cifar2_sub2.txt'
+filename = 'dataset3.txt'
 
+od = OutlierDetection(filename , True)    
 
-
-
-# od = OutlierDetection('dataset3.txt2' , True)    
-od = OutlierDetection('50_c2_d2.txt' , False)    
+# od = OutlierDetection('50_c2_d2.txt' , False)    
 
 
 epsilonMax, B, D, results, model = od.findLargestEpsilon()
 
 print "Epsilon max = ", epsilonMax
-# print 'Matrix B is \n', B
+print 'Matrix B is \n', B
 # print "Matrix D is  \n ", D
 
 #print "--------------------"    
@@ -21,21 +22,35 @@ print "Epsilon max = ", epsilonMax
 #print(model.display())
 
  
-epsilon = epsilonMax*0.5
+epsilon = epsilonMax*0.01
 t, outliers, results, model = od.findDistanceBandSetOfOutliersForEpsilon(epsilon)
 print "we have ",len(outliers), "outliers: ",outliers
 
 
-notFinished = True
+od.setOutlierList(outliers)
+t, newoutliers, results, model = od.findDistanceBandSetOfOutliersForEpsilon(epsilon)
+print "we have ",len(newoutliers), "outliers: ",newoutliers
+outliers+=newoutliers
+print "at the end we have ", len(outliers),":",outliers
+
+
+data={}
+data["B"]=od.B
+data["outliers"]=outliers        
+pickle.dump( data, open( filename_+"0.pickle", "wb" ) ) 
+
+
+notFinished = True 
 iteration = 0
 while notFinished:
     # remove outliers and resolve
-    
     print "\n\n Iteration ",iteration 
     
+   
     od.setOutlierList(outliers)
     print od.outliers
     print od.nonOutlier
+    print "Insertion of outliers procedure    "
     notFinished = od.insertOutliers_Method_CyclicAssignment()
 #     TODO: Bolun, please try to implement this two functions
 #     outliers = insertOutliers_Method_Ri_Assignment()   
@@ -44,17 +59,20 @@ while notFinished:
     print od.outliers
     print od.nonOutlier
 
-#     if notFinished:
-#         # what model do we solve to re-optimize B and D???? I am not sure about this step
-#         print od.B
-#         epsilonMax, B, D, results, model = od.findLargestEpsilon()
-#         print "Epsilon max = ", epsilonMax
[…]

### 2017-01-06 python/OurMethod/src/OutlierDetection.py

@@ -10,11 +10,11 @@ def solveModel(model):
         opt = SolverFactory("cplex")
         
 #         print "-------------Going to solve the model-------------"
-        solver_manager = SolverManagerFactory('neos')
-        results = solver_manager.solve(model, opt=opt)
+#         solver_manager = SolverManagerFactory('neos')
+#         results = solver_manager.solve(model, opt=opt)
         
-#         results = opt.solve(model)
-#         print(results)
+        results = opt.solve(model)
+        print(results)
 #         print "-------------Model solved-------------"
         
         return results
@@ -27,8 +27,8 @@ class OutlierDetection:
     EPS_M = 0.000001
     def getMatrixDFromResult(self,model):
         D=np.zeros((self.n, self.n))
-        for i in model.N:
-            for j in model.N:
+        for i in model.NAll:
+            for j in model.NAll:
                 D[i,j] = model.D[(i,j)].value
         return D
 
@@ -83,10 +83,11 @@ class OutlierDetection:
             x = [  (xi[k]-xj[k]) for k in xrange(self.d) ]
             return ( model.D[(i,j)] ==   sum(  x[k]*x[l]* model.B[(k,l)]      for k in model.d for l in model.d   )      )
         
-#         start_time = time.time()
+        start_time = time.time()
+        print "Start "
         model.distanceBetweenPointGivenBConstrain = Constraint(model.NAll*model.NAll, rule=distanceBetweenPointGivenB)
-#         elapsed_time = time.time() - start_time
-
+        elapsed_time = time.time() - start_time
+        print "done D contsr", elapsed_time
     def addConstraint_lower_diagonal_of_B_is_zero(self,model):
         #matrix B will be zero under diagonal
         def lowerBisZero(model, i,j):
@@ -216,11 +217,34 @@ class OutlierDetection:
         for i in model.N:
             t[i] = model.t[(i)].value
         outliers=[]
-        for i in xrange(self.n):
-            m = 1000;
-            for j in xrange(self.n):
-                if  self.labels[i]==self.labels[j] and i<>j:
-                    m = min(m, self.D[i,j])
-            if m > t[i]+self.EPS_M:
-                outliers+=[i]        
+#         for i in xrange(self.n):
+#             m = 1000;
+#             for j in xrange(self.n):
+#                 if  self.labels[i]==self.labels[j] and i<>j:
+#                     m = min(m, self.D[i,j])
+#             if m > t[i]+self.EPS_M:
[…]

### 2017-01-06 python/OurMethod/src/plots.py

@@ -1,0 +1,36 @@
+import tensorflow as tf
+import numpy as np
+import math
+import pickle 
+from xml.sax.handler import feature_external_ges
+import tensorflow as tf
+import tensorflow.examples.tutorials.mnist.input_data as input_data
+import matplotlib.pyplot as plt
+
+print "test"
+
+
+data=[]
+f = open("dataset_cifar_images2.txt")
+for line in f:
+    data += [line]
+
+#[7, 35, 64, 71, 73, 81]
+
+
+pic = data[12]
+pic = np.array([float(x) for x in pic.split()])
+print pic
+
+pic2 = np.reshape(pic, (32,32,3), order='F')
+pic2 = pic.reshape(3,32,32).transpose(1,2,0)
+     
+imgplot = plt.imshow(pic2)  
+ 
+plt.draw()   
+#fig.show()
+#
+plt.waitforbuttonpress()
+
+
+

### 2017-01-06 tensorflow/CFIAR_09_convolutional_autoencoder.py

@@ -1,0 +1,243 @@
+"""Tutorial on how to create a convolutional autoencoder w/ Tensorflow.
+
+Parag K. Mital, Jan 2016
+"""
+import tensorflow as tf
+import numpy as np
+import math
+from libs.activations import lrelu
+from libs.utils import corrupt
+import pickle 
+from xml.sax.handler import feature_external_ges
+import tensorflow as tf
+import tensorflow.examples.tutorials.mnist.input_data as input_data
+import matplotlib.pyplot as plt
+
+# %%
+def autoencoder(input_shape=[None, 3072],
+                n_filters=[3, 4, 4, 4 ],
+                filter_sizes=[3, 3, 3, 3 ],
+                corruption=False):
+    """Build a deep denoising autoencoder w/ tied weights.
+
+    Parameters
+    ----------
+    input_shape : list, optional
+        Description
+    n_filters : list, optional
+        Description
+    filter_sizes : list, optional
+        Description
+
+    Returns
+    -------
+    x : Tensor
+        Input placeholder to the network
+    z : Tensor
+        Inner-most latent representation
+    y : Tensor
+        Output reconstruction of the input
+    cost : Tensor
+        Overall cost to use for training
+
+    Raises
+    ------
+    ValueError
+        Description
+    """
+    # %%
+    # input to the network
+    x = tf.placeholder(
+        tf.float32, input_shape, name='x')
+
+
+    # %%
+    # ensure 2-d is converted to square tensor.
+    if len(x.get_shape()) == 2:
+        x_dim = 32
+        x_tensor = tf.reshape(
+            x, [-1, x_dim, x_dim, n_filters[0]])
+    elif len(x.get_shape()) == 4:
+        x_tensor = x
+    else:
+        raise ValueError('Unsupported input dimensions')
+    current_input = x_tensor
+
+    # %%
+    # Optionally apply denoising autoencoder
+    if corruption:
+        current_input = corrupt(current_input)
+
+    # %%
+    # Build the encoder
+    encoder = []
+    shapes = []
+    for layer_i, n_output in enumerate(n_filters[1:]):
+        n_input = current_input.get_shape().as_list()[3]
+        shapes.append(current_input.get_shape().as_list())
+        print shapes 
+        W = tf.Variable(
+            tf.random_uniform([
+                filter_sizes[layer_i],
[…]

### 2017-01-06 tensorflow/MNIST_09_convolutional_autoencoder.py

@@ -1,0 +1,213 @@
+"""Tutorial on how to create a convolutional autoencoder w/ Tensorflow.
+
+Parag K. Mital, Jan 2016
+"""
+import tensorflow as tf
+import numpy as np
+import math
+from libs.activations import lrelu
+from libs.utils import corrupt
+
+# %%
+def autoencoder(input_shape=[None, 784],
+                n_filters=[1, 10, 10, 10, 10],
+                filter_sizes=[3, 3, 3, 3, 3],
+                corruption=False):
+    """Build a deep denoising autoencoder w/ tied weights.
+
+    Parameters
+    ----------
+    input_shape : list, optional
+        Description
+    n_filters : list, optional
+        Description
+    filter_sizes : list, optional
+        Description
+
+    Returns
+    -------
+    x : Tensor
+        Input placeholder to the network
+    z : Tensor
+        Inner-most latent representation
+    y : Tensor
+        Output reconstruction of the input
+    cost : Tensor
+        Overall cost to use for training
+
+    Raises
+    ------
+    ValueError
+        Description
+    """
+    # %%
+    # input to the network
+    x = tf.placeholder(
+        tf.float32, input_shape, name='x')
+
+
+    # %%
+    # ensure 2-d is converted to square tensor.
+    if len(x.get_shape()) == 2:
+        x_dim = np.sqrt(x.get_shape().as_list()[1])
+        if x_dim != int(x_dim):
+            raise ValueError('Unsupported input dimensions')
+        x_dim = int(x_dim)
+        x_tensor = tf.reshape(
+            x, [-1, x_dim, x_dim, n_filters[0]])
+    elif len(x.get_shape()) == 4:
+        x_tensor = x
+    else:
+        raise ValueError('Unsupported input dimensions')
+    current_input = x_tensor
+
+    # %%
+    # Optionally apply denoising autoencoder
+    if corruption:
+        current_input = corrupt(current_input)
+
+    # %%
+    # Build the encoder
+    encoder = []
+    shapes = []
+    for layer_i, n_output in enumerate(n_filters[1:]):
+        n_input = current_input.get_shape().as_list()[3]
+        shapes.append(current_input.get_shape().as_list())
+        print shapes 
+        W = tf.Variable(
+            tf.random_uniform([
+                filter_sizes[layer_i],
+                filter_sizes[layer_i],
+                n_input, n_output],
[…]

### 2017-01-06 icml2017/paper.tex

@@
 \documentclass{article}
+\usepackage{amsmath}
+
+\newcommand{\mc}{\mathcal}
+
+\def\st{{\rm s.t.}}
 
@@
 \newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
+
+\renewcommand{\v}[1]{{{#1}}} %\mathbf  2  \ensuremath
+
+\newcommand{\vell}{\boldsymbol{\ell}}
+\newcommand{\valpha}{\boldsymbol{\alpha}}
+\newcommand{\vbeta}{\boldsymbol{\beta}}
+\newcommand{\vgamma}{\boldsymbol{\gamma}}
+\newcommand{\vGamma}{\boldsymbol{\Gamma}}
+\newcommand{\vdelta}{\boldsymbol{\delta}}
+\newcommand{\vlambda}{\boldsymbol{\lambda}}
+\newcommand{\vLambda}{\boldsymbol{\Lambda}}
+\newcommand{\vxi}{\boldsymbol{\xi}}
+\newcommand{\vpi}{\boldsymbol{\pi}}
+
+\newcommand{\xor}{\underline{\vee}}
+\newcommand{\Xor}{\underline{\bigvee}}
 
@@
 
-\section{Introduction}  
+\paragraph{Introduction}  
 Supervised Classification is one of the most commonly used Machine Learning paradigms both in the industry and academic research. There is a large body of past and continuing research on the topic
@@
 
+\begin{itemize}
+\item derive LP formulation and procedure to improve metric
+\item propose algorithm to report outliers and suggest regions which needs more samples
+
+\item iterative algorithm for training NN ?????
+
+\item TODO
+\end{itemize}
+
+ \clearpage 
 \section{Motivation \& Illustration Examples}
 
+\subparagraph{Distance Learning}
+
+\subparagraph{Outlier Detection \& Further Sampling Recommendation}
+
+\subparagraph{Interactive Sampling Procedure}
+
+\clearpage
 \section{Mathematical Formulation}
 
+\begin{equation}
+\mc{F} = \{ (\v{a},\v{B},\v{d}) \in \Re^p \times \Re^{p \times p} \times \Re_+^{N \times N} : \v{B}~\text{symmetric}, d_{ij} = \v{a}^{\top}
+\vdelta_{ij} + \vdelta_{ij}^{\top} \v{B}\vdelta_{ij} \quad \forall i,j \in \mc{N} \}
+\end{equation}
+or
+\begin{subequations} \label{set:feasible_region_distance_metric}
+\begin{alignat}{4}
+%\mc{F} = \Bigg\{ \v{a},\v{B},\v{d} : &  &&  \\
+    & d_{ij} = \sum_{k=1}^p \delta_{ijk} a_{k} + %\sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N} \label{eq:distance_metric_def} \\
+%    & 0 \leq d_{ij} \leq 1 && \qquad \forall i,j \in \mc{N} \\
+ %   & \v{a} \in \Re^p && \\ 
+    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p \Bigg\}
+\end{alignat}
+\end{subequations}
+
+\begin{subequations} \label{model:epsilon_lp_1}
+\begin{alignat}{4}
+\max_{{a},{B},{d},\epsilon}~~& \epsilon &&  \\
+\st~~& \epsilon \leq d_{ik} && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \label{eq:epsilon_lp_separation_constr_t} \\
+    & \eqref{set:feasible_region_distance_metric} & & 
+\end{alignat}
+\end{subequations}
+Let $\epsilon^{\max}$ be the maximum non-neighbor separation, i.e., the optimal value of $\epsilon$ in \eqref{model:epsilon_lp_1}.
+
+Given $\epsilon \in (0,\epsilon^{\max}]$, model \eqref{model:1} can be expressed as a linear programming feasibility problem:
+\begin{subequations} \label{model:big_lp_1}
+\begin{alignat}{4}
+\max_{\v{a},\v{B},\v{d},\v{t}}~~& \sum_{i \in \mc{N}} t_i &&  \\
+\st~~& t_i + \epsilon \leq d_{ik} && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \label{eq:big_lp_separation_constr_t} \\
+    & t_i \leq d_{ij} && \qquad \forall i \in \mc{N}, j \in \mc{C}_i \label{eq:big_lp_dual_constr_t} \\
+    & t_i \geq 0 & & \qquad \forall i \in \mc{N} \\
+    & \eqref{set:feasible_region_distance_metric} & & 
+\end{alignat}
+\end{subequations}
+For $\epsilon \in (0,\epsilon^{\max}]$, model \eqref{model:big_lp_1} is always feasible since the origin $\v{0}$ is always feasible.
+Note that $t_i$ represents the distance to point $i$'s nearest neighbor since constraints \eqref{eq:big_lp_dual_constr_t} ensure that $t_i \leq \min_{j \in \mc{C}_i} d_{ij}$,
+while the objective function encourages $t_i = \min_{j \in \mc{C}_i} d_{ij}$ for all $i$.
+Meanwhile, constraints \eqref{eq:big_lp_separation_constr_t} ensure that the separation $[\min_{k \in \mc{N}\backslash\mc{C}_i} d_{ik}] - [\min_{j \in \mc{C}_i} d_{ij}]$ is at least $\epsilon$.
+If model \eqref{model:big_lp_1} returns a feasible solution with $t_i^* = \min_{j \in \mc{C}_i} d_{ij}^* > 0$ for all $i \in \mc{N}$, then the distance metric satisfies requirements 1-3.
+Otherwise there exists a subset $\mc{O}$ of outlier points such that $0 \leq t_i^* < \min_{j \in \mc{C}_i} d_{ij}^*$ for all $i \in \mc{O}$, which means that no such distance metric guaranteeing a minimum separation exists for the choice of $\epsilon$.
+
+\clearpage 
 \section{Algorithm / Work Flow}
 
+\clearpage
 \section{Numerical Experiments/Results}
+
+\subsection{Outlier Detection and Further sampling recommendation}
+
+In the experiment we took MNIST and CIFAR100 dataset
+
+we used  auto-encoders and then run Algorithm XXX
+
+Cifra 
+[7, 35, 64, 71, 73, 81]
+
+\includegraphics[scale=.1]{fig/c5.eps}
+\includegraphics[scale=.1]{fig/c6.eps}
+\includegraphics[scale=.1]{fig/c12.eps}
+
+outlier
+\includegraphics[scale=.1]{fig/c7.eps}
+
+\includegraphics[scale=.1]{fig/c8.eps}
+\includegraphics[scale=.1]{fig/c10.eps}
+
+MNIST
+[120]
+
+\includegraphics[scale=.1]{fig/MNIST119.eps}
+\includegraphics[scale=.1]{fig/MNIST121.eps}
+\includegraphics[scale=.1]{fig/MNIST122.eps}
+\includegraphics[scale=.1]{fig/MNIST124.eps}
+
+ourlier
+\includegraphics[scale=.1]{fig/MNIST120.eps}
+
+In Figure \ref{fig:AE}
+\begin{figure}
+
+\todo[inline,color=green]{TODO}
+\caption{TODO}
+\label{fig:AE}
+
+\end{figure}
 
@@
 
+we run NN
+on following datasets, using 
+$\ell_1, \ell_2, \ell_\infty$ distance measure
+and compare it with the optimal distance measure we have train by our procedure
+
+In Figure \ref{fig:NN-exp}
+\begin{figure}
+
+\todo[inline,color=green]{TODO}
+\caption{TODO}
+\label{fig:NN-exp}
+
+\end{figure}
+
+\begin{table}
+\caption{Comparison of testing error of NN with different metrics.}
+\label{tbl:BD-NN}
+\begin{tabular}{l|r|r|r|r}
+dataset & NN-$\ell_1$ 
+		& NN-$\ell_2$
+		& NN-$\ell_\infty$
+        & NN-B
+\\        
+a1a
+\\
+a9a
+\\
+covtype
+\\
+mushrooms
+\\
+splice
+\\
+iris
+\\
+breast-cancer
+\end{tabular}
+
+\end{table}
+
 \subsection{Economy of data collection}
 
-DNN - > autoencoders
-
+\clearpage 
 \section{Conclusion}
@@
 \bibliographystyle{icml2016}
+
+\clearpage 
+\appendix
+
+\onecolumn 
+\section{Proofs}
+
+$$ TODO $$
 

### 2017-01-06 python/OurMethod/src/KNN.py
add

@@ -1,0 +1,81 @@
+
+import random
+import math
+import operator
+ 
+def loadDataset(filename, split, trainingSet=[] , testSet=[]):
+    labelset = []  
+    features = []
+    dataset = []
+    f = open(filename,'rU')
+    for line in f:
+        data =  line.split(':')
+        labelset=[float(xi) for xi in data[1].split()]
+        features=[int(data[0])]
+        dataset+=[labelset+features]
+    f.close()
+    for x in range(len(dataset)):
+        for y in range(3):
+            dataset[x][y] = float(dataset[x][y])
+        if random.random() < split:
+            trainingSet.append(dataset[x])
+        else:
+            testSet.append(dataset[x])
+ 
+ 
+def euclideanDistance(instance1, instance2, length):
+    distance = 0
+    for x in range(length):
+        distance += pow((instance1[x] - instance2[x]), 2)
+    return math.sqrt(distance)
+ 
+def getNeighbors(trainingSet, testInstance, k):
+    distances = []
+    length = len(testInstance)-1
+    for x in range(len(trainingSet)):
+        dist = euclideanDistance(testInstance, trainingSet[x], length)
+        distances.append((trainingSet[x], dist))
+    distances.sort(key=operator.itemgetter(1))
+    neighbors = []
+    for x in range(k):
+        neighbors.append(distances[x][0])
+    return neighbors
+ 
+def getResponse(neighbors):
+    classVotes = {}
+    for x in range(len(neighbors)):
+        response = neighbors[x][-1]
+        if response in classVotes:
+            classVotes[response] += 1
+        else:
+            classVotes[response] = 1
+    sortedVotes = sorted(classVotes.iteritems(), key=operator.itemgetter(1), reverse=True)
+    return sortedVotes[0][0]
+ 
+def getAccuracy(testSet, predictions):
+    correct = 0
+    for x in range(len(testSet)):
+        if testSet[x][-1] == predictions[x]:
+            correct += 1
+    return (correct/float(len(testSet))) * 100.0
+    
+def main():
+    # prepare data
+    trainingSet=[]
+    testSet=[]
+    split = 0.9
+    loadDataset("50_c2_d2.txt", split, trainingSet, testSet)
+    print 'Train set: ' + repr(len(trainingSet))
+    print 'Test set: ' + repr(len(testSet))
+    # generate predictions
+    predictions=[]
+    k = 3
+    for x in range(len(testSet)):
[…]

### 2017-01-06 python/OurMethod/src/NN.py

@@ -1,76 +1,0 @@
-
-
-
-
-#load the data
-
-#training
-#testing data
-
-
- #(I will find 3 closed points)
-
-
-# run NN
-# find out how many points in testing are wrongly classified
-
-
-#########################################  
-# kNN: k Nearest Neighbors  
-  
-# Input:      newInput: vector to compare to existing dataset (1xN)  
-#             dataSet:  size m data set of known vectors (NxM)  
-#             labels:   data set labels (1xM vector)  
-#             k:        number of neighbors to use for comparison   
-              
-# Output:     the most popular class label  
-#########################################  
-  
-from numpy import *  
-import operator  
-  
-# create a dataset which contains 4 samples with 2 classes  
-def createDataSet():  
-    # create a matrix: each row as a sample  
-    group = array([[1.0, 0.9], [1.0, 1.0], [0.1, 0.2], [0.0, 0.1]])  
-    labels = ['A', 'A', 'B', 'B'] # four samples and two classes  
-    return group, labels  
-  
-# classify using kNN  
-def kNNClassify(newInput, dataSet, labels, k):  
-    numSamples = dataSet.shape[0] # shape[0] stands for the num of row  
-  
-    ## step 1: calculate Euclidean distance  
-    # tile(A, reps): Construct an array by repeating A reps times  
-    # the following copy numSamples rows for dataSet  
-    diff = tile(newInput, (numSamples, 1)) - dataSet # Subtract element-wise  
-    squaredDiff = diff ** 2 # squared for the subtract  
-    squaredDist = sum(squaredDiff, axis = 1) # sum is performed by row  
-    distance = squaredDist ** 0.5  
-  
-    ## step 2: sort the distance  
-    # argsort() returns the indices that would sort an array in a ascending order  
-    sortedDistIndices = argsort(distance)  
-  
-    classCount = {} # define a dictionary (can be append element)  
-    for i in xrange(k):  
-        ## step 3: choose the min k distance  
-        voteLabel = labels[sortedDistIndices[i]]  
-  
-        ## step 4: count the times labels occur  
-        # when the key voteLabel is not in dictionary classCount, get()  
-        # will return 0  
-        classCount[voteLabel] = classCount.get(voteLabel, 0) + 1  
-  
-    ## step 5: the max voted class will return  
-    maxCount = 0  
-    for key, value in classCount.items():  
-        if value > maxCount:  
-            maxCount = value  
-            maxIndex = key  
-  
-    return maxIndex   
-
-
-
-

### 2017-01-10 python/OurMethod/src/Experiment.py
add

@@ -3,28 +3,33 @@ from __future__ import division
 from OutlierDetection import *
 
 import pickle 
-filename = 'dataset_cifar2_sub2.txt'
-filename = 'dataset3.txt'
-
-od = OutlierDetection(filename , True)    
-
+# filename = 'dataset_cifar2_sub2.txt'
+# filename = 'dataset_cifar_sub.txt'
 # od = OutlierDetection('50_c2_d2.txt' , False)    
 
 
-epsilonMax, B, D, results, model = od.findLargestEpsilon()
+
+filename = 'dataset3.txt'
+od = OutlierDetection(filename , True)    
+
+
+
+epsilonMax, B = od.findLargestEpsilonRowAndColumnGeneration()
 
 print "Epsilon max = ", epsilonMax
-print 'Matrix B is \n', B
+# print 'Matrix B is \n', B
 # print "Matrix D is  \n ", D
 
 #print "--------------------"    
 #print(results)
 #print(model.display())
 
+"""
  
 epsilon = epsilonMax*0.01
 t, outliers, results, model = od.findDistanceBandSetOfOutliersForEpsilon(epsilon)
 print "we have ",len(outliers), "outliers: ",outliers
+
 
 
 od.setOutlierList(outliers)
@@ -37,7 +42,7 @@ print "at the end we have ", len(outliers),":",outliers
 data={}
 data["B"]=od.B
 data["outliers"]=outliers        
-pickle.dump( data, open( filename_+"0.pickle", "wb" ) ) 
+pickle.dump( data, open( filename+"0.pickle", "wb" ) ) 
 
 
 notFinished = True 
@@ -72,7 +77,7 @@ while notFinished:
     data={}
     data["B"]=od.B
     data["outliers"]=outliers        
-    pickle.dump( data, open( filename_+str(iteration)+".pickle", "wb" ) ) 
+    pickle.dump( data, open( filename+str(iteration)+".pickle", "wb" ) ) 
     
     iteration=iteration+1
     
@@ -89,7 +94,7 @@ while notFinished:
 
 
 
-
+"""
 
 
 

### 2017-01-10 python/OurMethod/src/OutlierDetection.py

@@ -73,6 +73,7 @@ class OutlierDetection:
         self.nonOutlier = range(self.n)
         self.outlier = []
         self.d = len(self.features[0])
+        print "INIT FINISHED"
 
 
     def addConstraint_d_ij_as_function_of_features_and_B(self,model):
@@ -98,6 +99,155 @@ class OutlierDetection:
         model.lowerBisZeroConstrain = Constraint(model.d*model.d, rule=lowerBisZero)
 
 
+
+    def findLargestEpsilonRowAndColumnGeneration(self):
+        
+        B = np.identity(self.d)
+        notDone = True
+        S = {}
+        
+        if True:
+            RI = {}
+            PI = {}
+            # Now let's use current Metric to find out critical points
+            
+            start = time.time()
+            print "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXX"
+            
+            dm = [ [j,k,   sum([   (self.features[j][l]-self.features[k][l])*(self.features[j][m]-self.features[k][m]) for l in xrange(self.d) for m in xrange(self.d)           ])               ]  for j in xrange(self.n) for k in xrange(self.n)] 
+
+            print "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXX",time.time()-start
+            print dm[1:10]
+
+            start = time.time()
+            for sample in self.nonOutlier:
+#                 print sample
+                distanceInClass = 1000000
+                distanceToOtherClass = 1000000
+                for testTo in self.nonOutlier:
+                    if (sample <> testTo):
+                        x = [self.features[sample][k] - self.features[testTo][k] for k in xrange(self.d)]
+                        distance = sum(  x[k]*x[l]*B[k,l] for k in xrange(self.d) for l in xrange(self.d)   )
+                        if (self.labels[sample] == self.labels[testTo] and distance < distanceInClass):
+                            distanceInClass = distance
+                        if (self.labels[sample] <> self.labels[testTo] and distance < distanceToOtherClass):
+                            distanceToOtherClass = distance
+                            PI[sample] = testTo
+                RI[sample] = distanceToOtherClass / distanceInClass
+            print "YYYYYYYYYYYYYYYYYYYYYYYYY"   ,time.time()-start          
+            M = 0
+            Mi = -1
+            for k in RI:
+                if  RI[k] > 3:
+                    S[k] = 1
+                    S[PI[k]] = 1 
+            print "RI:",RI
+            
+        
+        
+        while notDone:
+            
+        
[…]

### 2017-01-11 cpp/src/Test.cpp
add

@@ -1,0 +1,66 @@
+//============================================================================
+// Name        : Test.cpp
+// Author      : Martin Takac
+// Version     :
+// Copyright   : Your copyright notice
+// Description : Hello World in C++, Ansi-style
+//============================================================================
+
+#include <iostream>
+using namespace std;
+
+#include <vector>
+#include <stdio.h>      /* printf, scanf, puts, NULL */
+#include <stdlib.h>     /* srand, rand */
+#include <time.h>
+
+#include <time.h>
+#include <sys/time.h>
+
+
+double get_wall_time(){
+    struct timeval time;
+    if (gettimeofday(&time,NULL)){
+        //  Handle error
+        return 0;
+    }
+    return (double)time.tv_sec + (double)time.tv_usec * .000001;
+}
+
+int main() {
+
+	int N = 203;
+	int d = 40;
+
+	std::vector<double> distances(N * N, 0);
+	std::vector<double> B(d * d, 0);
+
+	cout << "Started" << endl;
+	std::vector<double> features(N * d);
+	for (int i = 0; i < features.size(); i++) {
+		features[i] = rand() / (RAND_MAX + 0.0);
+	}
+	for (int i = 0; i < B.size(); i++) {
+		B[i] = rand() / (RAND_MAX + 0.0);
+	}
+
+	cout << "Going to compute Distance" << endl;
+	double start = get_wall_time();
+	for (int i = 0; i < N; i++) {
+		for (int j = 0; j < N; j++) {
+			int idx = i * N + j;
+			for (int k = 0; k < d; k++) {
+				for (int l = 0; l < d; l++) {
+
+					distances[idx] +=  (features[i * d + k] - features[j * d + k]) * B[k * d + l]
+								* (features[i * d + l]
+								- features[j * d + l]);
+				}
+			}
+
+		}
+	}
+	double end = get_wall_time();
+	cout << "DONE " << end-start << endl;
+	return 0;
+}

### 2017-01-11 cpp/src/example.cpp

@@ -1,0 +1,18 @@
+ #include <time.h>
+ double My_variable = 3.0;
+
+ int fact(int n) {
+     if (n <= 1) return 1;
+     else return n*fact(n-1);
+ }
+
+ int my_mod(int x, int y) {
+     return (x%y);
+ }
+
+ char *get_time()
+ {
+     time_t ltime;
+     time(&ltime);
+     return ctime(&ltime);
+ }

### 2017-01-11 cpp/src/myclass.py

@@ -1,0 +1,118 @@
+# This file was automatically generated by SWIG (http://www.swig.org).
+# Version 3.0.8
+#
+# Do not make changes to this file unless you know what you are doing--modify
+# the SWIG interface file instead.
+
+
+
+
+
+from sys import version_info
+if version_info >= (2, 6, 0):
+    def swig_import_helper():
+        from os.path import dirname
+        import imp
+        fp = None
+        try:
+            fp, pathname, description = imp.find_module('_myclass', [dirname(__file__)])
+        except ImportError:
+            import _myclass
+            return _myclass
+        if fp is not None:
+            try:
+                _mod = imp.load_module('_myclass', fp, pathname, description)
+            finally:
+                fp.close()
+            return _mod
+    _myclass = swig_import_helper()
+    del swig_import_helper
+else:
+    import _myclass
+del version_info
+try:
+    _swig_property = property
+except NameError:
+    pass  # Python < 2.2 doesn't have 'property'.
+
+
+def _swig_setattr_nondynamic(self, class_type, name, value, static=1):
+    if (name == "thisown"):
+        return self.this.own(value)
+    if (name == "this"):
+        if type(value).__name__ == 'SwigPyObject':
+            self.__dict__[name] = value
+            return
+    method = class_type.__swig_setmethods__.get(name, None)
+    if method:
+        return method(self, value)
+    if (not static):
+        if _newclass:
+            object.__setattr__(self, name, value)
+        else:
+            self.__dict__[name] = value
+    else:
+        raise AttributeError("You cannot add attributes to %s" % self)
+
+
+def _swig_setattr(self, class_type, name, value):
+    return _swig_setattr_nondynamic(self, class_type, name, value, 0)
+
+
+def _swig_getattr_nondynamic(self, class_type, name, static=1):
+    if (name == "thisown"):
+        return self.this.own()
+    method = class_type.__swig_getmethods__.get(name, None)
+    if method:
+        return method(self)
+    if (not static):
+        return object.__getattr__(self, name)
+    else:
+        raise AttributeError(name)
+
+def _swig_getattr(self, class_type, name):
+    return _swig_getattr_nondynamic(self, class_type, name, 0)
+
+
+def _swig_repr(self):
+    try:
+        strthis = "proxy of " + self.this.__repr__()
+    except Exception:
+        strthis = ""
[…]

### 2017-01-11 cpp/src/test.py

@@ -1,0 +1,4 @@
+import example
+example.fact(5)
+example.my_mod(7,3)
+example.get_time()

### 2017-01-11 python/OurMethod/src/OutlierDetection.py

@@ -3,7 +3,7 @@ import numpy as np
 import math
 import time
 #https://github.com/Pyomo/PyomoGallery/blob/master/network_interdiction/multi_commodity_flow/multi_commodity_flow_interdict.py
-
+import mymodule
     
 
 def solveModel(model):
@@ -23,6 +23,10 @@ def solveModel(model):
 
 
 class OutlierDetection:
+
+
+
+
 
     EPS_M = 0.000001
     def getMatrixDFromResult(self,model):
@@ -45,8 +49,15 @@ class OutlierDetection:
                     B[j,i] = B[i,j]
         return B
 
-    
-
+    def setBInSorter(self,B):
+        for i in xrange(self.d):
+            for j in xrange(self.d):
+                if j>i:
+                    self.sorter.setBij(i,j,2*B[i,j])
+                if j==i:
+                    self.sorter.setBij(i,j,B[i,j])
+                if j<i:
+                    self.sorter.setBij(i,j,0)
 
     def __init__(self, filename ,normalize):
 
@@ -58,8 +69,7 @@ class OutlierDetection:
             self.labels+=[ int(data[0]) ]
             self.features+=[  [float(xi) for xi in data[1].split() ]              ]
         f.close()
-        #centralize data TODO    
-            
+        
         #normalizeData
         if normalize:
             M = 0
@@ -73,6 +83,16 @@ class OutlierDetection:
         self.nonOutlier = range(self.n)
         self.outlier = []
         self.d = len(self.features[0])
+
+        self.sorter = mymodule.MySorter()
+        self.sorter.InitializeData(self.n,self.d)
+
+        for sample in xrange(self.n):
+            self.sorter.setLabel(sample,self.labels[sample])
+            for feat in xrange(self.d):
+                self.sorter.setFeature(sample, feat,self.features[sample][feat] )
+
+
         print "INIT FINISHED"
 
 
@@ -103,8 +123,13 @@ class OutlierDetection:
     def findLargestEpsilonRowAndColumnGeneration(self):
         
         B = np.identity(self.d)
+        self.setBInSorter(B)
         notDone = True
         S = {}
+        
+        
+        totalPoints  = self.sorter.computeTopRiPoints(10)
+        print totalPoints
         
         if True:
             RI = {}
@@ -112,7 +137,7 @@ class OutlierDetection:
             # Now let's use current Metric to find out critical points
             
             start = time.time()
[…]

### 2017-01-11 python/OurMethod/src/mymodule.py

@@ -1,0 +1,140 @@
+# This file was automatically generated by SWIG (http://www.swig.org).
+# Version 3.0.8
+#
+# Do not make changes to this file unless you know what you are doing--modify
+# the SWIG interface file instead.
+
+
+
+
+
+from sys import version_info
+if version_info >= (2, 6, 0):
+    def swig_import_helper():
+        from os.path import dirname
+        import imp
+        fp = None
+        try:
+            fp, pathname, description = imp.find_module('_mymodule', [dirname(__file__)])
+        except ImportError:
+            import _mymodule
+            return _mymodule
+        if fp is not None:
+            try:
+                _mod = imp.load_module('_mymodule', fp, pathname, description)
+            finally:
+                fp.close()
+            return _mod
+    _mymodule = swig_import_helper()
+    del swig_import_helper
+else:
+    import _mymodule
+del version_info
+try:
+    _swig_property = property
+except NameError:
+    pass  # Python < 2.2 doesn't have 'property'.
+
+
+def _swig_setattr_nondynamic(self, class_type, name, value, static=1):
+    if (name == "thisown"):
+        return self.this.own(value)
+    if (name == "this"):
+        if type(value).__name__ == 'SwigPyObject':
+            self.__dict__[name] = value
+            return
+    method = class_type.__swig_setmethods__.get(name, None)
+    if method:
+        return method(self, value)
+    if (not static):
+        if _newclass:
+            object.__setattr__(self, name, value)
+        else:
+            self.__dict__[name] = value
+    else:
+        raise AttributeError("You cannot add attributes to %s" % self)
+
+
+def _swig_setattr(self, class_type, name, value):
+    return _swig_setattr_nondynamic(self, class_type, name, value, 0)
+
+
+def _swig_getattr_nondynamic(self, class_type, name, static=1):
+    if (name == "thisown"):
+        return self.this.own()
+    method = class_type.__swig_getmethods__.get(name, None)
+    if method:
+        return method(self)
+    if (not static):
+        return object.__getattr__(self, name)
+    else:
+        raise AttributeError(name)
+
+def _swig_getattr(self, class_type, name):
+    return _swig_getattr_nondynamic(self, class_type, name, 0)
+
+
+def _swig_repr(self):
+    try:
[…]

### 2017-01-11 python/OurMethod/src/mymodule_wrap.cpp

@@ -1,0 +1,5318 @@
+/* ----------------------------------------------------------------------------
+ * This file was automatically generated by SWIG (http://www.swig.org).
+ * Version 3.0.8
+ *
+ * This file is not intended to be easily readable and contains a number of
+ * coding conventions designed to improve portability and efficiency. Do not make
+ * changes to this file unless you know what you are doing--modify the SWIG
+ * interface file instead.
+ * ----------------------------------------------------------------------------- */
+
+
+#ifndef SWIGPYTHON
+#define SWIGPYTHON
+#endif
+
+#define SWIG_PYTHON_DIRECTOR_NO_VTABLE
+
+
+#ifdef __cplusplus
+/* SwigValueWrapper is described in swig.swg */
+template<typename T> class SwigValueWrapper {
+  struct SwigMovePointer {
+    T *ptr;
+    SwigMovePointer(T *p) : ptr(p) { }
+    ~SwigMovePointer() { delete ptr; }
+    SwigMovePointer& operator=(SwigMovePointer& rhs) { T* oldptr = ptr; ptr = 0; delete oldptr; ptr = rhs.ptr; rhs.ptr = 0; return *this; }
+  } pointer;
+  SwigValueWrapper& operator=(const SwigValueWrapper<T>& rhs);
+  SwigValueWrapper(const SwigValueWrapper<T>& rhs);
+public:
+  SwigValueWrapper() : pointer(0) { }
+  SwigValueWrapper& operator=(const T& t) { SwigMovePointer tmp(new T(t)); pointer = tmp; return *this; }
+  operator T&() const { return *pointer.ptr; }
+  T *operator&() { return pointer.ptr; }
+};
+
+template <typename T> T SwigValueInit() {
+  return T();
+}
+#endif
+
+/* -----------------------------------------------------------------------------
+ *  This section contains generic SWIG labels for method/variable
+ *  declarations/attributes, and other compiler dependent labels.
+ * ----------------------------------------------------------------------------- */
+
+/* template workaround for compilers that cannot correctly implement the C++ standard */
[…]

### 2017-01-11 python/OurMethod/src/some_class.cpp

@@ -1,0 +1,99 @@
+#include "some_class.h"
+
+
+ 
+MySorter::MySorter(){
+	
+}
+ 
+ 
+ bool compareValueIdx (const valueIdx first,const valueIdx second){
+     return first.val < second.val;
+ }
+ 
+int MySorter::computeTopRiPoints(int k){
+    int totalPoints = 0; 
+    this->topList.resize(0);
+    
+    for (int sample = 0; sample<this->n;sample++){
+        double minInclass = 1000;
+        double minOutclass = 1000;
+        int idx = -1;
+        for (int to=0;to<this->n; to++){
+            if (sample != to){
+                double distance = this->computeDistanceBetweenTwoPoint(sample, to);
+                if (this->labels[sample]==this->labels[to] && minInclass > distance ){
+                    minInclass = distance;
+                }
+                if (this->labels[sample]!=this->labels[to] && minOutclass > distance ){
+                    minOutclass = distance;
+                    idx=to;
+                }
+                if (minOutclass > 0 && minOutclass < minInclass){
+                    this->topList.push_back( valueIdx(sample,to,minInclass/minOutclass) );
+                    totalPoints++;
+                }
+                
+                
+            }
+        }
+    }
+    this->topList.sort(compareValueIdx);    
+    
+    
+    return totalPoints;
+}
+
+
+void MySorter::InitializeData(int n, int d){
+this->n=n;
+this->d=d;	
+this->features.resize(n*d,0);
+this->B.resize(d*d,0);
+this->labels.resize(n,0);
+}
+
+void MySorter::setBij(int i, int j, double value){
+  this->B[i*this->d+j] = value;	
+}
+
+double MySorter::computeDistanceBetweenTwoPoint(int i,int j){
+    double distance = 0;
+    for (int k=0;k<this->d;k++){
+        for (int l=0;l<this->d;l++){
+        distance +=  (this->features[i * d + k] - this->features[j * d + k]) * this->B[k * d + l]
+                                * (this->features[i * d + l]
+                                - this->features[j * d + l]);              
+            
+        }
+    }
+    return distance;
+}
+
+void MySorter::computeDistanceVialation(double epsilon){
+	
+	
+	
+}
+
+
+void MySorter::setFeature(int sample, int feature, double value){
+  this->features[sample*this->d+feature] = value;	
+}
+ 
+void MySorter::setLabel(int sample, int label){
[…]

### 2017-01-11 python/OurMethod/src/some_class.h

@@ -1,0 +1,54 @@
+    #ifndef _SOME_CLASS_H_
+    #define _SOME_CLASS_H_
+
+#include <vector>
+#include <list>
+
+using namespace std;
+
+class valueIdx{
+public:
+valueIdx(){
+}
+valueIdx(int _s1, int _s2, double _val){
+    this->s1=_s1;
+    this->s2=_s2;
+    this->val = _val;
+}
+  int s1;
+  int s2;
+  double val;  
+};
+
+
+    class MySorter
+    {
+    private:
+        int     n;
+        int     d;
+        std::vector<double> features;
+        std::vector<double> B;
+        std::vector<int> labels;
+        std::list<valueIdx> topList;
+    public:
+         
+        MySorter();
+
+        double computeDistanceBetweenTwoPoint(int i=0,int j=0);
+
+        void InitializeData(int n=0, int d=0);
+        void setFeature(int sample=0, int feature=0, double value=0);
+        void setBij(int i=0, int j=0, double value=0);
+        void setLabel(int sample=0, int label=0);
+  
+        int computeTopRiPoints(int k=10);
+ 
+		void computeDistanceVialation(double epsilon=0);
+ 
+        virtual ~MySorter();
+ 
+        void MethodB(int a = 5);
+        int GetValA();
+    };
+
+    #endif  // _SOME_CLASS_H_ 

### 2017-01-20 icml2017/paper.tex
add

@@
 
+try the approach suggested today.
+Use a subset of data, find $B$, 
+compute $R^{-1}$ and remove values on the left from knee point
+and then we should get points on bounday and re-optimize.
+
+why our approach is better for proposing where to sample, we can also use KNN
+
 \clearpage
+\onecolumn 
 \section{Numerical Experiments/Results}
@@
 
-In the experiment we took MNIST and CIFAR100 dataset
+In the experiment we took MNIST and CIFAR100 dataset.
+\begin{itemize}
+\item We run autoencoders with CNN to 
+find a condensed representation of images
+\item after we find the best $B$ and get a collection of outliers
+\item We show both examples for a non-outlier case and also for outlier case
+\end{itemize}
 
-we used  auto-encoders and then run Algorithm XXX
+In Figure \ref{fig:AE-MNIST}
+(left) we show an non-outlier image together with 4 closest points.
+On right, we show an outlier image together with 4 it's closest neighbours.
+We compare it with the non-optimized distance metric (second row). The detailed description of the experiment is in supplementary material.
+\begin{figure}[h!]
 
-Cifra 
-[7, 35, 64, 71, 73, 81]
+\todo[inline,color=green]{TODO}
+\caption{TODO}
+\label{fig:AE-MNIST}
+
+\end{figure}
+
+In Figure \eqref{fig:AE-CIFAR}
+we show the same but on CIFAR100 dataset.
+The detailed description of the experiment is in supplementary material.
+\begin{figure}[h!]
+
+\todo[inline,color=green]{TODO}
+\caption{TODO}
+\label{fig:AE-CIFAR}
+
+\end{figure}
 
@@
 
-MNIST
-[120]
-
 \includegraphics[scale=.1]{fig/MNIST119.eps}
@@
 
-In Figure \ref{fig:AE}
-\begin{figure}
-
-\todo[inline,color=green]{TODO}
-\caption{TODO}
-\label{fig:AE}
-
-\end{figure}
-
+\clearpage
 \subsection{NN comparison}
@@
 In Figure \ref{fig:NN-exp}
-\begin{figure}
+\begin{figure}[h!]
 
@@
 
-\begin{table}
+\begin{table}[h!]
 \caption{Comparison of testing error of NN with different metrics.}
@@
 \end{table}
+
+\clearpage
 

### 2017-01-20 python/OurMethod/src/Experiment.py

@@ -3,18 +3,28 @@ from __future__ import division
 from OutlierDetection import *
 
 import pickle 
-# filename = 'dataset_cifar2_sub2.txt'
-# od = OutlierDetection('50_c2_d2.txt' , False)    
 
 
 
-# filename = 'dataset3.txt'
-filename = 'dataset_cifar2.txt'
+
+filename = 'dataset_cifar2_sub2.txt'
+od = OutlierDetection('50_c2_d2.txt' , False)    
+
+
+
+# filename = 'MNIST.txt'
+# filename = 'CIFAR.txt'
+# filename = 'dataset_cifar2.txt'
 # filename = 'dataset_cifar_sub.txt'
 # filename = 'dataset_cifar2_sub.txt'
-filename = '50_c2_d2.txt'
+# od = OutlierDetection(filename , True)    
 
-od = OutlierDetection(filename , True)    
+
+
+
+# filename = '50_c2_d2.txt'
+# od = OutlierDetection(filename , False)    
+
 
 
 
@@ -22,21 +32,75 @@ epsilonMax, B = od.findLargestEpsilonRowAndColumnGeneration()
 
 print "Epsilon max = ", epsilonMax
 
-# od.setBInSorter(B)
+epsilon = epsilonMax*0.01
 
 
-# epsilonMax, B, D, results, model = od.findLargestEpsilon()
+t,  newOutliers, B = od.findDistanceBandSetOfOutliersForEpsilon_SPARSE(epsilon,B)
+currentOultiers = newOutliers
+t,  newOutliers, B = od.findDistanceBandSetOfOutliersForEpsilon_SPARSE(epsilon,B,currentOultiers)
+for x in newOutliers:
+    currentOultiers+=[x]
 
-# for i in xrange(od.n):
-#     for j in xrange(od.n):
-#         print i,j, od.sorter.computeDistanceBetweenTwoPoint(i, j), D[(i,j)]
-# print "Epsilon max = ", epsilonMax
-# print B
+data={}
+data["B"]=od.B
+data["outliers"]=currentOultiers  
+data["epsilon"]=epsilon        
+pickle.dump( data, open( filename+"_INIT"+".pickle", "wb" ) )  
+
+wasDoneSomeChange = True 
+iteration = 0
+while wasDoneSomeChange:
+    print "\n\n Iteration ",iteration 
+    
+    print "Insertion of outliers procedure    "
+    print currentOultiers
+
[…]

### 2017-01-20 python/OurMethod/src/OutlierDetection.py

@@ -4,17 +4,22 @@ import math
 import time
 #https://github.com/Pyomo/PyomoGallery/blob/master/network_interdiction/multi_commodity_flow/multi_commodity_flow_interdict.py
 import mymodule
+from matplotlib.mlab import dist
+from dis import dis
     
-EMA = 0.0000000001
+EMA = 0.000001
 
 def solveModel(model):
-        opt = SolverFactory("cplex")#,solver_io='python')
-        
+        opt = SolverFactory("cbc")#,solver_io='python')
+#         opt = SolverFactory("cplexamp")
 #         print "-------------Going to solve the model-------------"
 #         solver_manager = SolverManagerFactory('neos')
 #         results = solver_manager.solve(model, opt=opt)
-        
-        results = opt.solve(model)
+        start_time = time.time()
+        print "Start "
+        results = opt.solve(model)#, warmstart=True)
+        elapsed_time = time.time() - start_time
+        print "solving took ", elapsed_time
 #         print(results)
 #         print "-------------Model solved-------------"
         
@@ -58,7 +63,7 @@ class OutlierDetection:
                 if j==i:
                     self.sorter.setBij(i,j,B[i,j])
                 if j<i:
-                    self.sorter.setBij(i,j,0)
+                    self.sorter.setBij(i,j,0.0)
 
     def __init__(self, filename ,normalize):
 
@@ -78,7 +83,7 @@ class OutlierDetection:
                     normi = sum(xi*xi for xi in sample)
                     M = max(M,normi)
             M = math.sqrt(M)
-            self.features = [   [ xi/M for xi in sample   ]        for sample in self.features  ]
+            self.features = [   [ xi/M for xi in sample    ]        for sample in self.features  ]
 
         self.n = len(self.labels)
         self.nonOutlier = range(self.n)
@@ -124,10 +129,58 @@ class OutlierDetection:
         self.violations = self.violationsHM.values()
 
     def addViolation(self,n1, n2):
+        hadThisKey = False
         if n1<n2:
-            self.violationsHM[str(n1)+"_"+str(n2)] = [n1,n2]
+            key = str(n1)+"_"+str(n2)
+            if key in self.violationsHM:
+                hadThisKey = True
+            self.violationsHM[key] = [n1,n2]
         else:
-            self.violationsHM[str(n2)+"_"+str(n1)] = [n2,n1]
+            key = str(n2)+"_"+str(n1)
+            if key in self.violationsHM:
[…]

### 2017-01-20 python/OurMethod/src/mymodule.py

@@ -121,6 +121,27 @@ class MySorter(_object):
     def computeDistanceBetweenTwoPoint(self, i=0, j=0):
         return _mymodule.MySorter_computeDistanceBetweenTwoPoint(self, i, j)
 
+    def setEpsilon(self, value=0):
+        return _mymodule.MySorter_setEpsilon(self, value)
+
+    def resetOutliers(self):
+        return _mymodule.MySorter_resetOutliers(self)
+
+    def setOutlier(self, idx=0):
+        return _mymodule.MySorter_setOutlier(self, idx)
+
+    def removeOutlier(self, idx=0):
+        return _mymodule.MySorter_removeOutlier(self, idx)
+
+    def getOutlierForTopList(self, index=0):
+        return _mymodule.MySorter_getOutlierForTopList(self, index)
+
+    def computeRi(self, sample=0):
+        return _mymodule.MySorter_computeRi(self, sample)
+
+    def getViolationsForT(self):
+        return _mymodule.MySorter_getViolationsForT(self)
+
     def computeTopRiPoints(self, k=10):
         return _mymodule.MySorter_computeTopRiPoints(self, k)
 

### 2017-01-20 python/OurMethod/src/mymodule_wrap.cpp

@@ -4259,6 +4259,538 @@ fail:
 }
 
 
+SWIGINTERN PyObject *_wrap_MySorter_setEpsilon__SWIG_0(PyObject *SWIGUNUSEDPARM(self), PyObject *args) {
+  PyObject *resultobj = 0;
+  MySorter *arg1 = (MySorter *) 0 ;
+  double arg2 ;
+  void *argp1 = 0 ;
+  int res1 = 0 ;
+  double val2 ;
+  int ecode2 = 0 ;
+  PyObject * obj0 = 0 ;
+  PyObject * obj1 = 0 ;
+  
+  if (!PyArg_ParseTuple(args,(char *)"OO:MySorter_setEpsilon",&obj0,&obj1)) SWIG_fail;
+  res1 = SWIG_ConvertPtr(obj0, &argp1,SWIGTYPE_p_MySorter, 0 |  0 );
+  if (!SWIG_IsOK(res1)) {
+    SWIG_exception_fail(SWIG_ArgError(res1), "in method '" "MySorter_setEpsilon" "', argument " "1"" of type '" "MySorter *""'"); 
+  }
+  arg1 = reinterpret_cast< MySorter * >(argp1);
+  ecode2 = SWIG_AsVal_double(obj1, &val2);
+  if (!SWIG_IsOK(ecode2)) {
+    SWIG_exception_fail(SWIG_ArgError(ecode2), "in method '" "MySorter_setEpsilon" "', argument " "2"" of type '" "double""'");
+  } 
+  arg2 = static_cast< double >(val2);
+  (arg1)->setEpsilon(arg2);
+  resultobj = SWIG_Py_Void();
+  return resultobj;
+fail:
+  return NULL;
+}
+
+
+SWIGINTERN PyObject *_wrap_MySorter_setEpsilon__SWIG_1(PyObject *SWIGUNUSEDPARM(self), PyObject *args) {
+  PyObject *resultobj = 0;
+  MySorter *arg1 = (MySorter *) 0 ;
+  void *argp1 = 0 ;
+  int res1 = 0 ;
+  PyObject * obj0 = 0 ;
+  
+  if (!PyArg_ParseTuple(args,(char *)"O:MySorter_setEpsilon",&obj0)) SWIG_fail;
+  res1 = SWIG_ConvertPtr(obj0, &argp1,SWIGTYPE_p_MySorter, 0 |  0 );
+  if (!SWIG_IsOK(res1)) {
[…]

### 2017-01-20 python/OurMethod/src/some_class.cpp

@@ -1,7 +1,7 @@
 #include "some_class.h"
 
 #include <algorithm>    // std::sort
- 
+#include <iostream>
 MySorter::MySorter(){
 	
 }
@@ -28,7 +28,137 @@ double  MySorter::getValueForTopList(int index){
     return this->topList[index].val;
 }
  
+int  MySorter::getOutlierForTopList(int index){
+        return this->topList[index].isOutliear;
+}
+  
+double MySorter::computeRi(int sample){
+    double inClassDistance=100000;
+    double OutClassDistance=100000;
+    for (int to=0; to<this->n; to++){
+        if(!this->isOutlier[to]){
+            
+            double distance =  this->computeDistanceBetweenTwoPoint(sample, to);           
+            if (this->labels[sample] ==  this->labels[to]){
+                if (inClassDistance > distance){
+                    inClassDistance = distance; 
+                }
+            }else{
+                if (OutClassDistance > distance){
+                    OutClassDistance = distance; 
+                }
+            }
+        }
+    }
+    return OutClassDistance / (inClassDistance);
+} 
  
+ 
+void MySorter::setEpsilon(double value){
+   this->epsilon = value;
+} 
+
+
+void MySorter::resetOutliers(){
+    for (int sample=0;sample<this->n; sample++){
+        this->isOutlier[sample]=0;
+    }
+}
+void MySorter::setOutlier(int idx){
+    this->isOutlier[idx]=1;
+}
+void MySorter::removeOutlier(int idx){
+    this->isOutlier[idx]=0;
+}
+
+
+
+
+int MySorter::getViolationsForT(){
+
+    this->topList.resize(0);
+
+    int ttp = 0;
+    for (int sample = 0; sample < this->n; sample++){
+        if (!this->isOutlier[sample]){
+            double closestInclassPoint = 10000;
+            double closestOutclassPoint = 10000;
+            
+            double MaxDistance = -10000;
+            int idxMaxDistance = -1;            
+            
+            int idxInClass=-1;
+            int idxoutClass=-1;
+            for (int to=0;to<this->n; to++){
+                if (sample != to && !this->isOutlier[to]){
+                    
+                    double distance = this->computeDistanceBetweenTwoPoint(sample, to);
+//                     if (sample==0 || to == 0)
+//                     std::cout << sample<<" "<<to<<" "<<distance<<std::endl;
+                    if (distance > MaxDistance){
+                        MaxDistance = distance;
+                        idxMaxDistance = to;
+//                         if (sample==0|| to==0)
[…]

### 2017-01-20 python/OurMethod/src/some_class.h

@@ -14,10 +14,20 @@ valueIdx(int _s1, int _s2, double _val){
     this->s1=_s1;
     this->s2=_s2;
     this->val = _val;
+    this->isOutliear =-1;
 }
+valueIdx(int _s1, int _s2, double _val, int _isOutliear){
+    this->s1=_s1;
+    this->s2=_s2;
+    this->val = _val;
+    this->isOutliear = _isOutliear;
+}
+
+
   int s1;
   int s2;
   double val;  
+  int isOutliear;
 };
 
 
@@ -26,10 +36,13 @@ valueIdx(int _s1, int _s2, double _val){
     private:
         int     n;
         int     d;
+        std::vector<bool> isOutlier;
         std::vector<double> features;
         std::vector<double> B;
         std::vector<int> labels;
         std::vector<valueIdx> topList;
+        double epsilon;
+        double EML = 0.000000001;
     public:
          
         MySorter();
@@ -39,12 +52,20 @@ valueIdx(int _s1, int _s2, double _val){
         void InitializeData(int n=0, int d=0);
         void setFeature(int sample=0, int feature=0, double value=0);
         void setBij(int i=0, int j=0, double value=0);
+        void setEpsilon(double value=0);
         void setLabel(int sample=0, int label=0);
-  
+        int getViolationsForT();
+        double computeRi(int sample=0);
+        void resetOutliers();
+        void setOutlier(int idx = 0);
+        void removeOutlier(int idx = 0);
+        
+        
         int computeTopRiPoints(int k=10);
  
         int getIndexForTopList(int index=0, int coordinate=0);
         double getValueForTopList(int index=0);
+        int getOutlierForTopList(int index=0);
  
  
 		void computeDistanceVialation(double epsilon=0);

### 2017-01-20 tensorflow/CFIAR_09_convolutional_autoencoder.py

@@ -15,7 +15,7 @@ import matplotlib.pyplot as plt
 
 # %%
 def autoencoder(input_shape=[None, 3072],
-                n_filters=[3, 4, 4, 4 ],
+                n_filters=[3, 8, 8, 3 ],
                 filter_sizes=[3, 3, 3, 3 ],
                 corruption=False):
     """Build a deep denoising autoencoder w/ tied weights.
@@ -170,8 +170,8 @@ def traing_cifar(feat, labels):
     # %%
     # Plot example reconstructions
     
-    fo = open('../python/OurMethod/src/dataset_cifar2.txt','w')
-    foi = open('../python/OurMethod/src/dataset_cifar_images2.txt','w')
+    fo = open('../python/OurMethod/src/CIFAR.txt','w')
+    foi = open('../python/OurMethod/src/CIFAR_images.txt','w')
     
     n_examples = 100
     for k in xrange(n/n_examples):

### 2017-01-20 tensorflow/MNIST_09_convolutional_autoencoder.py

@@ -10,7 +10,7 @@ from libs.utils import corrupt
 
 # %%
 def autoencoder(input_shape=[None, 784],
-                n_filters=[1, 10, 10, 10, 10],
+                n_filters=[1, 10, 10, 10, 5],
                 filter_sizes=[3, 3, 3, 3, 3],
                 corruption=False):
     """Build a deep denoising autoencoder w/ tied weights.
@@ -150,13 +150,13 @@ def test_mnist():
     # %%
     # Fit all training data
     batch_size = 100
-    n_epochs = 20
+    n_epochs = 200
     for epoch_i in range(n_epochs):
-        print epoch_i
+#         print epoch_i
 #     for epoch_i in range(2):
         for batch_i in range(mnist.train.num_examples // batch_size):
 #         for   batch_i in range( 1):
-            print batch_i
+#             print batch_i
             batch_xs, _ = mnist.train.next_batch(batch_size)
             train = np.array([img - mean_img for img in batch_xs])
             sess.run(optimizer, feed_dict={ae['x']: train})
@@ -165,10 +165,10 @@ def test_mnist():
     # %%
     # Plot example reconstructions
     
-    fo = open('../python/OurMethod/src/dataset3.txt','w')
-    foi = open('../python/OurMethod/src/dataset3_images.txt','w')
+    fo = open('../python/OurMethod/src/MNIST.txt','w')
+    foi = open('../python/OurMethod/src/MNIST_images.txt','w')
     
-    for k in xrange(10):
+    for k in xrange(50):
         print k
         n_examples = 64
         test_xs, test_ys = mnist.test.next_batch(n_examples)

### 2017-01-24 icml2017/paper.tex
add

@@
 
-\includegraphics[scale=.1]{fig/c5.eps}
-\includegraphics[scale=.1]{fig/c6.eps}
-\includegraphics[scale=.1]{fig/c12.eps}
+ \clearpage
 
-outlier
-\includegraphics[scale=.1]{fig/c7.eps}
+\subsection{MNIST}
 
-\includegraphics[scale=.1]{fig/c8.eps}
-\includegraphics[scale=.1]{fig/c10.eps}
+following table shows the outlier (first column) and 3 closest points in the dataset
 
-\includegraphics[scale=.1]{fig/MNIST119.eps}
-\includegraphics[scale=.1]{fig/MNIST121.eps}
-\includegraphics[scale=.1]{fig/MNIST122.eps}
-\includegraphics[scale=.1]{fig/MNIST124.eps}
+\begin{tabular}{cccc}
 
-ourlier
-\includegraphics[scale=.1]{fig/MNIST120.eps}
+2 &1& 1& 1\\
+
+\includegraphics[scale=.1]{fig/MNIST_207_2_0_207_2.eps}&
+\includegraphics[scale=.1]{fig/MNIST_207_2_1_942_1.eps}&
+\includegraphics[scale=.1]{fig/MNIST_207_2_2_510_1.eps}&
+\includegraphics[scale=.1]{fig/MNIST_207_2_3_514_1.eps}
+
+\\ \hline 
+2 & 0 & 2 & 2\\
+\includegraphics[scale=.1]{fig/MNIST_392_2_0_392_2.eps} &
+\includegraphics[scale=.1]{fig/MNIST_392_2_1_161_0.eps}&
+\includegraphics[scale=.1]{fig/MNIST_392_2_2_424_2.eps}&
+\includegraphics[scale=.1]{fig/MNIST_392_2_3_609_2.eps}
+\\
+\hline 
+2 & 0 & 0 & 0 \\
+
+\includegraphics[scale=.1]{fig/MNIST_653_2_0_653_2.eps} &
+\includegraphics[scale=.1]{fig/MNIST_653_2_1_171_0.eps}&
+\includegraphics[scale=.1]{fig/MNIST_653_2_2_252_0.eps}&
+\includegraphics[scale=.1]{fig/MNIST_653_2_3_938_0.eps}
+
+\\
+\hline 
+2 & 0 & 0 & 0 \\
+
+\includegraphics[scale=.1]{fig/MNIST_771_2_0_771_2.eps} &
+\includegraphics[scale=.1]{fig/MNIST_771_2_1_818_0.eps} &
+\includegraphics[scale=.1]{fig/MNIST_771_2_2_875_0.eps} &
+\includegraphics[scale=.1]{fig/MNIST_771_2_3_793_0.eps}
+
+\\ \hline
+
+1 & 2 & 2 &2 \\
+
+\includegraphics[scale=.1]{fig/MNIST_947_1_0_947_1.eps}&
+\includegraphics[scale=.1]{fig/MNIST_947_1_1_913_2.eps}&
+\includegraphics[scale=.1]{fig/MNIST_947_1_2_806_2.eps}&
+\includegraphics[scale=.1]{fig/MNIST_947_1_3_13_2.eps}
+\\ \hline
+1 & 2 & 1 & 2 \\
+
+\includegraphics[scale=.1]{fig/MNIST_962_1_0_962_1.eps}&
+\includegraphics[scale=.1]{fig/MNIST_962_1_1_760_2.eps}&
+\includegraphics[scale=.1]{fig/MNIST_962_1_2_733_1.eps}&
+\includegraphics[scale=.1]{fig/MNIST_962_1_3_456_2.eps}
+
+\end{tabular}
+
+\clearpage
+\subsection{Experiments with synthetic data}
+
+We compare with LMNN (I used the lmnn v3 software)
+with our approach
+In Figure \ref{fig:synthetic} we show the dataset
+and also we show the unit distance plot for various $K$ for LMNN algorithm.
+Note that for value of $K=2$ and $K=4$ the their result is terrible.
+\begin{figure}[h!]
+
+\includegraphics[scale=.2]{fig/synthetic1.eps}
+\includegraphics[scale=.3]{fig/synthetic1lmnn.eps}
+\includegraphics[scale=.2]{fig/synthetic1our.eps}
+
+\caption{Comparison of LMNN for various parameter $K$.
+In code it is written 
+ attract $K$ nearest similar labeled vectors. 
+ The last plot on right is the solution give by our algorithm. 
+ PS: just to note, this is different from the one you are used to plot.
+}
+\label{fig:synthetic}
+\end{figure}
 

### 2017-01-24 matlab/mlcircus-lmnn-5b49cafaeb9a/lmnn3/fig.m

@@ -1,0 +1,261 @@
+function h = fig(varargin)
+% FIG - Creates a figure with a desired size, no white-space, and several other options.
+%
+%       All Matlab figure options are accepted. 
+%       FIG-specific options of the form FIG('PropertyName',propertyvalue,...) 
+%       can be used to modify the default behavior, as follows:
+%
+%       -'units'    : preferred unit for the width and height of the figure 
+%                      e.g. 'inches', 'centimeters', 'pixels', 'points', 'characters', 'normalized' 
+%                      Default is 'centimeters'
+%
+%       -'width'    : width of the figure in units defined by 'units'
+%                      Default is 14 centimeters
+%                      Note: For IEEE journals, one column wide standard is
+%                      8.5cm (3.5in), and two-column width standard is 17cm (7 1/16 in)
+%
+%       -'height'   : height of the figure in units defined by 'units'
+%                      Specifying only one dimension sets the other dimension
+%                      to preserve the figure's default aspect ratio. 
+%
+%       -'font'     : The font name for all the texts on the figure, including labels, title, legend, colorbar, etc.
+%                      Default is 'Times New Roman' 
+%
+%       -'fontsize' : The font size for all the texts on the figure, including labels, title, legend, colorbar, etc.
+%                      Default is 14pt
+%       
+%       -'border'   : Thin white border around the figure (compatible with export_fig -nocrop) 
+%                      'on', 'off'
+%                      Default is 'off' 
+%
+%   FIG(H) makes H the current figure. 
+%   If figure H does not exist, and H is an integer, a new figure is created with
+%   handle H.
+%
+%   FIG(H,...) applies the properties to the figure H.
+%
+%   H = FIG(...) returns the handle to the figure created by FIG.
+%
+%
+% Example 1:
+%   fig
+%
+% Example 2:
+%   h=fig('units','inches','width',8,'height',8,'font','Helvetica','fontsize',20)
+%
+%
+% Copyright  © 2012 Reza Shirvany,  matlab.sciences@neverbox.com 
+% Source: 	 http://www.mathworks.com/matlabcentral/fileexchange/30736
[…]

### 2017-01-24 matlab/mlcircus-lmnn-5b49cafaeb9a/lmnn3/importfile.m

@@ -1,0 +1,22 @@
+function rawData1 = importfile(fileToRead1)
+%IMPORTFILE(FILETOREAD1)
+%  Imports data from the specified file
+%  FILETOREAD1:  file to read
+
+%  Auto-generated by MATLAB on 23-Jan-2017 15:00:44
+
+% Import the file
+rawData1 = importdata(fileToRead1);
+
+% For some simple files (such as a CSV or JPEG files), IMPORTDATA might
+% return a simple array.  If so, generate a structure so that the output
+% matches that from the Import Wizard.
+[~,name] = fileparts(fileToRead1);
+newData1.(genvarname(name)) = rawData1;
+
+% Create new variables in the base workspace from those fields.
+vars = fieldnames(newData1);
+for i = 1:length(vars)
+    assignin('base', vars{i}, newData1.(vars{i}));
+end
+

### 2017-01-24 python/OurMethod/src/CIFAR_clean.py

@@ -1,0 +1,57 @@
+
+import tensorflow as tf
+import numpy as np
+import math
+import pickle 
+from xml.sax.handler import feature_external_ges
+import tensorflow as tf
+import tensorflow.examples.tutorials.mnist.input_data as input_data
+import matplotlib.pyplot as plt
+
+
+f = open('CIFAR.txt','rU')
+fw = open('CIFAR_f.txt','w')
+i = 0
+dic={}
+problem=[]
+for line in f:
+    key, val = line.split(":")
+    if val in dic:
+        print i
+        problem+=[i] 
+    else:
+        fw.write(line)
+    dic[val] = 1
+    
+    i=i+1
+f.close()
+fw.close()    
+
+data=[]
+i = 0
+f = open("CIFAR_images.txt")
+fw = open("CIFAR_f_images.txt",'w')
+for line in f:
+    if i not in problem:
+        fw.write(line) 
+    data += [line]
+    i=i+1
+f.close()
+fw.close()
+#[7, 35, 64, 71, 73, 81]
+for id in problem:
+    print id
+    
+    pic = data[id]
+    pic = np.array([float(x) for x in pic.split()])
+    print pic
+    
+    pic2 = np.reshape(pic, (32,32,3), order='F')
+    pic2 = pic.reshape(3,32,32).transpose(1,2,0)
+         
+    imgplot = plt.imshow(pic2)  
+     
+    plt.draw()   
+    #fig.show()
+    #
+    plt.waitforbuttonpress()

### 2017-01-24 python/OurMethod/src/Experiment.py

@@ -7,18 +7,20 @@ import pickle
 
 
 
-filename = 'dataset_cifar2_sub2.txt'
-od = OutlierDetection('50_c2_d2.txt' , False)    
 
 
 
 # filename = 'MNIST.txt'
-# filename = 'CIFAR.txt'
+filename = 'CIFAR_f.txt'
 # filename = 'dataset_cifar2.txt'
 # filename = 'dataset_cifar_sub.txt'
 # filename = 'dataset_cifar2_sub.txt'
-# od = OutlierDetection(filename , True)    
+# filename = 'CIFAR.txt'
 
+
+filename = 'synthetic.txt'
+
+od = OutlierDetection(filename , False)    
 
 
 
@@ -29,6 +31,7 @@ od = OutlierDetection('50_c2_d2.txt' , False)
 
 
 epsilonMax, B = od.findLargestEpsilonRowAndColumnGeneration()
+
 
 print "Epsilon max = ", epsilonMax
 
@@ -73,6 +76,7 @@ while wasDoneSomeChange:
     
 print "FINAL LIST OF OUTLIERS",currentOultiers
 
+print B
 
 
 

### 2017-01-24 python/OurMethod/src/OutlierDetection.py

@@ -11,13 +11,13 @@ EMA = 0.000001
 
 def solveModel(model):
         opt = SolverFactory("cbc")#,solver_io='python')
-#         opt = SolverFactory("cplexamp")
+#         opt = SolverFactory("cplex")
 #         print "-------------Going to solve the model-------------"
 #         solver_manager = SolverManagerFactory('neos')
 #         results = solver_manager.solve(model, opt=opt)
         start_time = time.time()
         print "Start "
-        results = opt.solve(model)#, warmstart=True)
+        results = opt.solve(model)#)#, warmstart=True
         elapsed_time = time.time() - start_time
         print "solving took ", elapsed_time
 #         print(results)

### 2017-01-24 python/OurMethod/src/synthetic.m

@@ -1,0 +1,90 @@
+0: -15 1
+1: -15 0
+0: -15 -1
+0: -13 1
+1: -13 0
+0: -13 -1
+0: -11 1
+1: -11 0
+0: -11 -1
+0: -9 1
+1: -9 0
+0: -9 -1
+0: -7 1
+1: -7 0
+0: -7 -1
+0: -5 1
+1: -5 0
+0: -5 -1
+0: -3 1
+1: -3 0
+0: -3 -1
+0: -1 1
+1: -1 0
+0: -1 -1
+0: 1 1
+1: 1 0
+0: 1 -1
+0: 3 1
+1: 3 0
+0: 3 -1
+0: 5 1
+1: 5 0
+0: 5 -1
+0: 7 1
+1: 7 0
+0: 7 -1
+0: 9 1
+1: 9 0
+0: 9 -1
+0: 11 1
+1: 11 0
+0: 11 -1
+0: 13 1
+1: 13 0
+0: 13 -1
+0: 15 1
+1: 15 0
+0: 15 -1
+0: 17 1
+1: 17 0
+0: 17 -1
+0: 19 1
+1: 19 0
+0: 19 -1
+0: 21 1
+1: 21 0
+0: 21 -1
+0: 23 1
+1: 23 0
+0: 23 -1
+0: 25 1
+1: 25 0
+0: 25 -1
+0: 27 1
+1: 27 0
+0: 27 -1
+0: 29 1
+1: 29 0
+0: 29 -1
+0: 31 1
+1: 31 0
+0: 31 -1
+0: 33 1
+1: 33 0
+0: 33 -1
+0: 35 1
+1: 35 0
+0: 35 -1
+0: 37 1
+1: 37 0
+0: 37 -1
+0: 39 1
+1: 39 0
+0: 39 -1
+0: 41 1
+1: 41 0
+0: 41 -1
+0: 43 1
+1: 43 0
+0: 43 -1

### 2017-01-26 python/OurMethod/src/Adaptive2.py
Add

@@ -1,0 +1,192 @@
+from __future__ import division
+
+from OutlierDetection import *
+import random
+import pickle 
+
+
+
+import matplotlib.pyplot as plt
+
+
+
+# filename = 'MNIST.txt'
+filename = 'MNISTFULL.txt'
+# filename = 'dataset_cifar2.txt'
+# filename = 'dataset_cifar_sub.txt'
+# filename = 'dataset_cifar2_sub.txt'
+# filename = 'CIFAR.txt'
+
+
+# filename = 'synthetic.txt'
+
+# filename = 'CIFAR5.txt'
+
+ 
+
+odAll = OutlierDetection(filename , True)   
+
+allFeatures = odAll.features
+allLabels = odAll.labels
+allN=len(allLabels)
+print "All data:",allN , "d  = ",len(allFeatures[0])
+
+data  = pickle.load( open(   filename+"_INIT"+".pickle", "r" ) ) 
+# data  = pickle.load( open(   filename+"_S3"+".pickle", "r" ) ) 
+
+
+B = data["B"] 
+currentOultiers = data["outliers"]  
+epsilon = data["epsilon"]        
+labels = data['labels']
+features = data['features']
+selection = data['selection']
+
+ 
+print len(currentOultiers) , len(features)
+
+skippPoints = {}
+ALREADY_SELECTED={}
+totalWorkingPoints=0
+for x in selection:
+    ALREADY_SELECTED[x]  = 1
+    skippPoints[totalWorkingPoints]=x
+    totalWorkingPoints=totalWorkingPoints+1
+
+
+print "current ouliers:",len(currentOultiers)
+print "working set:",len(labels)
+
+
+
+odAll.setBInSorter(B)
+for k in currentOultiers:
+    globalID = selection[k]
+    i = globalID
+# for globalID in xrange(allN):
+#     i=globalID    
+    currentLabel = allLabels[ globalID  ]
+    
+    closestPointID = -1
+    minDistance = 1000
+    #---------- want to find a closest points in DB to include them
+    for j in xrange(allN):
+        if j not in ALREADY_SELECTED and currentLabel == allLabels[j]:
+            distance = odAll.sorter.computeDistanceBetweenTwoPoint(i, j)
+            if distance < minDistance:
+                minDistance = distance
+                closestPointID = j
+#     print "Outlier",i,"add ",closestPointID, minDistance
+    labels+=[ allLabels[closestPointID] ]
+    features+=[ allFeatures[closestPointID] ]
[…]

### 2017-01-26 python/OurMethod/src/Experiment.py

@@ -16,11 +16,12 @@ filename = 'CIFAR_f.txt'
 # filename = 'dataset_cifar_sub.txt'
 # filename = 'dataset_cifar2_sub.txt'
 # filename = 'CIFAR.txt'
+filename = 'MNISTFULL.txt'
 
 
-filename = 'synthetic.txt'
+# filename = 'synthetic.txt'
 
-od = OutlierDetection(filename , False)    
+od = OutlierDetection(filename , True)    
 
 
 
@@ -50,6 +51,8 @@ data["outliers"]=currentOultiers
 data["epsilon"]=epsilon        
 pickle.dump( data, open( filename+"_INIT"+".pickle", "wb" ) )  
 
+
+
 wasDoneSomeChange = True 
 iteration = 0
 while wasDoneSomeChange:
@@ -61,24 +64,28 @@ while wasDoneSomeChange:
     currentOultiers, wasDoneSomeChange = od.insertOutliers_Method_CyclicAssignmentSPARSE(currentOultiers)
     print currentOultiers
     
-    if (wasDoneSomeChange):
-        t,  newOutliers, B = od.findDistanceBandSetOfOutliersForEpsilon_SPARSE(epsilon,B,currentOultiers)    
-        print newOutliers
-        for x in newOutliers:
-            currentOultiers +=[x]
-    if iteration > 4:
-        break
+    
     iteration=iteration+1
     data={}
-    data["B"]=od.B
+    data["B"]=B
     data["outliers"]=currentOultiers        
     pickle.dump( data, open( filename+"_"+str(iteration)+".pickle", "wb" ) ) 
     
+    
+    
+    if (wasDoneSomeChange):
+        t,  newOutliers, B = od.findDistanceBandSetOfOutliersForEpsilon_SPARSE(epsilon,B,currentOultiers)    
+        print "new outliers identified",newOutliers
+        for x in newOutliers:
+            currentOultiers +=[x]
+    if iteration > 10:
+        break
 print "FINAL LIST OF OUTLIERS",currentOultiers
 
-print B
-
-
+data={}
+data["B"]=od.B
+data["outliers"]=currentOultiers        
+pickle.dump( data, open( filename+"_"+"FINAL"+".pickle", "wb" ) )  
 
 
     

### 2017-01-26 python/OurMethod/src/OutlierDetection.py

@@ -17,7 +17,9 @@ def solveModel(model):
 #         results = solver_manager.solve(model, opt=opt)
         start_time = time.time()
         print "Start "
-        results = opt.solve(model)#)#, warmstart=True
+        results = opt.solve(model)#)#
+#         results = opt.solve(model, warmstart=True)#)#
+        
         elapsed_time = time.time() - start_time
         print "solving took ", elapsed_time
 #         print(results)
@@ -65,25 +67,35 @@ class OutlierDetection:
                 if j<i:
                     self.sorter.setBij(i,j,0.0)
 
-    def __init__(self, filename ,normalize):
 
-        self.labels = []  
-        self.features = []
-        f = open(filename,'rU')
-        for line in f:
-            data =  line.split(':')
-            self.labels+=[ int(data[0]) ]
-            self.features+=[  [float(xi) for xi in data[1].split() ]              ]
-        f.close()
+    def __init__(self, filename ,normalize,labels=[], features=[]):
+
+        self.labels = labels 
+        self.features = features
         
-        #normalizeData
-        if normalize:
-            M = 0
-            for sample in self.features:
-                    normi = sum(xi*xi for xi in sample)
-                    M = max(M,normi)
-            M = math.sqrt(M)
-            self.features = [   [ xi/M for xi in sample    ]        for sample in self.features  ]
+        if filename != None:
+            f = open(filename,'rU')
+            i=0
+            for line in f:
+                data =  line.split(':')
+                self.labels+=[ int(data[0]) ]
+                self.features+=[  [float(xi) for xi in data[1].split() ]              ]
+                i=i+1
+                if i > 100:
+                    break
+            f.close()
+            
+            #normalizeData
+            if normalize:
+                M = 0
+                for sample in self.features:
+                        normi = sum(xi*xi for xi in sample)
+                        M = max(M,normi)
+                M = math.sqrt(M)
+                self.features = [   [ xi/M for xi in sample    ]        for sample in self.features  ]
+
+
+
 
         self.n = len(self.labels)
         self.nonOutlier = range(self.n)
@@ -173,8 +185,6 @@ class OutlierDetection:
             def fDE(model, idx):
                 i = self.violations[idx][0]
                 j = self.violations[idx][1]
-                if j==140:
-                    print idx, i,j
                 distance = self.sorter.computeDistanceBetweenTwoPoint(i, j)
[…]

### 2017-01-26 python/OurMethod/src/some_class.cpp

@@ -90,17 +90,22 @@ int MySorter::getViolationsForT(){
             int idxInClass=-1;
             int idxoutClass=-1;
             for (int to=0;to<this->n; to++){
+            
+            
+            double distance = this->computeDistanceBetweenTwoPoint(sample, to);
+                //                     if (sample==0 || to == 0)
+                //                     std::cout << sample<<" "<<to<<" "<<distance<<std::endl;
+                                    if (distance > MaxDistance){
+                                        MaxDistance = distance;
+                                        idxMaxDistance = to;
+                //                         if (sample==0|| to==0)
+                //                             std::cout<<"C++3 "<< sample<<" "<<to<<" "<< MaxDistance<<std::endl;
+                                    }
+            
+            
                 if (sample != to && !this->isOutlier[to]){
                     
-                    double distance = this->computeDistanceBetweenTwoPoint(sample, to);
-//                     if (sample==0 || to == 0)
-//                     std::cout << sample<<" "<<to<<" "<<distance<<std::endl;
-                    if (distance > MaxDistance){
-                        MaxDistance = distance;
-                        idxMaxDistance = to;
-//                         if (sample==0|| to==0)
-//                             std::cout<<"C++3 "<< sample<<" "<<to<<" "<< MaxDistance<<std::endl;
-                    }
+                    
                     
                     if (this->labels[sample] ==  this->labels[to]){
                         if (distance < closestInclassPoint){

### 2017-01-26 tensorflow/CFIAR_09_convolutional_autoencoder.py

@@ -15,7 +15,7 @@ import matplotlib.pyplot as plt
 
 # %%
 def autoencoder(input_shape=[None, 3072],
-                n_filters=[3, 8, 8, 3 ],
+                n_filters=[3, 40, 40, 2 ],
                 filter_sizes=[3, 3, 3, 3 ],
                 corruption=False):
     """Build a deep denoising autoencoder w/ tied weights.
@@ -170,8 +170,8 @@ def traing_cifar(feat, labels):
     # %%
     # Plot example reconstructions
     
-    fo = open('../python/OurMethod/src/CIFAR.txt','w')
-    foi = open('../python/OurMethod/src/CIFAR_images.txt','w')
+    fo = open('../python/OurMethod/src/CIFAR5.txt','w')
+    foi = open('../python/OurMethod/src/CIFAR5_images.txt','w')
     
     n_examples = 100
     for k in xrange(n/n_examples):
@@ -218,7 +218,7 @@ def traing_cifar(feat, labels):
 
 # %%
 if __name__ == '__main__':
-    cifar  = pickle.load( open( "cifar/3classCFAR100.pickle", "rb" ) )
+    cifar  = pickle.load( open( "cifar/5classCFAR100.pickle", "rb" ) )
     
     feat = cifar['data']
     labels = cifar['labels']

### 2017-01-26 tensorflow/MNIST_09_convolutional_autoencoder.py

@@ -10,7 +10,7 @@ from libs.utils import corrupt
 
 # %%
 def autoencoder(input_shape=[None, 784],
-                n_filters=[1, 10, 10, 10, 5],
+                n_filters=[1, 40, 40, 40, 4],
                 filter_sizes=[3, 3, 3, 3, 3],
                 corruption=False):
     """Build a deep denoising autoencoder w/ tied weights.
@@ -165,12 +165,13 @@ def test_mnist():
     # %%
     # Plot example reconstructions
     
-    fo = open('../python/OurMethod/src/MNIST.txt','w')
-    foi = open('../python/OurMethod/src/MNIST_images.txt','w')
+    fo = open('../python/OurMethod/src/MNISTFULL.txt','w')
+    foi = open('../python/OurMethod/src/MNISTFULL_images.txt','w')
     
-    for k in xrange(50):
+    
+    n_examples = 100
+    for k in xrange(10000/n_examples):
         print k
-        n_examples = 64
         test_xs, test_ys = mnist.test.next_batch(n_examples)
         
         test_xs_norm = np.array([img - mean_img for img in test_xs])
@@ -187,9 +188,9 @@ def test_mnist():
                         out+= [k]
             yy = test_ys[sj]
             label = sum( yy[j]*j for j in xrange(10) )
-            if (label == 0 or label==1 or label==2):
-                fo.write(str(int(label))+':'+' '.join([str(kk) for kk in out])+'\n')
-                foi.write(' '.join(  [str(kk) for kk in test_xs[sj] ]   )+'\n')
+#             if (label == 0 or label==1 or label==2):
+            fo.write(str(int(label))+':'+' '.join([str(kk) for kk in out])+'\n')
+            foi.write(' '.join(  [str(kk) for kk in test_xs[sj] ]   )+'\n')
     fo.close() 
     foi.close()
  

### 2018-05-20 gopath/src/GRPCdemo/client.go
add
add golang

@@ -1,0 +1,43 @@
+package main
+
+//client.go
+
+import (
+	"log"
+	"os"
+	"fmt"
+	"golang.org/x/net/context"
+	"google.golang.org/grpc"
+	pb"./hello"
+)
+
+const (
+	address     = "localhost:50051"
+)
+var (
+	defaultName string
+
+)
+
+
+func main() {
+	conn, err := grpc.Dial(address, grpc.WithInsecure())
+	if err != nil {
+		log.Fatal("did not connect: %v", err)
+	}
+	defer conn.Close()
+	c := pb.NewGreeterClient(conn)
+
+	fmt.Println("Please input your name: ")
+	fmt.Scanln(&defaultName)
+
+	name := defaultName
+	if len(os.Args) >1 {
+		name = os.Args[1]
+	}
+	r, err := c.SayHello(context.Background(), &pb.HelloRequest{Name:name})
+	if err != nil {
+		log.Fatal("could not greet: %v", err)
+	}
+	log.Printf("Greeting: %s", r.Message)
+}

### 2018-05-20 gopath/src/GRPCdemo/hello/hello.pb.go

@@ -1,0 +1,197 @@
+// Code generated by protoc-gen-go. DO NOT EDIT.
+// source: hello.proto
+
+package helloworld
+
+import proto "github.com/golang/protobuf/proto"
+import fmt "fmt"
+import math "math"
+
+import (
+	context "golang.org/x/net/context"
+	grpc "google.golang.org/grpc"
+)
+
+// Reference imports to suppress errors if they are not otherwise used.
+var _ = proto.Marshal
+var _ = fmt.Errorf
+var _ = math.Inf
+
+// This is a compile-time assertion to ensure that this generated file
+// is compatible with the proto package it is being compiled against.
+// A compilation error at this line likely means your copy of the
+// proto package needs to be updated.
+const _ = proto.ProtoPackageIsVersion2 // please upgrade the proto package
+
+// The request message containing the user's name.
+type HelloRequest struct {
+	Name                 string   `protobuf:"bytes,1,opt,name=name" json:"name,omitempty"`
+	XXX_NoUnkeyedLiteral struct{} `json:"-"`
+	XXX_unrecognized     []byte   `json:"-"`
+	XXX_sizecache        int32    `json:"-"`
+}
+
+func (m *HelloRequest) Reset()         { *m = HelloRequest{} }
+func (m *HelloRequest) String() string { return proto.CompactTextString(m) }
+func (*HelloRequest) ProtoMessage()    {}
+func (*HelloRequest) Descriptor() ([]byte, []int) {
+	return fileDescriptor_hello_0d7b30e2368a3ee3, []int{0}
+}
+func (m *HelloRequest) XXX_Unmarshal(b []byte) error {
+	return xxx_messageInfo_HelloRequest.Unmarshal(m, b)
+}
+func (m *HelloRequest) XXX_Marshal(b []byte, deterministic bool) ([]byte, error) {
+	return xxx_messageInfo_HelloRequest.Marshal(b, m, deterministic)
+}
+func (dst *HelloRequest) XXX_Merge(src proto.Message) {
+	xxx_messageInfo_HelloRequest.Merge(dst, src)
+}
[…]

### 2018-05-20 gopath/src/GRPCdemo/server.go

@@ -1,0 +1,30 @@
+// server.go
+package main
+import (
+"log"
+"net"
+"golang.org/x/net/context"
+"google.golang.org/grpc"
+pb"./hello"
+)
+
+const (
+	port = ":50051"
+)
+
+
+type server struct {}
+
+func (s *server) SayHello(ctx context.Context, in *pb.HelloRequest) (*pb.HelloReply, error) {
+	return &pb.HelloReply{Message: "Hello " + in.Name }, nil
+}
+
+func main() {
+	lis, err := net.Listen("tcp", port)
+	if err != nil {
+		log.Fatal("failed to listen: %v", err)
+	}
+	s := grpc.NewServer()
+	pb.RegisterGreeterServer(s, &server{})
+	s.Serve(lis)
+}

### 2018-05-20 gopath/src/GRPCdemo2/client.go

@@ -1,0 +1,47 @@
+package main
+
+//client.go
+
+import (
+	"log"
+	"os"
+	"fmt"
+	"golang.org/x/net/context"
+	"google.golang.org/grpc"
+	pb"./hello"
+)
+
+const (
+	address     = "localhost:50051"
+)
+var (
+	defaultName string
+	num1 float64
+	num2 float64
+)
+
+
+func main() {
+	conn, err := grpc.Dial(address, grpc.WithInsecure())
+	if err != nil {
+		log.Fatal("did not connect: %v", err)
+	}
+	defer conn.Close()
+	c := pb.NewGreeterClient(conn)
+
+	fmt.Println("Please input your name: ")
+	fmt.Scanln(&defaultName)
+	fmt.Println("Please input 1st number: ")
+	fmt.Scanln(&num1)
+	fmt.Println("Please input 2nd number: ")
+	fmt.Scanln(&num2)
+	name := defaultName
+	if len(os.Args) >1 {
+		name = os.Args[1]
+	}
+	r, err := c.SayHello(context.Background(), &pb.HelloRequest{Name:name,Inputnum1:num1,Inputnum2:num2 })
+	if err != nil {
+		log.Fatal("could not greet: %v", err)
+	}
+	log.Printf("Greeting: %s", r.Message)
+}

### 2018-05-20 gopath/src/GRPCdemo2/hello/hello.pb.go

@@ -1,0 +1,215 @@
+// Code generated by protoc-gen-go. DO NOT EDIT.
+// source: hello.proto
+
+package helloworld
+
+import proto "github.com/golang/protobuf/proto"
+import fmt "fmt"
+import math "math"
+
+import (
+	context "golang.org/x/net/context"
+	grpc "google.golang.org/grpc"
+)
+
+// Reference imports to suppress errors if they are not otherwise used.
+var _ = proto.Marshal
+var _ = fmt.Errorf
+var _ = math.Inf
+
+// This is a compile-time assertion to ensure that this generated file
+// is compatible with the proto package it is being compiled against.
+// A compilation error at this line likely means your copy of the
+// proto package needs to be updated.
+const _ = proto.ProtoPackageIsVersion2 // please upgrade the proto package
+
+// The request message containing the user's name.
+type HelloRequest struct {
+	Name                 string   `protobuf:"bytes,1,opt,name=name" json:"name,omitempty"`
+	Inputnum1            float64  `protobuf:"fixed64,2,opt,name=inputnum1" json:"inputnum1,omitempty"`
+	Inputnum2            float64  `protobuf:"fixed64,3,opt,name=inputnum2" json:"inputnum2,omitempty"`
+	XXX_NoUnkeyedLiteral struct{} `json:"-"`
+	XXX_unrecognized     []byte   `json:"-"`
+	XXX_sizecache        int32    `json:"-"`
+}
+
+func (m *HelloRequest) Reset()         { *m = HelloRequest{} }
+func (m *HelloRequest) String() string { return proto.CompactTextString(m) }
+func (*HelloRequest) ProtoMessage()    {}
+func (*HelloRequest) Descriptor() ([]byte, []int) {
+	return fileDescriptor_hello_c5a8784d3184843e, []int{0}
+}
+func (m *HelloRequest) XXX_Unmarshal(b []byte) error {
+	return xxx_messageInfo_HelloRequest.Unmarshal(m, b)
+}
[…]

### 2018-05-20 gopath/src/GRPCdemo2/server.go

@@ -1,0 +1,31 @@
+// server.go
+package main
+import (
+"log"
+"net"
+"golang.org/x/net/context"
+"google.golang.org/grpc"
+pb"./hello"
+	"strconv"
+)
+
+const (
+	port = ":50051"
+)
+
+
+type server struct {}
+
+func (s *server) SayHello(ctx context.Context, in *pb.HelloRequest) (*pb.HelloReply, error) {
+	return &pb.HelloReply{Message: "Hello " + in.Name +"\n" + strconv.FormatFloat(in.Inputnum1 , 'E', -1, 64)+ strconv.FormatFloat(in.Inputnum2 , 'E', -1, 64) + "="+ strconv.FormatFloat(in.Inputnum1 + in.Inputnum2 , 'E', -1, 64)}, nil
+}
+
+func main() {
+	lis, err := net.Listen("tcp", port)
+	if err != nil {
+		log.Fatal("failed to listen: %v", err)
+	}
+	s := grpc.NewServer()
+	pb.RegisterGreeterServer(s, &server{})
+	s.Serve(lis)
+}

### 2018-05-20 gopath/src/Helloworld/src/main/hello.go

@@ -1,0 +1,7 @@
+package main
+
+import "fmt"
+
+func main() {
+	fmt.Println("hello world!!! :P")
+}

### 2018-05-20 gopath/src/echoex/client.go

@@ -1,0 +1,47 @@
+package main
+
+import (
+	"net"
+	"fmt"
+	"os"
+	"bufio"
+)
+
+const BUFF_SIZE = 1024
+var input = make([]byte,BUFF_SIZE)
+
+func handleError(err error) {
+	if err == nil {
+		return
+	}
+	fmt.Printf("error:%s\n",err.Error())
+}
+
+func main() {
+	if len(os.Args) != 2 {
+		fmt.Println("Usage:<command> <port>")
+		return
+	}
+	port := os.Args[1]
+	tcpAddr,err := net.ResolveTCPAddr("tcp4","localhost:"+port)
+	handleError(err)
+	tcpConn,err := net.DialTCP("tcp4",nil,tcpAddr)
+	handleError(err)
+	reader :=  bufio.NewReader(os.Stdin)
+	var continued = true
+	var inputStr string
+	for continued {
+		n,err := reader.Read(input)
+		handleError(err)
+		if n > 0 {
+			k,_ := tcpConn.Write(input[:n])
+			if k > 0 {
+				inputStr = string(input[:k])
+				fmt.Printf("Write:%s",inputStr)
+				if inputStr == "exit\n" {  //在比对时由于有个回车符，所以加上\n
+					continued = false        //也可以将inputStr = TrimRight(inputStr,"\n")
+				}
+			}
+		}
+	}
+}

### 2018-05-20 gopath/src/echoex/server.go

@@ -1,0 +1,59 @@
+package main
+
+import (
+	"net"
+	"os"
+	"fmt"
+	"io"
+)
+
+const BUFF_SIZE = 1024
+var buff = make([]byte,BUFF_SIZE)
+
+// 接受一个TCPConn处理内容
+func handleConn(tcpConn *net.TCPConn){
+	if tcpConn == nil {
+		return
+	}
+	for {
+		n,err := tcpConn.Read(buff)
+		if err == io.EOF {
+			fmt.Printf("The RemoteAddr:%s is closed!\n",tcpConn.RemoteAddr().String())
+			return
+		}
+		handleError(err)
+		if string(buff[:n]) == "exit" {
+			fmt.Printf("The client:%s has exited\n",tcpConn.RemoteAddr().String())
+		}
+		if n > 0 {
+			fmt.Printf("Read:%s",string(buff[:n]))
+		}
+	}
+}
+// 错误处理
+func handleError(err error) {
+	if err == nil {
+		return
+	}
+	fmt.Printf("error:%s\n",err.Error())
+}
+
+func main() {
+	if len(os.Args) != 2 {
+		fmt.Println("Usage:<command> <port>")
+		return
+	}
+	port := os.Args[1]
+	tcpAddr,err := net.ResolveTCPAddr("tcp4","localhost:"+port)
+	handleError(err)
+	tcpListener,err := net.ListenTCP("tcp4",tcpAddr)  //监听
+	handleError(err)
+	defer tcpListener.Close()
+	for {
+		tcpConn,err := tcpListener.AcceptTCP()
+		fmt.Printf("The client:%s has connected!\n",tcpConn.RemoteAddr().String())
+		handleError(err)
+		defer tcpConn.Close()
+		go handleConn(tcpConn)    //起一个goroutine处理
+	}
+}

### 2018-05-20 gopath/src/echoframework/src/echo.pb.go

@@ -1,0 +1,191 @@
+// Code generated by protoc-gen-go. DO NOT EDIT.
+// source: echo.proto
+
+package echo
+
+import proto "github.com/golang/protobuf/proto"
+import fmt "fmt"
+import math "math"
+
+import (
+	context "golang.org/x/net/context"
+	grpc "google.golang.org/grpc"
+)
+
+// Reference imports to suppress errors if they are not otherwise used.
+var _ = proto.Marshal
+var _ = fmt.Errorf
+var _ = math.Inf
+
+// This is a compile-time assertion to ensure that this generated file
+// is compatible with the proto package it is being compiled against.
+// A compilation error at this line likely means your copy of the
+// proto package needs to be updated.
+const _ = proto.ProtoPackageIsVersion2 // please upgrade the proto package
+
+type EchoReq struct {
+	Msg                  string   `protobuf:"bytes,1,opt,name=msg" json:"msg,omitempty"`
+	XXX_NoUnkeyedLiteral struct{} `json:"-"`
+	XXX_unrecognized     []byte   `json:"-"`
+	XXX_sizecache        int32    `json:"-"`
+}
+
+func (m *EchoReq) Reset()         { *m = EchoReq{} }
+func (m *EchoReq) String() string { return proto.CompactTextString(m) }
+func (*EchoReq) ProtoMessage()    {}
+func (*EchoReq) Descriptor() ([]byte, []int) {
+	return fileDescriptor_echo_13c504789862e0e6, []int{0}
+}
+func (m *EchoReq) XXX_Unmarshal(b []byte) error {
+	return xxx_messageInfo_EchoReq.Unmarshal(m, b)
+}
+func (m *EchoReq) XXX_Marshal(b []byte, deterministic bool) ([]byte, error) {
+	return xxx_messageInfo_EchoReq.Marshal(b, m, deterministic)
+}
+func (dst *EchoReq) XXX_Merge(src proto.Message) {
+	xxx_messageInfo_EchoReq.Merge(dst, src)
+}
+func (m *EchoReq) XXX_Size() int {
+	return xxx_messageInfo_EchoReq.Size(m)
+}
[…]

### 2018-05-20 gopath/src/echoframework/src/server.go

@@ -1,0 +1,24 @@
+
+package echo
+
+import proto "github.com/golang/protobuf/proto"
+import fmt "fmt"
+import math "math"
+
+import (
+	context "golang.org/x/net/context"
+	grpc "google.golang.org/grpc")
+
+type EchoServerImp struct {
+
+}
+
+func (e *EchoServerImp) Echo(ctx context.Context, req *echo.EchoReq) (*echo.EchoRes, error) {
+	fmt.Printf("message from client: %v\n", req.GetMsg())
+
+	res := &echo.EchoRes{
+		Msg: req.GetMsg(),
+	}
+
+	return res, nil
+}

### 2018-05-20 gopath/src/tcpdemo/client.go

@@ -1,0 +1,29 @@
+package main
+import (
+	"fmt"
+	"net"
+	"os"
+)
+
+func main() {
+
+	conn, err := net.Dial("tcp", "127.0.0.1:8080")
+	if err != nil {
+		fmt.Println("dial failed:", err)
+		os.Exit(1)
+	}
+	defer conn.Close()
+
+
+	buffer := make([]byte, 512)
+
+	n, err2 := conn.Read(buffer)
+	if err2 != nil {
+		fmt.Println("Read failed:", err2)
+		return
+	}
+
+	fmt.Println("count:", n, "msg:", string(buffer))
+
+
+}

### 2018-05-20 gopath/src/tcpdemo/server.go

@@ -1,0 +1,57 @@
+package main
+import (
+"fmt"
+"net"
+"log"
+)
+
+func main() {
+
+addr := "0.0.0.0:8080"
+
+tcpAddr, err := net.ResolveTCPAddr("tcp",addr)
+
+if err != nil {
+log.Fatalf("net.ResovleTCPAddr fail:%s", addr)
+}
+
+listener, err := net.ListenTCP("tcp", tcpAddr)
+if err != nil {
+log.Fatalf("listen %s fail: %s", addr, err)
+} else {
+
+log.Println("rpc listening", addr)
+}
+
+
+for {
+conn, err := listener.Accept()
+if err != nil {
+log.Println("listener.Accept error:", err)
+continue
+}
+
+go handleConnection(conn)
+
+}
+
+}
+
+
+func handleConnection(conn net.Conn) {
+
+defer conn.Close()
+
+var buffer []byte = []byte("You are welcome. I'm server.!!!")
+
+n, err := conn.Write(buffer)
+
+if err != nil {
+
+fmt.Println("Write error:", err)
+}
+fmt.Println("send:", n)
+
+fmt.Println("connetion end")
+
+}

### 2018-05-20 matlab/plot2lines.m
modify

@@ -1,0 +1,23 @@
+
+plot(X, Y, 'k-o','linewidth', 2, 'markersize', 4);
+
+ylabel('# of constraints','fontname','标楷体', 'fontweight', 'bold', 'fontsize', 12 );
+
+xlabel('K2', 'fontname', '标楷体', 'fontweight', 'bold', 'fontsize',12);
+
+set(gca,'xtick',[1,2,3,4,5,6,7,8,9,10]);
+
+hold on
+
+plot(X, Z, 'k--o', 'linewidth', 2, 'markersize', 4);
+
+legend ConcurrentConstraints ActiveConstraints
+
+box off
+
+legend('boxoff');
+
+set(legend, 'fontname', '标楷体');
+
+set(legend, 'fontweight', '标楷体');
+hold off

### 2018-05-20 matlab/plotline.m

@@ -1,0 +1,12 @@
+
+
+plot(X, T, 'k-o','linewidth', 2, 'markersize', 4);
+
+ylabel('Time consumed/s','fontname','标楷体', 'fontweight', 'bold', 'fontsize', 12 );
+
+xlabel('generations', 'fontname', '标楷体', 'fontweight', 'bold', 'fontsize',12);
+
+set(gca,'xtick',[1,2,3,4,5,6]);
+
+
+hold off

### 2018-05-20 matlab/plotmatrix.m

@@ -1,0 +1,8 @@
+
+imagesc(A)          %×÷Í¼
+colorbar
+for i = 1:2
+    for j = 1:2
+        text(i, j, sprintf('%d',A(j,i)))
+    end
+end

### 2018-05-20 MS/thesis/tex 10 26/Adaptive_distance_metric_notes.tex
add cv

--- 2016-10-21 latex/Adaptive_distance_metric_notes.tex
@@
 
-\usepackage{url}
 \newcommand{\cone}{{\rm cone}} % Cone
@@
 \title{Adaptive Distance Metric Selection for Supervised Classification}
-\author{Krishnan Kumaran and Dimitri J. Papageorgiou \\
-{\small Corporate Strategic Research}\\
-{\small ExxonMobil Research and Engineering Company}\\
-{\small 1545 Route 22 East, Annandale, NJ 08801 USA}\\
-{\small dimitri.j.papageorgiou@exxonmobil.com} \\
-}
 
@@
 
-\section{Plot of number of outliers as function $\epsilon$}
+\todo[inline]{
+My questions:
 
-\todo[inline]{this should be done before next meeting on 2016-10-27}
-
-\begin{itemize}
-\item 
-  make a plots a number of outliers as function of epsilon
-+ show also the datasets which you have used and so on
-\item 
-  try different datasets, also generate the two gaussian mixtures
-\item   find out how to export figure to EPS from AIMMS
-\item  change a copy of {\bf output scatter plot} to use the learnt distance measure
-\end{itemize}
+Value of epsilon matters only when it is nearly reaching “max epsilon”, so why do we care about it after this algorithm?
+I mean it will not change the final solution if we keep epsilon less equal than “max epsilon”/2.
+}
 
@@
 Constraints \eqref{eq:mccormick_1}-\eqref{eq:mccormick_3} are the so-called McCormick envelopes needed to linearize the bilinear equation $w_{ij} = d_{ij} y_{ij}$.
-
-\todo[inline]{Modify to incorporate assumption that $0 \leq d_{ij} \leq 1$ for all $i$ and $j$.}
-
-\subsection{Similar to previous but we will have just one lambda}
-\label{sec:mimax_oneLamnda}
-\todo[inline]{FInish this soon and compare with previous approach}
 
@@
 \newpage
+\section{Iterative LP Algorithm with Row and Column Generation}
+
+A potential hurdle in the LP above is the huge number of constraints. For example, an instance with 1000
+points, 10 classes, and 100 points per class would require 900,000 constraints for each ($i$,$k$) pair, while an
+instance with 10,000 points, 10 classes, and 1000 points per class would require 9,000,000 constraints for
+each ($i$,$k$) pair. Meanwhile, the fundamental theorem of linear programming asserts that if an optimal
+solution exists, there exists an optimal basic feasible solution that will involve $n$ active constraints, where
+$n$ = $N$ + ($p$ + 1)$p$/2 and $m$ = $N^2$ ($O$($N^2$)). Note that $n$ << $m$. There is likely to be a large amount of
+degeneracy.
+
+Our goal is to significantly reduce the number of constraints that must be explicitly included in the LP.
+Let $N_A \subseteq   N$ be the set of active points considered in the LP. Let $S_i \subseteq  C_i$ and   $\overline S_i \subseteq \overline C_i $ for each point i 2 N.
+Here, $S_i ( \overline S_i)$ represents the set of co-class (non-class) neighbors that are currently considered in the LP.
+
+Let W be a positive scalar. Consider the following reduced LP that maximizes both $\epsilon$  and the minimum
+distance variables $t_i$:
+
+\begin{subequations} \label{model:big_lp_algorithm_1}
+\begin{alignat}{4}
+\max_{\v{a},\v{B},\v{d},\v{t}}~~& \sum_{i \in \mc{N}_A} t_i &&  \\
+\st~~& t_i + \epsilon \leq d_{ik} && \qquad \forall i \in \mc{N}_A, k \in \overline{\mc{S}}_i \label{eq:big_lp_separation_constr_al_1} \\
+    & t_i \leq d_{ij} && \qquad \forall i \in \mc{N}_A, j \in \mc{S}_i \label{eq:big_lp_dual_constr_al_1} \\
+    & t_i \geq 0 & & \qquad \forall i \in \mc{N}_A \\
+       & d_{ij} = \sum_{k=1}^p \delta_{ijk} a_{k} + \sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N}  \\
+    & 0 \leq d_{ij} \leq 1 && \qquad \forall i,j \in \mc{N} \\
+    & \v{a} \in \Re^p && \\ 
+    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p
+\end{alignat}
+\end{subequations}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.15]{Fast_LP.png}
+%\vspace{-0.25in}
+\caption{LP Approach via Row and Column Generation (Fast LP)}
+\label{fig:Fast_LP}
+\end{center}
+\end{figure}
+
+\begin{algorithm}
+%{\small
+\caption{LP Approach via Row and Column Generation (Fast LP)}
+\label{algo:Fast_LP}
+\begin{algorithmic}[1]
+\STATE Initialize: $\mc{N}_A= \mc{N}; O=\varnothing; S_i=\lbrace argmin\lbrace d_{ij}:j \in \mc{C}_i\rbrace \rbrace$; $\overline{S}_i=\lbrace argmin\lbrace d_{ik}:k \in \mc{N} \setminus \mc{C}_i\rbrace \rbrace$; Fix $\epsilon$ ; \textbf{B}= Euclidean distance metric;
+\STATE DONE = False
+\STATE (Re-)Solve model \eqref{model:big_lp_algorithm_1} for $B^*,d^*_{ij},t^*_i$. Fix the distance metric to $d^*_{ij}$.
+\FOR{ $i \in \mc{N}_A$ }
+	\STATE Set $\mc{V}_i= \lbrace j \in \mc{C}_i\setminus \mc{S}_i : t^*_i> d^*_{ij}\rbrace $. 
+	\STATE Set $\overline{\mc{V}}_i= \lbrace k \in \overline{\mc{C}}_i\setminus \overline{\mc{S}}_i : t^*_i + \epsilon > d^*_{ik}\rbrace $.
+ 	\STATE Set $\mc{V}_i= \lbrace j \in \mc{C}_i\setminus \mc{S}_i : t^*_i> d^*_{ij}\rbrace $. 
+\ENDFOR
+\STATE ...
+\STATE ...\todo[inline]{(need time to edit, I put a pic tells the algorithm down there)}
+
+	\STATE Store the outliers and distance metric
+\end{algorithmic}
+%}
+\end{algorithm}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.8]{Fast_LP_fig.png}
+%\vspace{-0.25in}
+\caption{LP Approach via Row and Column Generation (Fast LP)}
+\label{fig:Fast_LP_fig}
+\end{center}
+\end{figure}
+
+\todo[inline]{
+My questions:
+
+1. Why NN, not 2-NN, 3-NN?  OK, it reduces the calculating time.
+
+2. What if 3-NN or 6-NN performs better in accuracy? Do we need experiments on this?
+
+3. Value of epsilon matters only when it is nearly reaching “max epsilon”, so why do we care about it ? I mean it will not change the solution if we keep epsilon less equal than “max epsilon”/2.
+}
+
+\newpage
+\section{Outlier re-insertion}
+
+\subsection{Outlier re-insertion in MILP}
+
+.........\todo[inline]{(2 pages, Later I will put it on)}
+
+\subsection{Outlier re-insertion with ranking of $R_i$}
+
+Though the MILP problem is improved, when facing large scale of dataset, it will be out of the capability to solve in a short time. Here represents a new method with
+$R_i =  {\min_{j \in \mc{C}_i} d_{ij}}/ {\min_{k \in \overline{\mc{C}}_i} d_{ik}}$
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[scale=0.8]{Figure_R_i.png}
+%\vspace{-0.25in}
+\caption{Algorithm performing method with $R_i$}
+\label{fig:Figure_R_i}
+\end{center}
+\end{figure}
+
+Note that the iteration need to loop over several times to achieve the end.
+When the dataset is very large, it will be time consuming.
+To discard unnecessary procedures, introduce an improved re-insertion method:
+
+\begin{algorithm}
+%{\small
+\caption{Improved Method of Outlier Re-insertion with Ranking of $R'_i$}
+\label{algo:Improved_Method_of_Outlier_Re-insertion}
+\begin{algorithmic}[1]
+\STATE Compute $R_i$ for each outlier $i$; 
+\STATE Identify all non-outliers $j$ for which $i$ is now the nearest co-class/non-class neighbor, i.e. all $j$ whose $R_i$ values are affected by insertion of $i$;
+\STATE Define $R'_i= min (R_i  ,\min_j{R_j })$;
+\STATE Sort outliers in the order of decreasing $R'_i$;
+\STATE Insert the outliers according to decreasing ranking of $R'_i$;
+\STATE Repeat steps 1-5 until no further re-insertion is possible, i.e. remaining outliers all have $R'_i<1$;
+
+\end{algorithmic}
+%}
+\end{algorithm}
+
+\todo[inline]{My question:
+
+4.If Metric does not change after we put points back, so why do we do that? It’s meaningless.
+
+5. About what to do next?
+
+ (1) See how initialization of Matrix B influence the solving time in Fast LP.
+
+ (2) Comparison of our method and others( k-nn ,svm…) with different dataset.
+
+(3) Improving of the method (hardest)
+}
+
+\newpage
+
 \section{Nomenclature}
@@
 
-\newpage
 \section{Gershgorin Circle Theorem}
@@
 
-\todo[inline]{In the AIMMS code, we do not store the full $\v{B}$ matrix, but instead work only with the upper diagonal.
-Thus, it does not make sense to sum over all elements in row $k$ as written in $\sum _{\ell \neq k} b^+_{k\ell}$.
-Task: Write a similar version of constraints~\ref{model:gershgorin_restriction} in Latex.
-Implement these additional variables and constraints in AIMMS.
-Also, include a binary parameter, say, PI-Require-PSD (use underscores) such that these new variables and constraints are only active if PI-Require-PSD = 1, i.e., you should put a conditional statement ``$|$ ~ PI-Require-PSD'' in the ``index domain'' of these new variables and constraints.
-}
-
-\newpage 
-\part{Progress Reports}
-
-\subsection{2016-10-21}
-\begin{itemize}
-\item Loading instance works
-
-\item Solving  \eqref{model:epsilon_lp_1} works now
-
-\item Model \eqref{model:milp_with_outlier_detection}
-works. I did it in the aimms code "MILP SECTION4" Part.
-
-\end{itemize}
-{\bf problems and questions:}
-\begin{itemize}
-\item queston 1 How to show the certain points in the plots?
-\item question 2
-
-\end{itemize}
-
-\newpage
-\part{Tasks to do }
-
-\begin{itemize}
-\item 1. Create new dataset -> e.g. 2 - Guassian with diffrent mu and Sigma
-\item 2. ammend the code to add new point in a.g. Scatter Point
-\item 3. Implement Optimization of Distance Metrix                 ACCOMPLISHED
-\item 4. Add the robust version for section 4. (have just one lambda) both Latex and AIMS (PROCESSING)
-\item 5. Create a performance profiles -- example 100 datasets and comapre 3-4 distance measures 
-\item 6. add new codes for replacing "a delta"  -> to  "a |delta| "           ACCOMPLISHED
-\item 7. add button to load instance          ACCOMPLISHED
-\item 8. For Infesible problem we solved during the meeting why it was not infeasible                  ACCOMPLISHED
-
-\end{itemize}
-
 \end{document}

### 2018-05-21 MS/Lehigh course/444/hw1.m
add course

@@ -1,0 +1,15 @@
+clear; clc;
+
+up=100;
+low=-100;
+n=100;
+a=1;
+b=2;
+c=3;
+
+x1=(up-low)*rand(1,n)+low;
+x2=(up-low)*rand(1,n)+low;
+
+func=@(x,y) sign(a*x+b*y+c);
+yi = arrayfun(func,x1,x2);
+plot(x1,x2);

### 2018-05-21 MS/Lehigh course/444/plot2dcurves.m

@@ -1,0 +1,14 @@
+clear; clc;
+
+x1 = -3:0.05:3;
+x2 = -3:0.05:3;
+[x1,x2] = meshgrid(x1,x2);
+
+func = @(x,y) 2*x^2 + 1*y^2 + 1*x*y + 1*x + 1*y - 3;
+
+z = arrayfun(func,x1,x2);
+
+figure(); hold on;
+contour(x1,x2,z,[0 0],'b-');
+contour(x1,x2,z,[-1 1],'y:');
+contour(x1,x2,z,[2 2],'b-');

### 2018-05-21 MS/Lehigh course/444/plot2dcurvesex.m

@@ -1,0 +1,12 @@
+clear; clc;
+
+x1 = -3:0.05:3;
+x2 = -3:0.05:3;
+[x1,x2] = meshgrid(x1,x2);
+
+func = @(x,y) 2*x^2 + 1*y^2 + 1*x*y + 1*x + 1*y - 3;
+
+z = arrayfun(func,x1,x2);
+
+figure(); hold on;
+contour(x1,x2,z,[0 0],'y:');

### 2018-05-21 MS/Lehigh course/444/project444/Regression/LRegression.cpp

@@ -1,0 +1,202 @@
+
+#include "LRegression.h"
+
+#include <cmath>
+
+LLinearRegression::LLinearRegression()
+{
+
+}
+
+LLinearRegression::~LLinearRegression()
+{
+
+}
+
+bool LLinearRegression::TrainModel(
+    IN const LRegressionProblem& problem, 
+    IN float learningRate, 
+    IN unsigned int trainTimes)
+{
+    // 检查参数
+    if (problem.XMatrix.RowLen < 2)
+        return false;
+    if (problem.XMatrix.ColumnLen < 1)
+        return false;
+    if (problem.YVector.ColumnLen != 1)
+        return false;
+    if (problem.YVector.RowLen != problem.XMatrix.RowLen)
+        return false;
+    if (learningRate <= 0.0f)
+        return false;
+
+    // 每个样本中最后一项增加常数项的特征值:1.0
+    m_xMatrix.Reset(problem.XMatrix.RowLen, problem.XMatrix.ColumnLen + 1);
+    for (unsigned int row = 0; row < m_xMatrix.RowLen; row++)
+    {
+        for (unsigned int col = 0; col < m_xMatrix.ColumnLen-1; col++)
+        {
+            m_xMatrix[row][col] = problem.XMatrix[row][col];
+        }
+        m_xMatrix[row][m_xMatrix.ColumnLen-1] = 1.0f; 
+    }
+
+    m_yVector = problem.YVector;
+
+    // 初始化权重向量
+    m_wVector.Reset(m_xMatrix.ColumnLen, 1, 0.0f);
+  
+    const LRegressionMatrix& X = m_xMatrix;
+    const LRegressionMatrix& Y = m_yVector;
+    LRegressionMatrix& W = m_wVector;
+    float A = learningRate;
+
+    LRegressionMatrix XT = X.T();
+
+    LRegressionMatrix XW;
+    LRegressionMatrix O;
+
+    for (unsigned int i = 0; i < trainTimes; i++)
+    {
+        XW = X * W;
+        O = XT * (XW - Y);
+        W = W - O.ScalarMul(A);
+    }
+
+    return true;
+}
+
+bool LLinearRegression::GetWeightVector(OUT LRegressionMatrix& weightVector)
+{
+    if (m_wVector.RowLen < 1)
+        return false;
+
+    weightVector = m_wVector;
+
+    return true;
+}
+
[…]

### 2018-05-21 MS/Lehigh course/444/project444/Regression/LRegression.h

@@ -1,0 +1,125 @@
+/// @file LRegression.h
+/// @brief 本文件中声明了一些回归算法
+/// 
+/// Detail:
+/// 线性回归
+/// 优点: 结果易于理解, 计算上不复杂
+/// 缺点: 对非线性数据拟合不好
+/// @author Burnell_Liu Email:burnell_liu@outlook.com
+/// @version   
+/// @date 10:10:2015
+
+#ifndef _LREGRESSION_H_
+#define _LREGRESSION_H_
+
+
+#include "LMatrix.h"
+
+typedef LMatrix<float> LRegressionMatrix;
+
+
+
+/// @brief 回归原始问题结构
+struct LRegressionProblem
+{
+    /// @brief 构造函数
+    /// @param[in] sampleMatrix 样本矩阵, 每一行为一个样本, 每行中的值为样本的特征值, 至少需要两个样本
+    /// @param[in] targetVector 目标向量(列向量), 行数为样本矩阵的行数, 列数为1, 每行的值代表样本矩阵中每个样本的目标(输出)
+    LRegressionProblem(IN const LRegressionMatrix& sampleMatrix, IN const LRegressionMatrix& targetVector)
+        : XMatrix(sampleMatrix), YVector(targetVector)
+    {
+    }
+
+    const LRegressionMatrix& XMatrix; ///< 样本矩阵
+    const LRegressionMatrix& YVector; ///< 目标向量(列向量)
+};
+
+/// @brief 线性回归类
+/// 线性函数为 h(x)  =  X * W
+/// W为特征权重的列向量, X为特征的行向量
+class LLinearRegression
+{
+public:
+    /// @brief 构造函数
+    LLinearRegression();
+
+    /// @brief 析构函数
+    ~LLinearRegression();
+
+    /// @brief 训练模型
+    /// @param[in] problem 原始问题
+    /// @param[in] learningRate 学习速度, 学习速度必须大于0
+    /// @param[in] trainTimes 训练次数
+    /// @return 成功返回true, 失败返回false(参数错误的情况下会返回失败)
+    bool TrainModel(
+        IN const LRegressionProblem& problem,
+        IN float learningRate,
+        IN unsigned int trainTimes);
+
+    /// @brief 获取权重向量(列向量)
+    /// 权重向量的长度为样本特征数目加1, 权重向量的最后一项为常数项值
+    /// @param[out] weightVector
[…]

### 2018-05-21 MS/Lehigh course/444/project444/Regression/main.cpp

@@ -1,0 +1,34 @@
+
+#include "LRegression.h"
+
+#include <cstdio>
+#include <Windows.h>
+
+int main()
+{
+    LMatrix<float> x(3, 1);
+    x[0][0] = 1.0f;
+    x[1][0] = 2.0f;
+    x[2][0] = 3.0f;
+
+    LMatrix<float> y(3, 1);
+    y[0][0] = 1.0f;
+    y[1][0] = 0.0f;
+    y[2][0] = 0.0f;
+
+    LRegressionProblem problem(x, y);
+    LLogisticRegression logistic;
+    logistic.TrainModel(problem, 1.0f, 500);
+    printf("%f\n",logistic.GetLikelihood());
+    LRegressionMatrix weight;
+    logistic.GetWeightVector(weight);
+    for (unsigned int i = 0; i < weight.RowLen; i++)
+    {
+        printf("%f  ", weight[i][0]);
+    }
+    printf("\n");
+
+    system("pause");
+
+    return 0;
+}
